---
title: "IJM Papers Notebook"
output:
  pdf_document: default
  html_document:
    df_print: paged
---

```{r Preamble Loading Packages and Script.}
# Setting working directory to top of MINOS repository.
library(here)
library(knitr)
knitr::opts_knit$set(root.dir = here::here())

# Importing packages and supporting R. scripts.
source(here::here("IJM_case_study_notebook", "utils.R"))
source(here::here("IJM_case_study_notebook", "transition_model_functions.R"))
source(here::here("IJM_case_study_notebook", "paper_1_plots.R"))

library(dplyr)
library(texreg)
library(lme4)
library(glmnet)
library(mice)
library(sjPlot)
library(visreg)
library(ggplot2)
library(ggpattern)
library(VIM)
library(caret)
library(tidyverse)
library(performance)
library(broom.mixed)
library(ggridges)
library(ggmice)
library(MASS)
library(Rcpp)

# Set save directories for plots and tables.
save.path <- "IJM_plots_and_tables/"
create.if.not.exists(save.path)

# Set directories for input Understanding Society.
understanding.society.data.dir <- "data/composite_US/"
# set.seed(8) # set seed if require reproducible MICE results.
```

# Section 2: Baseline SF-12 MCS Model

This section formats raw Understanding Society (UKHLS) data and fits an Ordinary Least Squares model estimating Short Form 12 Mental Component Score (SF-12 MCS). This OLS model is used in Sections 2 and 3 of the IJM case study paper.

```{r OLS Data Preprocessing., echo=FALSE, warning=FALSE}

# Load Understanding Society data for the years 2011-2013.
filelist <- list.files(understanding.society.data.dir,
                       include.dirs = FALSE,
                       full.names = TRUE,
                       pattern = '[0-9]{4}_US_cohort.csv')[3:5]#[21:23] # get files for 2011-2013.
understanding.society.data <- do.call(rbind, lapply(filelist, read.csv))
names(understanding.society.data)[names(understanding.society.data) == 'SF_12'] <- 'SF_12_MCS'

# Baseline OLS model formula.
baseline.ols.model.formula.string <- "I(scale(log((SF_12_MCS)+10))) ~ factor(sex) + 
                  relevel(factor(ethnicity), ref='WBI') + 
                  scale(age) + 
                  factor(education_state) + 
                  factor(labour_state) + 
                  relevel(factor(NSSEC), ref=1) +
                  relevel(factor(region), ref='London') +
                  scale(hh_income)"

# Calculate required variables for regression to run. 
raw.model.formula <- as.formula(baseline.ols.model.formula.string)
variables <- all.vars(raw.model.formula)

# Get only needed variables and replace missing codes with NA.
understanding.society.data <- update.column.names(understanding.society.data)
understanding.society.data <- understanding.society.data[, append(variables, c("time", 'pidp','hidp', 'weight'))]
understanding.society.data <- replace.missing(understanding.society.data)

# Use raw data both with and without incomplete columns containing missing data removed.
understanding.society.data <- drop_na(understanding.society.data)

# SF12_MCS mean and variance reused later.
sf12.mcs.mean <- mean(log(understanding.society.data$SF_12_MCS+10))
sf12.mcs.std <- sqrt(var(log(understanding.society.data$SF_12_MCS+10)))

# Fit SF-12 MCS baseline OLS model.
sf12.mcs.ols <- lm(baseline.ols.model.formula.string,
              data= understanding.society.data)

#Save Coefficients to LaTeX table.
OLS.make.latex.tables(sf12.mcs.ols)
```

This section performs five-fold cross-validation of the baseline OLS model and estimates the root mean squared error (RMSE) for the OLS model.

```{r OLS Cross-Validation., echo=FALSE, warning=FALSE, warning=FALSE}
# Baseline cross val.
# Estimating the root mean squared error score of the baseline OLS model using five-fold cross-validation.

trControl <- trainControl(method = "cv", number=5, trim=T, verboseIter = TRUE, savePredictions = TRUE)

raw.cross.val.sf12.mcs.model <- train(as.formula(baseline.ols.model.formula.string), data = understanding.society.data,
               method = "lm",
               trControl = trControl)

# Getting RMSE scores for each of five cross folds.
raw.RMSE.statistics <- raw.cross.val.sf12.mcs.model$pred %>% 
  group_by(Resample) %>%
  mutate(obs =  exp(sf12.mcs.std * obs + sf12.mcs.mean) - 10) %>%
  mutate(pred =  exp(sf12.mcs.std * pred + sf12.mcs.mean) - 10) %>%
  summarise(output.RMSE=caret::RMSE(pred, obs)) %>%
  summarise(mean = mean(output.RMSE), std = sd(output.RMSE))

# Compute mean RMSE and standard deviation across all five folds.
print("Baseline OLS model RMSE Statistics: ")
print("RMSE mean: ")
print(raw.RMSE.statistics$mean)
print("RMSE standard deviation: ")
print(raw.RMSE.statistics$std)
```

# Section 3: Presentation of the OLS model

This section produces diagnostics for the OLS model providing evidence for why this model fails and how it can be improved. Plots form this section are included in Section 3 of the IMA case study paper.

```{r OLS Diagnostic Plots., echo=FALSE, warning=FALSE}

# Diagnostic plots for OLS presentation. Standard figures given using plot() function on lm object.
# Plot coefficient forest plot. Note exponential scaling for lognormal model.
ols.exponential.sf12.mcs.forest.plot(sf12.mcs.ols, paste0(save.path, "figure_3a_presentation_forest.pdf"))
# residuals density and quantile-quantile (qq) plots. checking for normality of residuals.
residual.density.plot(res=resid(sf12.mcs.ols), plot.file.name=paste0(save.path, "figure_3b_presentation_residual_density.pdf"), guide="normal")
qq.plot(resid(sf12.mcs.ols), paste0(save.path, "figure_3c_presentation_qq.pdf"))

# Creating scale-location plot using model residual errors. Doing this manually for consistency with other plots later..
squareRootRes <- sqrt(abs(scale(resid(sf12.mcs.ols))))
fitted.residuals <- as.data.frame(cbind(fitted(sf12.mcs.ols), squareRootRes))
colnames(fitted.residuals) <- c("fitted", "sqrt_residuals")
fitted.residual.plot(fitted.residuals, paste0(save.path, "figure_3d_presentation_scale_location_plot.pdf"))

# Performing nowcasting estimating SF-12 MCS scores from 2014-2020 using 2013 data.
# Loading and formatting 2013 data.
start.data <- understanding.society.data[which(understanding.society.data$time==2013),]
# Changing some variable names for consistency and readability.
start.data <- update.column.names(start.data)
handover.data <- start.data[, c("pidp", "SF_12_MCS", "hidp", "time")]
rolling.data <- start.data 

# mean and variances for unscaling back to standard SF-12 MCS variable.
start.sf12.mcs.mean <- mean(log(understanding.society.data$SF_12_MCS+10))
start.sf12.mcs.std <- sqrt(var(log(understanding.society.data$SF_12_MCS+10)))

# Repeat prediction using OLS model 8 times to transition from 2013 to 2021.
for (i in 1:8){
  rolling.data$SF_12_MCS <- ((exp(start.sf12.mcs.mean + start.sf12.mcs.std * predict(sf12.mcs.ols, rolling.data))-10))
  rolling.data[, 'time'] <- rolling.data[, 'time'] +1
  handover.data <- rbind(handover.data, rolling.data[, c("pidp", "hidp", "SF_12_MCS", "time")])
}

# Plotting handovers using ridgeline plots.
handover.boxplots(understanding.society.data, handover.data, "SF_12_MCS", save.path, "ols_SF12_boxplot")
density.ridges(understanding.society.data, "SF_12_MCS", save=TRUE, save.path=save.path, filename.tag = "figure_4a_ols_raw_ridges")
density.ridges(handover.data, "SF_12_MCS", save=TRUE, save.path=save.path, filename.tag = "figure_4b_ols_handover_ridges")

# Tidying up some data not used anymore.
rm(understanding.society.data)
rm(handover.data, rolling.data, start.data)
rm(fitted.residuals, squareRootRes, raw.cross.val.sf12.mcs.model)
```

# Section 4: Missingness

This section processes Understanding Society data again including further variables required for multiple imputation chained equations (MICE) imputation. The missing data structure for Understanding Society data is also provided.

```{r MICE Preprocessing., echo=FALSE, warning=FALSE}
# Load in UKHLS data again preprocessing for MICE imputation.
mice.data.filelist <- list.files(understanding.society.data.dir,
                       include.dirs = FALSE,
                       full.names = TRUE,
                       pattern = '[0-9]{4}_US_cohort.csv')
mice.data <- do.call(rbind, lapply(mice.data.filelist, read.csv))
mice.data <- update.column.names(mice.data)
names(mice.data)[names(mice.data) == 'SF_12'] <- 'SF_12_MCS'

# Define the regression model formula for the OLS model using MICE imputation.
# Note more variables are included due to imputation that cannot be used in the baseline model.
mice.formula.string <- "I(scale(log(SF_12_MCS+10))) ~ 
                        factor(sex) + 
                        relevel(factor(ethnicity), ref='WBI') + 
                        scale(age) + 
                        factor(education_state) + 
                        factor(labour_state) + 
                        relevel(factor(NSSEC), ref='1') +
                        relevel(factor(region), ref='London') +
                        scale(hh_income) + 
                        scale(I(hh_income**2)) +
                        relevel(factor(housing_quality), ref='Low') +
                        factor(neighbourhood_safety) + 
                        factor(loneliness) +
                        nutrition_quality +
                        ncigs"

# Get required UKHLS variables and replace missing value codes.
mice.model.formula <- as.formula(mice.formula.string)
variables <- all.vars(mice.model.formula)
mice.data <- replace.missing(mice.data)

# Preserving key columns that cannot be imputed. These are used later.
# Preserving time, sample weights, and identifiers.
mice.pidp <- mice.data[which(mice.data$time %in% seq(2011,2018)), "pidp"]
mice.hidp <- mice.data[which(mice.data$time %in% seq(2011,2018)), "hidp"]
mice.time <- mice.data[which(mice.data$time %in% seq(2011,2018)), "time"]
mice.weights <- mice.data[which(mice.data$time %in% seq(2011,2018)), "weight"]
```


This section performs MICE imputation and saves model coefficients.

```{r Running MICE., echo=FALSE, warning=FALSE}

# Plotting missing data structure for 2011-2013 Understanding Society data.
#defining required columns and labels for missing data structure aggr plot in VIM.
aggr.columns <- c("SF_12_MCS",
                 "NSSEC",
                 "education_state",
                 "labour_state", 
                 "ethnicity", 
                 "hh_income",
                 "neighbourhood_safety",
                 "loneliness",
                 "ncigs",
                 'nutrition_quality'
)
aggr.labels <- c("SF-12 MCS",
                 "NSSEC",
                 "Education State",
                 "Labour State", 
                 "Ethnicity", 
                 "Household Income",
                 "Neighbourhood Safety",
                 "Loneliness",
                 "Number of cigarettes",
                 'Nutrition Quality'
)

# Create aggr plot for missing data structure.
mice.missingness.structure.aggr.plot(mice.data, save.path, aggr.columns, "figure_5a_total_missingness_structure1.pdf")

# Defining columns that are IMPUTED in MICE imputation.
imp.columns <- c("SF_12_MCS",
                 'sex',
                 "NSSEC",
                 "education_state",
                 "labour_state", 
                 "region", 
                 "ethnicity", 
                 "age", 
                 "time", 
                 "hh_income",
                 "housing_quality",
                 "neighbourhood_safety",
                 "loneliness",
                 "ncigs",
                 'nutrition_quality'
)

# Defining all columns used in MICE imputation. Not all columns are imputed. All columns are used to predict imputed values.
mice.columns <- c("age", 
                  "region", 
                  "NSSEC", 
                  "ncigs",
                  "education_state",            
                  "ethnicity",
                  "loneliness",
                  "sex", 
                  "SF_12_MCS",
                  "nkids",       
                  "behind_on_bills",
                  "financial_situation",
                  "future_financial_situation",
                  "likely_move",
                  "ghq_depression",
                  "ghq_happiness",
                  "clinical_depression", 
                  "scsf1",
                  "health_limits_social",
                  "housing_quality",
                  "hh_income",
                  "neighbourhood_safety",
                  "labour_state",
                  "nutrition_quality"
)

# Categorical variables must be declared for the MICE package to work.
mice.data$ethnicity <- factor(mice.data$ethnicity)
mice.data$region <- factor(mice.data$region)
mice.data$NSSEC <- factor(mice.data$NSSEC)
mice.data$education_state <- factor(mice.data$education_state)
mice.data$loneliness <- factor(mice.data$loneliness)
mice.data$ethnicity <- factor(mice.data$ethnicity)
mice.data$sex <- factor(mice.data$sex)

mice.data$ghq_happiness <- factor(mice.data$ghq_happiness)
mice.data$ghq_depression <- factor(mice.data$ghq_depression)
mice.data$clinical_depression <- factor(mice.data$clinical_depression)
mice.data$scsf1 <- factor(mice.data$scsf1)
mice.data$health_limits_social <- factor(mice.data$health_limits_social)
mice.data$housing_quality <- factor(mice.data$housing_quality)
mice.data$loneliness <- factor(mice.data$loneliness)
mice.data$neighbourhood_safety <- factor(mice.data$neighbourhood_safety)
mice.data$labour_state <- factor(mice.data$labour_state)


# MICE imputation is time intensive. This option allows for reloading previous MICE imputation for faster plotting.
# Setting this to F means results will take at least a day for these parameters on a local machine.
load.cache <- T # load cached data?
n.populations <- 10 # number of imputed populations.
max.mice.iterations.per.population <- 10 # mice iterations per imputed population.

# if loading cached mice data check it exists. if it doesn't exist cannot use cache.
if (load.cache) { # check for saved MICE data. if cached data doesn't exist force MICE algorihtm to be run.
  if (!file.exists("data/transitions/imputed_mice_populations.rds")) {
    load.cache <- F
  }
}

# -either load cached mice data or run MICE from scratch.
  if (load.cache) {
  imputed.mice.populations <- readRDS("data/transitions/imputed_mice_populations.rds")
  if ("SF_12" %in% names(imputed.mice.populations$data)){
    names(imputed.mice.populations$data)[names(imputed.mice.populations$data) == 'SF_12'] <- 'SF_12_MCS'
  }
} else {
  # Number of mice imputations and number of imputation steps per population.
  # run MICE algorithm.
  imputed.mice.populations <- mice(data = mice.data[mice.data$time %in%  seq(2011, 2018), mice.columns],
                   m = n.populations, maxit = max.mice.iterations.per.population,
                   remove.collinear=T)
  
  # future mice is parallelised version of MICE. useful on multi-core machines but uses a lot of resources.
  #imputed.mice.populations <- futuremice(data = mice.data[, mice.columns], #method=method,
  #                m = n.populations, maxit = max.mice.iterations.per.population,
  #                 remove.collinear=T, quiet=F,
  #                 progressor = progressr::handlers("progress"))
  
  # save MICE data for caching later.
  create.if.not.exists(here::here("data", "transitions"))
  saveRDS(imputed.mice.populations, here::here("data", "transitions", "imputed_mice_populations.rds"))
}

```

This section applies the OLS SF-12 MCS model to all 30 MICE imputed populations. 
These 30 models are pooled together producing a final set of model coefficients estimating SF-12 MCS.
Diagnostic plots assessing MICE convergence and model goodness of fit are also provided.

```{r Formatting MICE data., echo=FALSE, warning=FALSE}

# Extract imputed data from mids object produced by MICE() function.
# Attach other variables needed for model including personal/household identifiers (pidp/hidp), sample weights and time that aren't imputed.
mice.populations.long <- complete(imputed.mice.populations, action = "long", include=T) 

# Reassign variables that could not be imputed. Weights and IDs.
mice.populations.long$pidp <- mice.pidp
mice.populations.long$hidp <- mice.hidp
mice.populations.long$weight <- mice.weights
mice.populations.long$time <- mice.time
mice.populations.long <- update.column.names(mice.populations.long)

# Looking at data from 2011-2013 only. Data used in baseline model for direct comparison.
mice.populations.long.subset <- mice.populations.long[mice.populations.long$time %in% c(2011, 2012, 2013), ]
# MICE doesn't like completely empty loneliness column in base data so giving it a dummy column. Not used in any validation.
mice.populations.long.subset[which(mice.populations.long.subset$.imp==0),"loneliness"] <- mice.populations.long.subset[which(mice.populations.long.subset$.imp==2), "loneliness"]
# Cast back to MIDS for pooling.
imputed.mice.populations.subset <- as.mids(mice.populations.long.subset) 
```

```{r MICE Diagnostics., echo=FALSE, warning=FALSE}

# Make MICE convergence plot. checking variance and mean SF-12 MCS values for each imputed population and MICE iteration for stability.
mice.convergence.trace.plot(imputed.mice.populations, save.path, "figure_5b_ols_mice_convergence.pdf")

# Fit OLS model to all 30 MICE populations and pool together into one model.
mice.sf12.mcs.ols <- with(imputed.mice.populations.subset, lm(as.formula(mice.formula.string)))
final.sf12.mcs.mice.pool<- pool(mice.sf12.mcs.ols)

# Summary statistics for the pooled OLS model.
pooled.sf12.mcs.mice.ols <- mice.sf12.mcs.ols$analyses[[1]]
pool.sum <- summary(final.sf12.mcs.mice.pool)
pooled.sf12.mcs.mice.ols$coefficients = pool.sum$estimate
mice.preds<- predict(pooled.sf12.mcs.mice.ols)
pool.r.squared(final.sf12.mcs.mice.pool) # getting r squared.

# mids object can't make most of the summary plots needed.
# Cast mids object to an lm predict object.
# Use a dummy lm model and overwrite model coefficients, standard errors, and t/p values.
mice.lm.object <- summary(lm(mice.formula.string, data = complete(imputed.mice.populations.subset)))
mice.lm.object$coefficients[,1] <- pool.sum$estimate
mice.lm.object$coefficients[,2] <- pool.sum$std.error
mice.lm.object$coefficients[,3] <- pool.sum$statistic
mice.lm.object$coefficients[,4] <- pool.sum$p.value

# making forest plots and qq plot for MICE model diagnostics.
mice.ols.sf12.mcs.forest.plot(mice.lm.object, paste0(save.path,'figure_5c_mice_SF12_forest.pdf'))
qq.plot(resid(mice.lm.object), paste0(save.path, "figure_5d_mice_qq.pdf"))
SF12.MCS.OLS.MICE.make.latex.tables(final.sf12.mcs.mice.pool)

rm(pooled.sf12.mcs.mice.ols)
```

# Section 5: Validation and Uncertainty

This section describes how the OLS model is validated as well as methods for testing uncertainty due to missing data and model coefficients.

This section applies five fold cross validation to the OLS model using MICE imputed data. This model is used to forecast from 2013-2020 comparing model output against real data using 'nowcasting'.

## Uncertainty due to calibration data.

```{r MICE Cross-Validation and Nowcasting., echo=FALSE, warning=FALSE}
# Required mean and variances of sf-12 ms for scaling later.
mice.sf12.mcs.mean <- mean(log(complete(imputed.mice.populations, 1)$SF_12_MCS+10))
mice.sf12.mcs.std <- sqrt(var(log(complete(imputed.mice.populations, 1)$SF_12_MCS+10)))

# Apply five fold cross-validation to the OLS model using MICE data.
mice.cross.val.sf12.mcs.model <- train(as.formula(mice.formula.string), data = complete(imputed.mice.populations.subset, 1, include=F),
               method = "lm",
               trControl = trControl)

# calculating RMSE mean and variance for five cross validation folds.
mice.RMSE.statistics <- mice.cross.val.sf12.mcs.model$pred %>% 
  group_by(Resample) %>%
  mutate(obs =  exp(mice.sf12.mcs.std * obs + mice.sf12.mcs.mean) - 10) %>%
  mutate(pred =  exp(mice.sf12.mcs.std * pred + mice.sf12.mcs.mean) - 10) %>%
  summarise(output.RMSE=caret::RMSE(pred, obs)) %>%
  summarise(mean = mean(output.RMSE), std = sd(output.RMSE))

print("MICE RMSE Statistics: ")
print(mice.RMSE.statistics$mean)
print(mice.RMSE.statistics$std)

# Saving cross-validation OLS model coefficients.
sf12.mcs.ols.crossval.coefficients(mice.cross.val.sf12.mcs.model)

# Performing nowcasting use MICE model.
# Process MICE imputed data so it can be run using the lm predict function.
# Allows nowcasting to be performed.
crossval.mice.data <- complete(imputed.mice.populations.subset, 1, include = F)
crossval.mice.data <- replace.missing(crossval.mice.data)
crossval.mice.data <- drop_na(crossval.mice.data)
crossval.mice.data <- update.column.names(crossval.mice.data)
crossval.mice.data <- crossval.mice.data[which(crossval.mice.data$time==2013),]
  
# Use the cross-validted OLS model to perform nowcasting from 2013 to 2020.
start.data <- crossval.mice.data
rolling.data <- start.data
handover.data <- rolling.data[, c("pidp", "hidp", "SF_12_MCS", "time")]

for (i in 1:8){
  rolling.data$SF_12_MCS <- exp(mice.sf12.mcs.mean + mice.sf12.mcs.std * predict(mice.cross.val.sf12.mcs.model, rolling.data))-10
  rolling.data$SF_12_MCS  <- rolling.data$SF_12_MCS
  rolling.data[, 'time'] <- rolling.data[, 'time'] +1
  handover.data <- rbind(handover.data, rolling.data[, c("pidp", 'hidp', "SF_12_MCS", "time")])
}

# Plot nowcasting results using density ridges and boxplots.
handover.boxplots(mice.data[which(mice.data$time>=2014),], handover.data, "SF_12_MCS", save.path, "figure_6b_crossval_sf12_mcs_mice_validation_ridges_boxplots")
#density.ridges(mice.data[which(mice.data$time>=2014),], "SF_12_MCS", save=TRUE, save.path=save.path, filename.tag = "figure_6a_crossval_mice_raw_ridges")
density.ridges(handover.data[which(handover.data$time>=2014),], "SF_12_MCS", save=TRUE, save.path=save.path, filename.tag = "figure_6a_crossval_sf12_mcs_mice_validation_ridgelines")

rm(handover.data, rolling.data, start.data)
# setting dummy data for loneliness column to NA again.. Needed? 
#imputed.mice.populations.subset$data$loneliness<-NA
```

## Uncertainty due to model coefficients

This section tests OLS model uncertainty due to model coefficients. Model coefficients are randomly sampled from a multi-variate Normal distribution. 
Multiple randomised models are used to predict SF-12 MCS and compared to determine any significant differences.

```{r OLS Model With Randomised Coefficients., echo=FALSE, warning=FALSE}

# Get OLS prediction using MICE imputed data. Fitting as OLS model. 
# Use this model and randomise its coefficients to test for stability.
randomised.mice.model.data <- data.frame()
random.mice.lm.object <- lm(mice.formula.string, data = complete(imputed.mice.populations.subset, 1))

# Randomise model coefficients 100 times and predict SF-12 MCS scores. Looking for any variance in prediction due to randomised coefficients.
for (i in 1:100) {
  # Randomise OLS model coefficients using multivariate random Normal sampling from MASS package.
  model.choice <- random.mice.lm.object
  model.choice$coefficients <- MASS::mvrnorm(n=1, mu=mice.lm.object$coefficients[, 1], Sigma=vcov(mice.lm.object))

  # Perform nowcasting from 2013-2020 using randomised coefficients model and understanding society data.
  random.start.data <- crossval.mice.data
  for (j in 1:7){
    random.start.data$SF_12_MCS <- exp(mice.sf12.mcs.mean + mice.sf12.mcs.std *predict(model.choice, random.start.data))-10
  }
  
  # Estimate SF-12 MCS distribution in 2020 for each randomised model using kernel density estimation.
  individual.density <- density(random.start.data$SF_12_MCS)
  new.data.frame <- cbind(individual.density$x, individual.density$y, i)
  colnames(new.data.frame) <- c("SF_12_MCS", "Density", "run_id")
  
  # Stored SF-12 MCS density estimates for each set of randomised coefficients.
  # Produces 100 KDE curves plotted together to look for any areas where prediction is sensetive to randomised coefficients.
  randomised.mice.model.data <- rbind(randomised.mice.model.data, new.data.frame)

}

# Plot SF-12 MCS predicted distributions for each of the 100 models with randomised coefficients.
sf12.mcs.randomised.coefficients.plot(randomised.mice.model.data, save.path, "figure_7_randomised_coefficients_2020_density.pdf")

rm(crossval.mice.data, random.start.data, randomised.mice.model.data)
```


## Uncertainty due to model variables using LASSO variable selection.

Model coefficients are tested further using variable selection. The least absolute shrinkage and selection operator (LASSO) method is used to 
identify any model coefficients used in the OLS model that are not statistically significant and could be removed to create a more parsimonious model.

```{r OLS Model LASSO Variable Selection., echo=FALSE, warning=FALSE}

# Format MICE data to work with glmnet package.
lasso.data <- tidyr::drop_na(complete(imputed.mice.populations.subset))
X <- model.matrix(as.formula(mice.formula.string), data=lasso.data)
y <- lasso.data$SF_12_MCS
weight <- lasso.data$weight

# Apply cross-validated LASSO algorithm.
sf12.mcs.cv.lasso <- cv.glmnet(X, y, family = "gaussian", weights = weight)

# Plotting optimal parameter choice for the LASSO using cross-validation using 1se and minimum error rules.
sf12.mcs.cv.lasso.plot(sf12.mcs.cv.lasso, save.path,'figure_8_ols_cv_lasso_2013.pdf')

# plot cross-validation diagnostic.
plot(sf12.mcs.cv.lasso, xlab="L1 Regularisation Constraint (log(lambda))", ylab="Mean Squared Error") # run twice so prints to notebook.

# Get two sets of coefficients chosen using minimum error and 1 standard error rules.
lasso.min.coefs <- coef(sf12.mcs.cv.lasso, s=sf12.mcs.cv.lasso$lambda.min)
lasso.min.coefs <- lasso.min.coefs[-c(2),] # remove weird bug where intercept printed twice.
lasso.1se.coefs <- coef(sf12.mcs.cv.lasso, s=sf12.mcs.cv.lasso$lambda.1se)
lasso.1se.coefs <- lasso.1se.coefs[-c(2),] # remove weird bug where intercept printed twice.
lasso_model_names <- c("Minimum Error", "First Standard Error") # Label coefficient sets.

# saving coefficients to latex table.
sf12.mcs.lasso.coefficients.table(lasso.min, lasso.1se, lasso.min.coefs, lasso.1se.coefs)
rm(lasso.data, X, y)
```

## Uncertainty due to sample weights using extrapolated weights 

This section explores application of sample weights in the OLS model using sample weights from different years of Understanding Society data to determine
any difference in model structure and prediction. 
The aim is to determine if model coefficients change over time due to change in demographics reflected in sample weights.
Weighted regressions are compared using 2013 sample weights, 2013 sample weights projected to 2018, and 2018 sample weights.

```{r Weighted OLS model., echo=FALSE, warning=FALSE}

# Get 2016-2018 Understanding Society MICE imputed data. Assign standard Understanding society sample weights.
imputed.mice.populations.subset.2016.2018 <- mice.populations.long[which(mice.populations.long$time %in% c(2016, 2017, 2018)), ]
imputed.mice.populations.subset.2016.2018 <- as.mids(imputed.mice.populations.subset.2016.2018)

# Get 2011-2013 sample weights projected into 2016-2018 using cell-based reweighting.
# Reweighting done on age, sex, and ethnicity based on data from Office for National Statistics midyear demographic estimates.
extrapolated.weights.filelist <- list.files("data/extrapolated_weights/",
                       include.dirs = FALSE,
                       full.names = TRUE,
                       pattern = 'extrapolated_weights_data_[0-9]{4}.csv')[1:3]# get files for 2016-2018.

# Add extrapolated 2016-2018 extrapolated weights to 2011-2013 MICE data. 
# Comparing differences between OLS models fitted using real UKHLS data and sample weights from 2016-2018
# versus model using 2011-2013 data but with 2016-2018 projected sample weights.
# Curious if these two models have similar coefficients or if reweighting alone is insufficient for using 2011-2013 model to predict 2016-2018 states.

extrapolated.weights.data <- do.call(rbind, lapply(extrapolated.weights.filelist, read.csv))
extrapolated.weights.data <- replace.missing(extrapolated.weights.data)
extrapolated.weights <- extrapolated.weights.data[, c("plus_5_weight")]
imputed.mice.populations.subset.2011_2013.updated.weights <- mice.populations.long.subset
imputed.mice.populations.subset.2011_2013.updated.weights$weight <- extrapolated.weights
imputed.mice.populations.subset.2011_2013.updated.weights <- as.mids(imputed.mice.populations.subset.2011_2013.updated.weights)

rm(extrapolated.weights.data)
rm(mice.populations.long, mice.populations.long.subset)
```


More weighted regression using MICE pooled data.
Producing LATEX table comparing OLS model coefficients using different sample weights.

```{r Saving Weighted Regression Models., echo=FALSE, warning=FALSE}

# Fit linear regression on 2011-2013 MICE data using 2011-2013 and 2016-2018 extrapolated weights to compare any differences between models.
# weighted regression for 2016-2018 using 2011-2013 models and projected weights
sf12.mcs.ols.weighted.2013 <- pool(with(imputed.mice.populations.subset.2011_2013.updated.weights, lm(as.formula(mice.formula.string), weights = weight)))

#  weighted regression for 2016-2018 using 2018 data.
sf12.mcs.ols.weighted.2018 <- pool(with(imputed.mice.populations.subset.2016.2018, lm(as.formula(mice.formula.string), weights = weight)))

# Print models to latex tables.
sf12.mcs.weighted.ols.latex.coefficients.table(sf12.mcs.ols.weighted.2013, sf12.mcs.ols.weighted.2018)

rm(imputed.mice.populations.subset.2011_2013.updated.weights, imputed.mice.populations.subset.2016.2018)
```

# Section 6: Heterogeneity using Generalised Linear Mixed models.

This section aims to estimate longitudinal heterogeneity within individuals over time using generalised linear mixed modelling.
A GLMM model using individual person random intercepts is fitted and assessed using model diagnostics from previous uncertainty and presentation sections.

This model is assessed using repeated diagnostic plots and cross-validation methods. 

```{r Generalised Linear Mixed Model., echo=FALSE, warning=FALSE}

# Preprocessing MICE data to use in GLMM.
# Getting mice data for preprocessing and use in GLMM.
glmm.mice.populations.long.subset <- complete(imputed.mice.populations.subset, "long", include=T)
rm(imputed.mice.populations.subset)

# reflecting SF-12 MCS to be right skewed so can be modelled using gamma glmm.
reflect <- T
if (reflect) {
    max.sf12.mcs.value <- nanmax(mice.data$SF_12_MCS)
    glmm.mice.populations.long.subset$SF_12_MCS <- max.sf12.mcs.value - glmm.mice.populations.long.subset$SF_12_MCS + 0.001
  }

# Order MICE data by time. Add lagged dependent SF-12 MCS variable. Take 2011-2013 data.
glmm.mice.populations.long.subset <- glmm.mice.populations.long.subset %>%
           group_by(pidp) %>%
            mutate(last = lag(.data[["SF_12_MCS"]], order_by = time)) %>%
            rename_with(.fn = ~paste0('SF_12_MCS_', .), .cols = last)  # add the dependent as prefix to the calculated diff
glmm.mice.populations.long.subset <- glmm.mice.populations.long.subset[glmm.mice.populations.long.subset$time %in% c(2011, 2012, 2013), ]

# ARE THESE NEEDED?
#glmm.mice.populations.long.subset$.imp <- as.numeric(glmm.mice.populations.long.subset$.imp)
#glmm.mice.populations.long.subset <- as.data.frame(glmm.mice.populations.long.subset)
glmm.mice.set <- as.mids(glmm.mice.populations.long.subset)

# define GLMM model formula
sf12.mcs.glmm.model.formula.string <- "I(log(SF_12_MCS+10)) ~ I(log(SF_12_MCS_last)+10) +
                  factor(sex) + 
                  relevel(factor(ethnicity), ref='WBI') + 
                  scale(age) + 
                  factor(education_state) + 
                  factor(labour_state) + 
                  relevel(factor(NSSEC), ref='1') +
                  relevel(factor(region), ref='London') +
                  scale(hh_income) + 
                  I(scale(hh_income**2)) +
                  relevel(factor(housing_quality), ref='Low') +
                  factor(neighbourhood_safety) +
                  factor(loneliness) + 
                  nutrition_quality + 
                  ncigs + time +
                  (1|pidp)"

# apply GLMM to pooled MICE data.
sf12.glmm.model <- with(glmm.mice.set, glmer(sf12.mcs.glmm.model.formula.string,  
               nAGQ=0, # fast but inaccurate optimiser. nAGQ=1 takes a few weeks.
               family=Gamma(link='log')#, weights=weight# gamma family with log link. no weights for MICE sample.
               ))

# pool GLMM SF-12 MCS model results.
sf12.glmm.pool <- pool(sf12.glmm.model)

# Print GLMM latex coefficients table.
sf12.mcs.glmm.coefficients.latex.table(sf12.glmm.pool)

# Get Nakagawa R-squared for GLMMs.
print(r2_nakagawa(sf12.glmm.model$analyses[[1]]))

# Cast MICE mids object to nlmer predict object allowing for diagnostic plots.
mice.glmm.object <- sf12.glmm.model$analyses[[1]]
mice.glmm.object@beta <- sf12.glmm.pool$pooled$estimate

# Transform SF-12 MCS data back to correct distribution scale for diagnostic plots.
glmm.fitted <-  max.sf12.mcs.value - (exp(predict(mice.glmm.object, type='response')) - 10)
```

```{r GLMM Diagnostics., echo=FALSE, warning=FALSE}
# Make GLMM diagnostic plots. 
# Forest coefficient plot. note flipping coefficients required for reflected data.
# Allows coefficients to align with results from previous models.
mice.glmm.object@beta <- - mice.glmm.object@beta # flip coefficients due to flipped SF-12 MCS variable.
gamma.forest.plot(mice.glmm.object, save.path, paste0(save.path, "figure_9a_sf12_mcs_glmm_forest.pdf"))
mice.glmm.object@beta <- - mice.glmm.object@beta # flip coefficients back after plotting diagnostics so can use in handovers. 

# QQ and residual density plots testing normality of residuals.
qq.plot(scale(residuals(mice.glmm.object, type='deviance')), paste0(save.path, "figure_9c_sf12_mcs_glmm_qq.pdf")) # also have pearson type residuals.
residual.density.plot(res=residuals(mice.glmm.object) , plot.file.name=paste0(save.path, "figure_9b_sf12_mcs_glmm_residual_density.pdf"), guide="normal")

# Scale-location plot testing fitted vs residual values for homoscedasticity. Need to do manually for GLMM model as not built in like for OLS.
squareRootRes <- sqrt(residuals(mice.glmm.object, type='pearson')**2)
fitted.residuals <- as.data.frame(cbind(glmm.fitted, squareRootRes))
colnames(fitted.residuals) <- c("fitted", "sqrt_residuals")
fitted.residual.plot(fitted.residuals, paste0(save.path, "figure_9d_sf12_mcs_glmm_scale_location_plot.pdf"))
rm(fitted.residuals, squareRootRes)
```

Performing nowcasting using the updated GLMM model.

```{r GLMM Nowcasting., echo=FALSE, warning=FALSE}
# Process MICE data for nowcasting by removing incomplete rows.
# Get 2013 start data for nowcasting. 
start.data <- complete(glmm.mice.set, 1)
start.data <- start.data[which(start.data$time==2013),]
start.data$SF_12_MCS <- max.sf12.mcs.value - start.data$SF_12_MCS
start.data$SF_12_MCS_last <- max.sf12.mcs.value - start.data$SF_12_MCS_last 
handover.data <- start.data
rolling.data <- start.data

# Perform nowcasting from 2013-2021 for SF-12 MCS using GLMM model.
for (i in 1:8){
  rolling.data$SF_12_MCS <- max.sf12.mcs.value - rolling.data$SF_12_MCS
  rolling.data$SF_12_MCS_last <- max.sf12.mcs.value - rolling.data$SF_12_MCS_last 

  rolling.data$SF_12_MCS <- (exp(predict(mice.glmm.object, rolling.data, type='response',allow.new.levels=T))-10)
  rolling.data$SF_12_MCS <- max.sf12.mcs.value - rolling.data$SF_12_MCS
  rolling.data[which(rolling.data$SF_12_MCS < 0), "SF_12_MCS"] <- 0
  rolling.data[which(rolling.data$SF_12_MCS > 100), "SF_12_MCS"] <- 100
  rolling.data[, 'time'] <- rolling.data[, 'time'] + 1
  handover.data <- rbind(handover.data, rolling.data)
  
  rolling.data$SF_12_MCS_last <- rolling.data$SF_12_MCS
}

# Plot nowcasting results in boxplots/ridgeline plots.
handover.boxplots(mice.data[which(mice.data$time>= 2013),], handover.data, "SF_12_MCS", save.path, "figure_10b_glmm_SF_12_MCS_boxplot")
density.ridges(mice.data[which(mice.data$time>= 2013),], "SF_12_MCS", save=TRUE, save.path=save.path, filename.tag = "figure_4a_ols_real_SF_12_MCS_ridges")
density.ridges(handover.data, "SF_12_MCS", save=TRUE, save.path=save.path, filename.tag = "figure_10a_glmm_handover_ridges")

rm(handover.data, start.data, rolling.data)
```

Five-fold cross-validation applied to GLMM model estimating final RMSE score.

```{r GLMM Cross-Validation., echo=FALSE, warning=FALSE}

# Function needed to apply GLMM using five fold cross-validation and print Nakagawa R-squared.
fit.glmm.to.each.fold <- function(mice.fold.data) {
  sf12.glmm.model <- with(mice.fold.data, glmer(sf12.mcs.glmm.model.formula.string,  
               nAGQ=0, # fast but inaccurate optimiser. nAGQ=1 takes forever..
               family=Gamma(link='log')#, weights=weight# gamma family with log link.
               ))
  
  sf12.glmm.pool <- pool(sf12.glmm.model)
  
  # mice objects dont go in forest plot annoyingly. move coefficients over to a
  # dummy lm that sjPlot::plot_models can read.
  mice.glmm.object <- sf12.glmm.model$analyses[[1]]
  mice.glmm.object@beta <- sf12.glmm.pool$pooled$estimate
  # give nakagawa r squared.
  print(r2_nakagawa(sf12.glmm.model$analyses[[1]]))
  return(mice.glmm.object)
}

#split mice sets into 5 based on pidps
pidps <- unique(mice.pidp)
glmm.cross.folds <- 5
pidp.chunks <- groupKFold(pidps, k=glmm.cross.folds)
rmse.glmm.values <- c()

for (j in 1:glmm.cross.folds)
{
 pidp.chunks.sample <- unique(pidps[pidp.chunks[[j]]])
 glmm.mice.populations.long.subset.fold <- filter(glmm.mice.populations.long.subset, !pidp %in% pidp.chunks.sample)
 glmm.mice.set.fold <- as.mids(glmm.mice.populations.long.subset.fold)
 sf12.glmm.fold <- fit.glmm.to.each.fold(glmm.mice.set.fold)
 glmm.mice.populations.long.subset.test <- drop_na(filter(glmm.mice.populations.long.subset, pidp %in% pidp.chunks.sample))
 glmm.fold.RMSE <- caret::RMSE(max.sf12.mcs.value - exp(predict(sf12.glmm.fold, glmm.mice.populations.long.subset.test, type='response', allow.new.levels=T)) + 10,
                max.sf12.mcs.value - glmm.mice.populations.long.subset.test$SF_12_MCS) #replace with CARET::RMSE
 rmse.glmm.values[j] <- glmm.fold.RMSE
}

print(mean(rmse.glmm.values))
print(sd(rmse.glmm.values))
rm(glmm.mice.set.fold, sf12.glmm.fold, glmm.mice.populations.long.subset.fold, glmm.mice.populations.long.subset.test, pidp.chunks, pidp.chunks.sample)
```