---
title: "MINOS Debug"
output: html_notebook
---


# Setup

```{r "setup", include=FALSE}

require(tidyverse)
require(ggplot2)
require(purrr)

workingDir <- "/home/luke/Documents/WORK/MINOS/"
knitr::opts_knit$set(root.dir = workingDir)
rm(workingDir)
```

Source utils for some functions.
```{r}
source('R_Scripts/utils.r')
```


Set up all the paths for the output directories and load in all waves of a single year of data.

```{r}
output.path <- 'Minos/output/default_config/'

baseline.path <- paste0(output.path, 'baseline')
allchild.path <- paste0(output.path, 'hhIncomeChildUplift')
povertychild.path <- paste0(output.path, 'hhIncomePovertyLineChildUplift')

# Handle the runtime subdirectory by selecting the most recent (utils.R func) 
base.path <- get_runtime_subdirectory(baseline.path)
#base.path <- baseline.path
```


```{r}
# Read scot datafiles in
scot.files <- list.files('/home/luke/Documents/WORK/MINOS/Minos/data/scotland_US/', full.names = TRUE)
scot.dat <- do.call(rbind, lapply(scot.files, read.csv))

# Replenishing data
#repl <- read.csv('/home/luke/Documents/WORK/MINOS/Minos/data/replenishing/replenishing_pop_2019-2070.csv')
#repl <- read.csv('/home/luke/Documents/WORK/MINOS/Minos/data/replenishing/replenishing_pop_2019-2070.csv')


# read in all the output data files
base.files <- list.files(base.path,
                         pattern = '[0-9]{4}.csv',
                         full.names = TRUE)
data <- do.call(rbind, lapply(base.files, read.csv))
```

## Input data files
```{r}
# Read raw datafiles in
raw.files <- list.files('/home/luke/Documents/WORK/MINOS/Minos/data/stock/', full.names = TRUE)
raw.dat <- do.call(rbind, lapply(raw.files, read.csv))

# Replenishing data
repl <- read.csv('/home/luke/Documents/WORK/MINOS/Minos/data/replenishing/replenishing_pop_2019-2070.csv')
```


# REPLENISHING

## EDUCATION
```{r}
# plot counts of each state over time (will only change with the replenishing but good to see)
educ.state <- repl %>% 
  group_by(time, education_state) %>%
  count()

# set column types
educ.state$education_state <- as.factor(educ.state$education_state)

ggplot(data = educ.state, mapping = aes(x = education_state, y = n, fill=education_state)) +
  geom_col(position='dodge')
```
## Ethnicity
```{r}
# plot counts of each state over time (will only change with the replenishing but good to see)
ethnic.state <- repl %>% 
  group_by(time, ethnicity) %>%
  count()

# set column types
ethnic.state$ethnicity <- as.factor(ethnic.state$ethnicity)

ggplot(data = ethnic.state, mapping = aes(x = ethnicity, y = n, fill=ethnicity)) +
  geom_col(position='dodge')

ggplot(data = filter(ethnic.state, ethnicity != 'WBI'), mapping = aes(x = ethnicity, y = n, fill=ethnicity)) +
  geom_col(position='dodge')
```


# MODEL OUTPUT

## Handovers

First get the final_US data, and baseline output.
```{r}
# Read raw datafiles in
raw.files <- list.files('/home/luke/Documents/WORK/MINOS/Minos/data/final_US/', full.names = TRUE)
raw.dat <- do.call(rbind, lapply(raw.files, read.csv))

base.path <- 'Minos/output/default_config/baseline/'
base.path <- get_runtime_subdirectory(base.path)
#base.testpath <- 'tmp/test_out/baseline/'
base.files <- list.files(base.path,
                         pattern = '[0-9]{4}.csv',
                         full.names = TRUE)
base.dat <- do.call(rbind, lapply(base.files, read.csv))
```

Now we want to plot these against the output data, so it would be useful to create a generic function that would do it for us. Something that accepts both final_US data and output as an argument, meaning we can do all the loading and processing of outputs before the function call. Saves repeated code and means we can stick it in the utils for later.

```{r}
raw.income <- raw.dat %>% 
  select(pidp, time, hh_income, weight) %>%
  group_by(time) %>%
  summarise(income = weighted.mean(hh_income, weight)) %>%
  mutate(source = 'final_US')

raw.income


test <- raw.dat %>%
  select(pidp, time, hh_income, weight)

test

#base.income <- base.dat %>%
#  select(pidp, time, hh_income, weight) %>%
#  group_by(time) %>%
#  summarise(income = weighted.mean(hh_income, weight, na.rm = TRUE)) %>%
#  mutate(source = 'baseline_output')#

#base.income
```


### Income
```{r}
# first figure out how to plot final_US
# start with hh_income
raw.income <- raw.dat %>% 
  select(pidp, time, hh_income, weight) %>%
  group_by(time) %>%
  summarise(income = weighted.mean(hh_income, weight)) %>%
  mutate(source = 'final_US')

base.income <- base.dat %>%
  select(pidp, time, hh_income, weight) %>%
  group_by(time) %>%
  summarise(income = weighted.mean(hh_income, weight, na.rm = TRUE)) %>%
  mutate(source = 'baseline_output')

# merge before plot
income <- rbind(raw.income, base.income)

# Now plot
ggplot(data = income, mapping = aes(x = time, y = income, group = source, colour = source)) +
  geom_line() +
  geom_vline(xintercept=2018, linetype='dotted')

## Try a version where final_US is limited to only those present from wave 1 
# onwards because the sample refreshments are messing with the plot
raw.income.wave1 <- raw.dat$pidp[raw.dat$time == 2009]

raw.income2 <- raw.dat %>% 
  select(pidp, time, hh_income) %>%
  filter(pidp %in% raw.income.wave1) %>%
  group_by(time) %>%
  summarise(income = mean(hh_income, na.rm = TRUE)) %>%
  mutate(source = 'final_US')

base.income2 <- base.dat %>%
  select(pidp, time, hh_income) %>%
  filter(pidp %in% raw.income.wave1) %>%
  group_by(time) %>%
  summarise(income = mean(hh_income, na.rm = TRUE)) %>%
  mutate(source = 'baseline_output')

income2 <- rbind(raw.income2, base.income2)

# Now plot
ggplot(data = income2, mapping = aes(x = time, y = income, group = source, colour = source)) +
  geom_line() +
  geom_vline(xintercept=2018, linetype='dotted')

raw.income.check <- raw.dat %>% 
  select(pidp, time, hh_income) %>%
  filter(pidp %in% raw.income.wave1)

base.income.check <- base.dat %>%
  select(pidp, time, hh_income) %>%
  filter(pidp %in% raw.income.wave1)

#rm(raw.income, base.income, income, raw.income.wave1, raw.income2, base.income2, 
#   raw.income.check, base.income.check)
```

### SF12
```{r}
# first figure out how to plot final_US
# start with hh_income
raw.sf12 <- raw.dat %>% 
  select(pidp, time, SF_12_MCS) %>%
  group_by(time) %>%
  summarise(sf12 = mean(SF_12_MCS, na.rm = TRUE)) %>%
  mutate(source = 'final_US')

base.sf12 <- base.dat %>%
  select(pidp, time, SF_12_MCS) %>%
  group_by(time) %>%
  summarise(sf12 = mean(SF_12_MCS, na.rm = TRUE)) %>%
  mutate(source = 'baseline_output')

# merge before plot
sf12 <- rbind(raw.sf12, base.sf12)

# Now plot
ggplot(data = sf12, mapping = aes(x = time, y = sf12, group = source, colour = source)) +
  geom_line() +
  geom_vline(xintercept=2018, linetype='dotted')

## Try a version where final_US is limited to only those present from wave 1 
# onwards because the sample refreshments are messing with the plot
raw.sf12.wave1 <- raw.dat$pidp[raw.dat$time == 2009]

raw.sf12.2 <- raw.dat %>% 
  select(pidp, time, SF_12_MCS) %>%
  filter(pidp %in% raw.sf12.wave1) %>%
  group_by(time) %>%
  summarise(sf12 = mean(SF_12_MCS, na.rm = TRUE)) %>%
  mutate(source = 'final_US')

base.sf12.2 <- base.dat %>%
  select(pidp, time, SF_12_MCS) %>%
  filter(pidp %in% raw.sf12.wave1) %>%
  group_by(time) %>%
  summarise(sf12 = mean(SF_12_MCS, na.rm = TRUE)) %>%
  mutate(source = 'baseline_output')

sf12.2 <- rbind(raw.sf12.2, base.sf12.2)

# Now plot
ggplot(data = sf12.2, mapping = aes(x = time, y = sf12, group = source, colour = source)) +
  geom_line() +
  geom_vline(xintercept=2018, linetype='dotted')
```


### Housing Quality
```{r}
raw.housing <- raw.dat %>% 
  select(pidp, time, housing_quality) %>%
  group_by(time, housing_quality) %>%
  count() %>%
  mutate(source = 'final_US')

base.housing <- base.dat %>%
  select(pidp, time, housing_quality) %>%
  group_by(time, housing_quality) %>%
  count() %>%
  mutate(source = 'baseline_output')



# merge before plot
housing <- rbind(raw.housing, base.housing)
housing$housing_quality <- as.factor(housing$housing_quality)

# Now plot
ggplot(data = housing, mapping = aes(x = time, y = n, group = housing_quality, colour = housing_quality)) +
  geom_line() +
  geom_vline(xintercept=2018, linetype='dotted')

housing.norm <- housing %>%
  group_by(time) %>%
  mutate(total = sum(n)) %>%
  mutate(prct = (n / total))

ggplot(data = housing.norm, mapping = aes(x = time, y = prct, fill=housing_quality)) +
  geom_bar(stat = 'identity') +
  geom_vline(xintercept=2018, linetype='dotted')

rm(raw.housing, base.housing, housing, housing.norm)
```

### Neighbourhood Safety

```{r}
raw.neighbour <- raw.dat %>% 
  select(pidp, time, neighbourhood_safety) %>%
  group_by(time, neighbourhood_safety) %>%
  count() %>%
  mutate(source = 'final_US')

base.neighbour <- base.dat %>%
  select(pidp, time, neighbourhood_safety) %>%
  group_by(time, neighbourhood_safety) %>%
  count() %>%
  mutate(source = 'baseline_output')



# merge before plot
neighbour <- rbind(raw.neighbour, base.neighbour)
neighbour$neighbourhood_safety <- as.factor(neighbour$neighbourhood_safety)

# Now plot
ggplot(data = neighbour, mapping = aes(x = time, y = n, group = neighbourhood_safety, colour = neighbourhood_safety)) +
  geom_line() +
  geom_vline(xintercept=2018, linetype='dotted')

neighbour.norm <- neighbour %>%
  group_by(time) %>%
  filter(neighbourhood_safety != -9) %>%
  mutate(total = sum(n)) %>%
  mutate(prct = (n / total))

ggplot(data = neighbour.norm, mapping = aes(x = time, y = prct, fill=neighbourhood_safety)) +
  geom_bar(stat = 'identity') +
  geom_vline(xintercept=2018, linetype='dotted')

#rm(raw.neighbour, base.neighbour, neighbour, neighbour.norm)
```

### Loneliness

```{r}
raw.loneliness <- raw.dat %>% 
  select(pidp, time, loneliness) %>%
  group_by(time, loneliness) %>%
  count() %>%
  mutate(source = 'final_US')

base.loneliness <- base.dat %>%
  select(pidp, time, loneliness) %>%
  group_by(time, loneliness) %>%
  count() %>%
  mutate(source = 'baseline_output')



# merge before plot
loneliness <- rbind(raw.loneliness, base.loneliness)
loneliness$loneliness <- as.factor(loneliness$loneliness)

# Now plot
ggplot(data = loneliness, mapping = aes(x = time, y = n, group = loneliness, colour = loneliness)) +
  geom_line() +
  geom_vline(xintercept=2018, linetype='dotted')

loneliness.norm <- loneliness %>%
  group_by(time) %>%
  filter(loneliness != -9) %>%
  mutate(total = sum(n)) %>%
  mutate(prct = (n / total))

ggplot(data = loneliness.norm, mapping = aes(x = time, y = prct, fill=loneliness)) +
  geom_bar(stat = 'identity') +
  geom_vline(xintercept=2018, linetype='dotted')

rm(raw.loneliness, base.loneliness, loneliness, loneliness.norm)
```

### Nutrition Quality

TODO: Drop negative values ONLY from waves with no data i.e. not 7,9,11

```{r}
# first figure out how to plot final_US
# start with hh_income
raw.nut <- raw.dat %>% 
  select(pidp, time, nutrition_quality) %>%
  group_by(time) %>%
  summarise(nutrition_quality = mean(nutrition_quality, na.rm = TRUE)) %>%
  mutate(source = 'final_US')

base.nut <- base.dat %>%
  select(pidp, time, nutrition_quality) %>%
  group_by(time) %>%
  summarise(nutrition_quality = mean(nutrition_quality, na.rm = TRUE)) %>%
  mutate(source = 'baseline_output')

# merge before plot
nutrition_quality <- rbind(raw.nut, base.nut)

# Now plot
ggplot(data = nutrition_quality, mapping = aes(x = time, y = nutrition_quality, group = source, colour = source)) +
  geom_line() +
  geom_vline(xintercept=2018, linetype='dotted')

## Try a version where final_US is limited to only those present from wave 1 
# onwards because the sample refreshments are messing with the plot
raw.wave1 <- raw.dat$pidp[raw.dat$time == 2009]

raw.nut2 <- raw.dat %>% 
  select(pidp, time, nutrition_quality) %>%
  filter(pidp %in% raw.wave1) %>%
  filter(nutrition_quality >= 0) %>%
  group_by(time) %>%
  summarise(nutrition_quality = mean(nutrition_quality, na.rm = TRUE)) %>%
  mutate(source = 'final_US')

base.nut2 <- base.dat %>%
  select(pidp, time, nutrition_quality) %>%
  filter(pidp %in% raw.wave1) %>%
  group_by(time) %>%
  summarise(nutrition_quality = mean(nutrition_quality, na.rm = TRUE)) %>%
  mutate(source = 'baseline_output')

nutrition_quality2 <- rbind(raw.nut2, base.nut2)

# Now plot
ggplot(data = nutrition_quality2, mapping = aes(x = time, y = nutrition_quality, group = source, colour = source)) +
  geom_line() +
  geom_vline(xintercept=2018, linetype='dotted')

rm(raw.nut, base.nut, nutrition_quality, raw.wave1, raw.nut2, base.nut2, 
    nutrition_quality2)
```

### Physical Health

NOTE: At present, physical health is not predicted or transitioned.

```{r}
# first figure out how to plot final_US
# start with hh_income
raw.phealth <- raw.dat %>% 
  select(pidp, time, phealth) %>%
  group_by(time) %>%
  summarise(phealth = mean(phealth, na.rm = TRUE)) %>%
  mutate(source = 'final_US')

base.phealth <- base.dat %>%
  select(pidp, time, phealth) %>%
  group_by(time) %>%
  summarise(phealth = mean(phealth, na.rm = TRUE)) %>%
  mutate(source = 'baseline_output')

# merge before plot
phealth <- rbind(raw.phealth, base.phealth)

# Now plot
ggplot(data = phealth, mapping = aes(x = time, y = phealth, group = source, colour = source)) +
  geom_line() +
  geom_vline(xintercept=2018, linetype='dotted')

## Try a version where final_US is limited to only those present from wave 1 
# onwards because the sample refreshments are messing with the plot
raw.wave1 <- raw.dat$pidp[raw.dat$time == 2009]

raw.phealth2 <- raw.dat %>% 
  select(pidp, time, phealth) %>%
  filter(pidp %in% raw.wave1) %>%
  group_by(time) %>%
  summarise(phealth = mean(phealth, na.rm = TRUE)) %>%
  mutate(source = 'final_US')

base.phealth2 <- base.dat %>%
  select(pidp, time, phealth) %>%
  filter(pidp %in% raw.wave1) %>%
  group_by(time) %>%
  summarise(phealth = mean(phealth, na.rm = TRUE)) %>%
  mutate(source = 'baseline_output')

phealth2 <- rbind(raw.phealth2, base.phealth2)

# Now plot
ggplot(data = phealth2, mapping = aes(x = time, y = phealth, group = source, colour = source)) +
  geom_line() +
  geom_vline(xintercept=2018, linetype='dotted')

raw.phealth.check <- raw.dat %>% 
  select(pidp, time, phealth) %>%
  filter(pidp %in% raw.wave1)

base.phealth.check <- base.dat %>%
  select(pidp, time, phealth) %>%
  filter(pidp %in% raw.wave1)

rm(raw.phealth, base.phealth, phealth, raw.wave1, raw.phealth2, base.phealth2, 
   raw.phealth.check, base.phealth.check, phealth2)
```



## Demographics

### Age

DONE: Triple the number of 16 year olds in each replenishing cohort and look at this again.

TODO: Look at the leading cause of attrition - disease? older ages more likely?
In the raw data.


```{r}
# plot counts of each state over time (will only change with the replenishing but good to see)
age.state <- data %>% 
  group_by(time, age_bucket) %>%
  count()

# set column types
age.state$age_bucket <- as.factor(age.state$age_bucket)
age.state$time <- as.integer(age.state$time)

ggplot(data = age.state, mapping = aes(x = time, y = n, group = age_bucket, color = age_bucket)) +
  geom_line()
```

```{r}
age.state2 <- data %>% 
  group_by(time) %>%
  summarise(age = mean(age))

age.state2$time <- as.integer(age.state2$time)

ggplot(data = age.state2, mapping = aes(x = time, y = age)) +
  geom_line()

```

TODO: Look at average age at death

```{r}
died <- data %>% group_by(time, cause_of_death) %>%
  summarise(mean_age = mean(age))

ggplot(data = died, mapping = aes(x = time, y = mean_age, group = cause_of_death, color = cause_of_death)) +
  geom_line()
```

```{r, include=FALSE}
rm(age.state, age.state2, died)
```


### Sex

```{r}
# plot counts of each state over time (will only change with the replenishing but good to see)
sex.state <- data %>% 
  group_by(time, sex) %>%
  count()

# set column types
sex.state$sex <- as.factor(sex.state$sex)

ggplot(data = sex.state, mapping = aes(x = time, y = n, group = sex, color = sex)) +
  geom_line()
```
Product of mortality and replenishment - older age groups increase in number and women live longer than men.

### Education

TODO: Make this same plot for just the replenishing population, and see if they are the sole cause of the large increase in level 2 education. It could just be them, or it could also be that more people from other groups are dying. Need to find out regardless.

```{r}
# plot counts of each state over time (will only change with the replenishing but good to see)
educ.state <- data %>% 
  group_by(time, education_state) %>%
  count()

# set column types
educ.state$education_state <- as.factor(educ.state$education_state)

ggplot(data = educ.state, mapping = aes(x = time, y = n, group = education_state, color = education_state)) +
  geom_line()
```

See transition model summaries at the bottom for reference.

### Ethnicity

```{r}
# plot counts of each state over time (will only change with the replenishing but good to see)
ethnic.state <- data %>% 
  group_by(time, ethnicity) %>%
  count()

# set column types
ethnic.state$ethnicity <- as.factor(ethnic.state$ethnicity)

ggplot(data = ethnic.state, mapping = aes(x = time, y = n, group = ethnicity, color = ethnicity)) +
  geom_line()

ggplot(data = filter(ethnic.state, ethnicity != 'WBI'), mapping = aes(x = time, y = n, group = ethnicity, color = ethnicity)) +
  geom_line()
```

```{r}
# CLEANUP
#rm(age.state, educ.state, ethnic.state, sex.state)
```


## SF 12

```{r}
sf12 <- data %>% 
  select(pidp, time, SF_12_MCS)

# calculate and plot mean over time
sf12.byyr <- data %>% group_by(time) %>%
  summarise(SF_12_MCS = mean(SF_12_MCS))

ggplot(data = sf12.byyr, mapping = aes(x = time, y = SF_12_MCS)) +
  geom_line()
```

```{r}
# Lets overlay some histograms at 3 time points - 2018 (before model), 2020 (pathways kick in?), 2030 (long term)
sf12.2018 <- sf12 %>% filter(time == 2018)
sf12.2020 <- sf12 %>% filter(time == 2020)
sf12.2030 <- sf12 %>% filter(time == 2030)

sf12.joined <- rbind(sf12.2018, sf12.2020, sf12.2030)
sf12.joined$time <- as.factor(sf12.joined$time)

ggplot(data = sf12.joined, mapping = aes(x = SF_12_MCS, group = time, fill = time, color = time)) +
  geom_histogram(position='dodge')
```

TODO: Why are we getting the same exact values from 2020 - 2030?

```{r}
print("2018:")
sprintf("Min: %f", min(sf12.2018$SF_12_MCS))
sprintf("Max: %f", max(sf12.2018$SF_12_MCS))
sprintf("Mean: %f", mean(sf12.2018$SF_12_MCS))
print("2020:")
sprintf("Min: %f", min(sf12.2020$SF_12_MCS))
sprintf("Max: %f", max(sf12.2020$SF_12_MCS))
sprintf("Mean: %f", mean(sf12.2020$SF_12_MCS))
print("2030:")
sprintf("Min: %f", min(sf12.2030$SF_12_MCS))
sprintf("Max: %f", max(sf12.2030$SF_12_MCS))
sprintf("Mean: %f", mean(sf12.2030$SF_12_MCS))
```

## hh_income

TODO: PLOT THE RAW DATA!!!

```{r}
income <- data %>% 
  select(pidp, time, hh_income)

# calculate and plot mean over time
income.byyr <- data %>% group_by(time) %>%
  summarise(hh_income = mean(hh_income))

ggplot(data = income.byyr, mapping = aes(x = time, y = hh_income)) +
  geom_line()
```

Again lets try overlaid histograms to see distributions over time.

```{r}
# Lets overlay some histograms at 3 time points - 2018 (before model), 2020 (pathways kick in?), 2030 (long term)
income.2018 <- income %>% filter(time == 2018)
income.2020 <- income %>% filter(time == 2020)
income.2030 <- income %>% filter(time == 2030)

income.joined <- rbind(income.2018, income.2020, income.2030)

income.joined$time <- as.factor(income.joined$time)
income.joined$hh_income <- as.numeric(income.joined$hh_income)

ggplot(data = income.joined, mapping = aes(x = hh_income, group = time, fill = time, color = time)) +
  geom_histogram(bins = 50, position='dodge')
```


Check out the min/max for each time point, looks like it spreads out massively.
```{r}
print("2018:")
sprintf("Min: %f", min(income.2018$hh_income))
sprintf("Max: %f", max(income.2018$hh_income))
sprintf("Mean: %f", mean(income.2018$hh_income))
print("2020:")
sprintf("Min: %f", min(income.2020$hh_income))
sprintf("Max: %f", max(income.2020$hh_income))
sprintf("Mean: %f", mean(income.2020$hh_income))
print("2030:")
sprintf("Min: %f", min(income.2030$hh_income))
sprintf("Max: %f", max(income.2030$hh_income))
sprintf("Mean: %f", mean(income.2030$hh_income))
```


## Pathways

### ncigs

DONE: Fixed problem where the rescale factor was still being applied in prediction but not in the estimation of the model.
DONE: Fixed line in the r_utils prediction method where the non-smokers were being predicted as smokers.
TODO: Fix the input data issue where lots of these vars are being reported as missing still (negative numbers). This should be in the run script somewhere.

```{r}
ncigs <- data %>% 
  select(pidp, time, ncigs)

# calculate and plot mean over time
ncigs.byyr <- data %>% group_by(time) %>%
  summarise(ncigs = mean(ncigs))

ggplot(data = ncigs.byyr, mapping = aes(x = time, y = ncigs)) +
  geom_line()
```

```{r}
# Lets overlay some histograms at 3 time points - 2018 (before model), 2020 (pathways kick in?), 2030 (long term)
ncigs.2018 <- ncigs %>% filter(time == 2018)
ncigs.2020 <- ncigs %>% filter(time == 2020)
ncigs.2030 <- ncigs %>% filter(time == 2030)

ncigs.joined <- rbind(ncigs.2018, ncigs.2020, ncigs.2030)
ncigs.joined$time <- as.factor(ncigs.joined$time)

ggplot(data = ncigs.joined, mapping = aes(x = ncigs, group = time, fill = time, color = time)) +
  geom_histogram(position='dodge')
```

```{r}
# Lets also look at the number of smokers vs non-smokers
smokers.count <- ncigs %>% 
  group_by(time) %>%
  summarise(non.smoker = sum(ncigs == 0),
            smoker = sum(ncigs > 0)) %>%
  pivot_longer(cols = non.smoker:smoker,
               names_to = 'smoking_status',
               values_to = 'count')

ggplot(data = smokers.count, mapping = aes(x = time, y = count, group = smoking_status, color = smoking_status)) +
  geom_line()
```

### Housing Quality

```{r}
# plot counts of each state over time (will only change with the replenishing but good to see)
housing.state <- data %>% 
  group_by(time, housing_quality) %>%
  count()

# set column types
housing.state$housing_quality <- as.factor(housing.state$housing_quality)

ggplot(data = housing.state, mapping = aes(x = time, y = n, group = housing_quality, color = housing_quality)) +
  geom_line()
```

### Neighbourhood Safety

```{r}
# plot counts of each state over time (will only change with the replenishing but good to see)
neighbour.state <- data %>% 
  group_by(time, neighbourhood_safety) %>%
  count()

# set column types
neighbour.state$neighbourhood_safety <- as.factor(neighbour.state$neighbourhood_safety)

ggplot(data = neighbour.state, mapping = aes(x = time, y = n, group = neighbourhood_safety, color = neighbourhood_safety)) +
  geom_line()
```

### Loneliness

```{r}
# plot counts of each state over time (will only change with the replenishing but good to see)
loneliness.state <- data %>% 
  group_by(time, loneliness) %>%
  count()

# set column types
loneliness.state$loneliness <- as.factor(loneliness.state$loneliness)

ggplot(data = loneliness.state, mapping = aes(x = time, y = n, group = loneliness, color = loneliness)) +
  geom_line()
```

# TRANSITION MODEL SUMMARIES

```{r, include=FALSE}
trans.path <- 'Minos/data/transitions/'

educ.mod <- readRDS(paste0(trans.path, 'education_state/nnet/education_state_2018_2019.rds'))
sf_12.mod <- readRDS(paste0(trans.path, 'SF_12_MCS/ols/SF_12_MCS_2018_2019.rds'))
house.mod <- readRDS(paste0(trans.path, 'housing_quality/clm/housing_quality_2018_2019.rds'))
income.mod <- readRDS(paste0(trans.path, 'hh_income/ols/hh_income_2018_2019.rds'))
```


## Education

```{r}
summary(income.mod)
```




# WIP NONSENSE

```{r}
# Read raw datafiles in
raw.files <- list.files('/home/luke/Documents/MINOS/Minos/data/final_US/', full.names = TRUE)
raw.dat <- do.call(rbind, lapply(raw.files, read.csv))

correct.files <- list.files('/home/luke/Documents/MINOS/Minos/data/corrected_US/', full.names = TRUE)
correct <- do.call(rbind, lapply(correct.files, read.csv))

```

```{r}
f.sf12 <- raw.dat %>% select(pidp, time, SF_12_MCS)
c.sf12 <- correct %>% select(pidp, time, SF_12_MCS)


```

Now see if any SF_12_MCS values are missing in either the final data or corrected.

```{r}
sum(is.na(f.sf12$SF_12_MCS))
sum(is.na(c.sf12$SF_12_MCS))

sum(f.sf12$SF_12_MCS == -9)
sum(c.sf12$SF_12_MCS == -9)

f.drop <- f.sf12 %>% select(-pidp)
c.drop <- c.sf12 %>% select(-pidp)

# missing by year
final.miss <- f.drop %>% 
  group_by(time) %>%
  summarise(final.missing = sum((SF_12_MCS == -9)))

correct.miss <- c.drop %>% 
  group_by(time) %>%
  summarise(correct.missing = sum((SF_12_MCS == -9)))

compare <- merge(final.miss, correct.miss, by='time')
```



