---
title: "Equivalent Income"
output: html_notebook
---


This notebook will visualise the new equivalent income outcome, and do some comparisons to hh_income and potentially also some validation using values from the original spreadsheet created by Chris Wu (where it was first derived).

# SETUP

```{r "setup", include=FALSE}

require(tidyverse)
require(ggplot2)

workingDir <- "/home/luke/Documents/WORK/MINOS/"
knitr::opts_knit$set(root.dir = workingDir)
rm(workingDir)
```

```{r, include=FALSE}
source('Minos/minos/validation/utils.r')
```

# Data

```{r}
# set output path to SIPHER 7 experiment out
out.path <- 'Minos/output/SIPHER7/'
# read all files into dataframe (util function handles runtime subdirectory etc.)
base.dat <- read_output(out.path, 'baseline')
```

# Visualise

## Simple Lineplot

Currently the calculation only happens at the end of a timestep, so the value is 0 in the first year.

```{r}
base.subset <- base.dat %>%
  select(pidp, hidp, time, age, weight, hh_income, equivalent_income, starts_with('S7_'), loneliness) %>%
  group_by(time) %>%
  summarise(mean_household_income = weighted.mean(hh_income, w = weight, na.rm=TRUE),
            mean_equivalent_income = weighted.mean(equivalent_income, w = weight, na.rm=TRUE),
            sd_household_income = sd(hh_income, na.rm=TRUE),
            sd_equivalent_income = sd(equivalent_income, na.rm=TRUE)) %>%
  pivot_longer(cols = mean_household_income:sd_equivalent_income,
               names_sep = '_',
               names_to = c('stat', 'var'),
               values_to = 'value')

## Not ideal pivot_longer as it cuts off everything after the second underscore, however we can still work with it
```


```{r}
base.subset2 <- base.subset %>%
  pivot_wider(names_from = 'stat') %>%
  filter(time > 2020)
```

Now visualise.

```{r}
ggplot(data = base.subset2, aes(x = time, y = mean, group = var, color = var)) +
  geom_line() +
  xlab('Year') +
  ylab('Mean income (£s)') +
  ggtitle('Comparison of Household Income to Equivalent Income')
```

```{r}
ggplot(data = base.subset2, aes(x = time, y = mean, group = var, color = var)) +
  geom_line() +
  geom_ribbon(aes(y = mean, ymin = mean - sd, ymax = mean + sd, fill = var), alpha = .2) +
  xlab('Year') +
  ylab('Mean income (£s)') +
  ggtitle('Comparison of Household Income to Equivalent Income (with sd)')
```

## Adapting Chris' Spreadsheet

```{r}
# Want to remove the one-hot encoding but finding it very difficult in Python

df <- read_excel(path = 'EI_calculation.xlsx')
```


```{r}
df2 <- df %>%
  pivot_longer(cols = phy1:lone3,
               names_to = 'variable',
               values_to = 'level')
```


```{r}
df3 <- df %>%
  pivot_longer(cols = -c(pidp, i_hidp, dis_hcost, hh_size, Yc, EI)) %>%
  filter(value > 0) %>%
  mutate(level = readr::parse_number(as.character(name)))

df3$name <- gsub("\\d+", "", df3$name)

df3 <- df3 %>% 
  select(-value) %>%
  pivot_wider(names_from = 'name',
              values_from = 'level') %>%
  rename(S7_physical_health = phy,
         S7_mental_health = men,
         loneliness = lone,
         S7_labour_state = em,
         S7_housing_quality = hous,
         S7_neighbourhood_safety = safe) %>%
  

write.csv(df3, 
          file = '/home/luke/Documents/WORK/MINOS/EI_calc_prepared.csv')

```








