---
title: "Handovers - SIPHER 7 Equivalent Income"
output:
  html_document:
    toc: true
    toc_float: true
    collapsed: false
    number_sections: true
    df_print: paged
    code_folding: hide
---

# SETUP

```{r "setup", include=FALSE}

require(tidyverse)
require(ggplot2)
require(here)
require(dplyr)
require(tidyr)
require(purrr)

#workingDir <- "/home/luke/Documents/WORK/MINOS/"
workingDir <- normalizePath('../')
knitr::opts_knit$set(root.dir = workingDir)
knitr::opts_chunk$set(
  warning = FALSE,
  message = FALSE
)
rm(workingDir)
```

Source utils for some functions.

```{r}
source(here::here('minos', 'utils_datain.R'))
source(here::here('minos', 'utils_validation_vis.R'))
source(here::here('minos', 'validation', 'utils.r'))
```

## Data

```{r}
# Read raw datafiles in
raw.files <- list.files(here::here('data', 'final_US'), pattern='[0-9]{4}_US_cohort.csv', full.names = TRUE)
raw.dat <- do.call(rbind, lapply(raw.files, read.csv))

#out.path <- 'Minos/output/SIPHER7/'
out.path <- here::here('output', 'SIPHER7/')
base.dat <- read_singular_local_out(out.path, 'baseline', drop.dead = TRUE)
```

## Constants

```{r}
start.year <- 2020
save.path <- here::here("plots", "handovers", 'SIPHER7')
create.if.not.exists(save.path)

shall.we.save <- FALSE
```

# Weight Testing

```{r}
raw.weight <- raw.dat %>%
  select(pidp, time, weight) %>%
  group_by(time) %>%
  summarise(mean.weight = mean(weight, na.rm = TRUE))

ggplot(raw.weight, aes(x = time, y = mean.weight)) +
  geom_line()

raw.weight.WBI <- raw.dat %>%
  select(pidp, time, weight, ethnicity) %>%
  filter(ethnicity == 'WBI') %>%
  group_by(time) %>%
  summarise(mean.weight = mean(weight, na.rm=TRUE))

ggplot(raw.weight.WBI, aes(x=time, y = mean.weight)) +
  geom_line()

raw.weight.eth <- raw.dat %>%
  select(pidp, time, weight, ethnicity) %>%
  group_by(time, ethnicity) %>%
  summarise(mean.weight = mean(weight, na.rm = TRUE))

ggplot(raw.weight.eth, aes(x = time, y = mean.weight, group = ethnicity, color = ethnicity)) +
  geom_line()
```


# INPUTS

## Income

```{r}
# first figure out how to plot final_US
# start with hh_income
raw.income <- raw.dat %>% 
  dplyr::select(pidp, time, hh_income, weight) %>%
  group_by(time) %>%
  summarise(income = mean(hh_income, na.rm=TRUE)) %>%
  mutate(source = 'final_US')

base.income <- base.dat %>%
  dplyr::select(pidp, time, hh_income, weight) %>%
  group_by(time) %>%
  summarise(income = mean(hh_income)) %>%
  mutate(source = 'baseline_output')

# merge before plot
income <- rbind(raw.income, base.income)

# Now plot
ggplot(data = income, mapping = aes(x = time, y = income, group = source, colour = source)) +
  geom_line() +
  geom_vline(xintercept=start.year, linetype='dotted') +
  labs(title = 'Household Income', subtitle = 'Full Sample') +
  xlab('Year') +
  ylab('Income')

## Try a version where final_US is limited to only those present from wave 1 
# onwards because the sample refreshments are messing with the plot
raw.income.wave1 <- raw.dat$pidp[raw.dat$time == 2009]

raw.income2 <- raw.dat %>% 
  dplyr::select(pidp, time, hh_income) %>%
  filter(pidp %in% raw.income.wave1) %>%
  group_by(time) %>%
  summarise(income = mean(hh_income, na.rm = TRUE)) %>%
  mutate(source = 'final_US')

base.income2 <- base.dat %>%
  dplyr::select(pidp, time, hh_income) %>%
  filter(pidp %in% raw.income.wave1) %>%
  group_by(time) %>%
  summarise(income = mean(hh_income, na.rm = TRUE)) %>%
  mutate(source = 'baseline_output')

income2 <- rbind(raw.income2, base.income2)

# Now plot
ggplot(data = income2, mapping = aes(x = time, y = income, group = source, colour = source)) +
  geom_line() +
  geom_vline(xintercept=start.year, linetype='dotted') +
  labs(title = 'Household Income') +
  xlab('Year') +
  ylab('Income')

if (shall.we.save) {
  ggsave(filename = 'hh_income_wav1.png',
         plot = last_plot(),
         path = save.path)
}

raw.income.check <- raw.dat %>% 
  dplyr::select(pidp, time, hh_income) %>%
  filter(pidp %in% raw.income.wave1)

base.income.check <- base.dat %>%
  dplyr::select(pidp, time, hh_income) %>%
  filter(pidp %in% raw.income.wave1)

rm(raw.income, base.income, income, raw.income.wave1, raw.income2, base.income2, 
   raw.income.check, base.income.check)
```

### Modified Lineplots

```{r}
handover_lineplots(raw.dat, base.dat, 'hh_income')
```


### Boxplots

```{r}
handover_boxplots(raw.dat, base.dat, 'hh_income')
```


### Spaghetti

```{r}
# raw.inc <- raw.dat %>%
#   select(pidp, age, time, hh_income)
# base.inc <- base.dat %>%
#   select(pidp, age, time, hh_income)
# 
# income.spag <- rbind(raw.inc, base.inc)
# 
# spaghetti_plot(income.spag, 'hh_income',
#                save = shall.we.save,
#                save.path = save.path)
# 
# rm(raw.inc, base.inc, income.spag)
```


# OUTCOMES

## Equivalent Income

```{r}
# first figure out how to plot final_US
# start with hh_income
raw.ei <- raw.dat %>% 
  dplyr::select(pidp, time, equivalent_income, weight) %>%
  filter(equivalent_income != -9) %>%
  group_by(time) %>%
  summarise(equivalent_income = weighted.mean(equivalent_income, w=weight, na.rm = TRUE)) %>%
  mutate(source = 'final_US')

base.ei <- base.dat %>%
  dplyr::select(pidp, time, equivalent_income, weight) %>%
  group_by(time) %>%
  summarise(equivalent_income = weighted.mean(equivalent_income, w=weight, na.rm = TRUE)) %>%
  mutate(source = 'baseline_output')

# merge before plot
ei <- rbind(raw.ei, base.ei)
# drop -9 values (missing)
ei <- ei %>%
  filter(equivalent_income != -9)

# Now plot
ggplot(data = ei, mapping = aes(x = time, y = equivalent_income, group = source, colour = source)) +
  geom_line() +
  geom_vline(xintercept=start.year, linetype='dotted') +
  labs(title = 'Equivalent Income', subtitle = 'Full Sample') +
  xlab('Year') +
  ylab('EI')

## Try a version where final_US is limited to only those present from wave 1 
# onwards because the sample refreshments are messing with the plot
raw.ei.wave1 <- raw.dat$pidp[raw.dat$time == 2017]

raw.ei.2 <- raw.dat %>% 
  dplyr::select(pidp, time, equivalent_income, weight) %>%
  filter(pidp %in% raw.ei.wave1) %>%
  filter(equivalent_income != -9) %>%
  group_by(time) %>%
  summarise(equivalent_income = weighted.mean(equivalent_income, w=weight, na.rm = TRUE)) %>%
  mutate(source = 'final_US')

base.ei.2 <- base.dat %>%
  dplyr::select(pidp, time, equivalent_income, weight) %>%
  filter(pidp %in% raw.ei.wave1) %>%
  group_by(time) %>%
  summarise(equivalent_income = weighted.mean(equivalent_income, w=weight, na.rm = TRUE)) %>%
  mutate(source = 'baseline_output')

ei.2 <- rbind(raw.ei.2, base.ei.2)
# drop -9 values (missing)
ei.2 <- ei.2 %>%
  filter(equivalent_income != -9)

# Now plot
ggplot(data = ei.2, mapping = aes(x = time, y = equivalent_income, group = source, colour = source)) +
  geom_line() +
  geom_vline(xintercept=start.year, linetype='dotted') +
  labs(title = 'Equivalent Income', subtitle = 'Wave 9 sample') +
  xlab('Year') +
  ylab('EI')

if (shall.we.save) {
  ggsave(filename = 'EI_wav1.png',
         plot = last_plot(),
         path = save.path)
}


rm(raw.ei, base.ei, ei, raw.ei.wave1, raw.ei.2, base.ei.2, ei.2)
```

### Modified Lineplots

```{r}
handover_lineplots(raw.dat, base.dat, 'equivalent_income')
```

### Check Replenishing Population

Might give us a clue about the big correction in first year of simulation?

```{r}
repl.file <- here::here('data', 'replenishing', 'replenishing_pop_2019-2070.csv')
repl.dat <- read.csv(repl.file)

repl.equiv <- repl.dat %>%
  select(time, equivalent_income, weight) %>%
  group_by(time) %>%
  summarise(equivalent_income = weighted.mean(equivalent_income, w = weight, na.rm = TRUE))

ggplot(repl.equiv, aes(x = time, y = equivalent_income)) +
  geom_line()
```


### Boxplots

```{r}
handover_boxplots(raw.dat, base.dat, 'equivalent_income')
```

### Spaghetti

```{r}
# raw.ei <- raw.dat %>%
#   select(pidp, age, time, equivalent_income)
# base.ei <- base.dat %>%
#   select(pidp, age, time, equivalent_income)
# 
# ei.spag <- rbind(raw.ei, base.ei)
# 
# spaghetti_plot(base.ei, 'equivalent_income')
# 
# spaghetti_plot(ei.spag, 'equivalent_income',
#                save = shall.we.save,
#                save.path = save.path)
# 
# rm(raw.ei, base.ei, ei.spag)
```

# PATHWAYS

## S7 Housing Quality

```{r}
prepped.list <- validation_prep_ordinal(raw.dat, base.dat, 'S7_housing_quality')

housing <- prepped.list$var
housing.norm <- prepped.list$norm

# Now plot
ggplot(data = housing, mapping = aes(x = time, y = n, group = S7_housing_quality, colour = S7_housing_quality)) +
  geom_line() +
  geom_vline(xintercept=start.year, linetype='dotted') +
  labs(title = 'S7 Housing Quality', subtitle = 'Counts by Level') +
  xlab('Year') +
  ylab('Count')

ggplot(data = housing.norm, mapping = aes(x = time, y = prct, fill=S7_housing_quality)) +
  geom_bar(stat = 'identity') +
  geom_vline(xintercept=start.year, linetype='dotted') +
  labs(title = 'S7 Housing Quality') +
  xlab('Year') +
  ylab('Proportion')

if (shall.we.save) {
  ggsave(filename = 'S7_housing_quality.png',
         plot = last_plot(),
         path = save.path)
}

rm(prepped.list, housing, housing.norm)
```



```{r}
hous.pivoted <- combine_and_pivot_long(df1 = base.dat, 
                                       df1.name = 'simulated', 
                                       df2 = raw.dat, 
                                       df2.name = 'raw', 
                                       var = 'S7_housing_quality')

cv_ordinal_plots(pivoted.df = hous.pivoted, 
                 var = 'S7_housing_quality',
                 save = shall.we.save,
                 save.path = save.path)
```

### Spaghetti

```{r}
# raw.s <- raw.dat %>%
#   select(pidp, age, time, S7_housing_quality)
# base.s <- base.dat %>%
#   select(pidp, age, time, S7_housing_quality)
# 
# spag <- rbind(raw.s, base.s)
# 
# spaghetti_plot(spag, 'S7_housing_quality',
#                save = shall.we.save,
#                save.path = save.path)
# 
# rm(raw.s, base.s, spag)
```

## S7 Neighbourhood Safety

```{r}
prepped.list <- validation_prep_ordinal(raw.dat, base.dat, 'S7_neighbourhood_safety')

nh_safety <- prepped.list$var
nh_safety.norm <- prepped.list$norm

# Now plot
ggplot(data = nh_safety, mapping = aes(x = time, y = n, group = S7_neighbourhood_safety, colour = S7_neighbourhood_safety)) +
  geom_line() +
  geom_vline(xintercept=start.year, linetype='dotted') +
  labs(title = 'S7 Neighbourhood Safety', subtitle = 'Counts by Level') +
  xlab('Year') +
  ylab('Count')

ggplot(data = nh_safety.norm, mapping = aes(x = time, y = prct, fill=S7_neighbourhood_safety)) +
  geom_bar(stat = 'identity') +
  geom_vline(xintercept=start.year, linetype='dotted') +
  labs(title = 'S7 Neighbourhood Safety') +
  xlab('Year') +
  ylab('Proportion')

if (shall.we.save) {
  ggsave(filename = 'S7_neighbourhood_safety.png',
         plot = last_plot(),
         path = save.path)
}

## just look at means in case the means are causing some problems
raw.dat.2 <- raw.dat
raw.dat.2$S7_neighbourhood_safety2[raw.dat.2$S7_neighbourhood_safety == 'Often'] <- 1
raw.dat.2$S7_neighbourhood_safety2[raw.dat.2$S7_neighbourhood_safety == 'Some of the time'] <- 2
raw.dat.2$S7_neighbourhood_safety2[raw.dat.2$S7_neighbourhood_safety == 'Hardly ever'] <- 3
base.dat.2 <- base.dat
base.dat.2$S7_neighbourhood_safety2[base.dat.2$S7_neighbourhood_safety == 'Often'] <- 1
base.dat.2$S7_neighbourhood_safety2[base.dat.2$S7_neighbourhood_safety == 'Some of the time'] <- 2
base.dat.2$S7_neighbourhood_safety2[base.dat.2$S7_neighbourhood_safety == 'Hardly ever'] <- 3

handover_lineplots(raw.dat.2, base.dat.2, 'S7_neighbourhood_safety2')

rm(prepped.list, nh_safety, nh_safety.norm)
```



```{r}
pivoted <- combine_and_pivot_long(df1 = base.dat, 
                                       df1.name = 'simulated', 
                                       df2 = raw.dat, 
                                       df2.name = 'raw', 
                                       var = 'S7_neighbourhood_safety')

cv_ordinal_plots(pivoted.df = pivoted, 
                 var = 'S7_neighbourhood_safety',
                 save = shall.we.save,
                 save.path = save.path)
```

### Spaghetti

```{r}
# raw.s <- raw.dat %>%
#   select(pidp, age, time, S7_neighbourhood_safety)
# base.s <- base.dat %>%
#   select(pidp, age, time, S7_neighbourhood_safety)
# 
# spag <- rbind(raw.s, base.s)
# 
# spaghetti_plot(spag, 'S7_neighbourhood_safety',
#                save = shall.we.save,
#                save.path = save.path)
# 
# rm(raw.s, base.s, spag)
```


## S7 Labour State

```{r}
prepped.list <- validation_prep_ordinal(raw.dat, base.dat, 'S7_labour_state')

lab.state <- prepped.list$var
lab.state.norm <- prepped.list$norm

# Now plot
ggplot(data = lab.state, mapping = aes(x = time, y = n, group = S7_labour_state, colour = S7_labour_state)) +
  geom_line() +
  geom_vline(xintercept=start.year, linetype='dotted') +
  labs(title = 'S7 Labour State', subtitle = 'Counts by Level') +
  xlab('Year') +
  ylab('Count')

ggplot(data = lab.state.norm, mapping = aes(x = time, y = prct, fill=S7_labour_state)) +
  geom_bar(stat = 'identity') +
  geom_vline(xintercept=start.year, linetype='dotted') +
  labs(title = 'S7 Labour State') +
  xlab('Year') +
  ylab('Proportion')

if (shall.we.save) {
  ggsave(filename = 'S7_labour_state.png',
         plot = last_plot(),
         path = save.path)
}

rm(prepped.list, lab.state, lab.state.norm)
```



```{r}
pivoted <- combine_and_pivot_long(df1 = base.dat, 
                                       df1.name = 'simulated', 
                                       df2 = raw.dat, 
                                       df2.name = 'raw', 
                                       var = 'S7_labour_state')

cv_ordinal_plots(pivoted.df = pivoted, 
                 var = 'S7_labour_state',
                 save = shall.we.save,
                 save.path = save.path)
```

### Spaghetti

```{r}
# raw.s <- raw.dat %>%
#   select(pidp, age, time, S7_labour_state)
# base.s <- base.dat %>%
#   select(pidp, age, time, S7_labour_state)
# 
# spag <- rbind(raw.s, base.s)
# 
# spaghetti_plot(spag, 'S7_labour_state',
#                save = shall.we.save,
#                save.path = save.path)
# 
# rm(raw.s, base.s, spag)
```

## S7 Physical Health

```{r}
prepped.list <- validation_prep_ordinal(raw.dat, base.dat, 'S7_physical_health')

var <- prepped.list$var
norm <- prepped.list$norm

tit <- 'S7 Physical Health'

# Now plot
ggplot(data = var, mapping = aes(x = time, y = n, group = S7_physical_health, colour = S7_physical_health)) +
  geom_line() +
  geom_vline(xintercept=start.year, linetype='dotted') +
  labs(title = tit, subtitle = 'Counts by Level') +
  xlab('Year') +
  ylab('Count')

ggplot(data = norm, mapping = aes(x = time, y = prct, fill=S7_physical_health)) +
  geom_bar(stat = 'identity') +
  geom_vline(xintercept=start.year, linetype='dotted') +
  labs(title = tit) +
  xlab('Year') +
  ylab('Proportion')

if (shall.we.save) {
  ggsave(filename = 'S7_physical_health.png',
         plot = last_plot(),
         path = save.path)
}


handover_lineplots(raw.dat, base.dat, 'S7_physical_health')


rm(prepped.list, var, norm, tit)
```



```{r}
pivoted <- combine_and_pivot_long(df1 = base.dat, 
                                       df1.name = 'simulated', 
                                       df2 = raw.dat, 
                                       df2.name = 'raw', 
                                       var = 'S7_physical_health')

cv_ordinal_plots(pivoted.df = pivoted, 
                 var = 'S7_physical_health',
                 save = shall.we.save,
                 save.path = save.path)
```

### Spaghetti

```{r}
# raw.s <- raw.dat %>%
#   select(pidp, age, time, S7_physical_health)
# base.s <- base.dat %>%
#   select(pidp, age, time, S7_physical_health)
# 
# spag <- rbind(raw.s, base.s)
# 
# spaghetti_plot(spag, 'S7_physical_health',
#                save = shall.we.save,
#                save.path = save.path)
# 
# rm(raw.s, base.s, spag)
```

## S7 Mental Health

```{r}
prepped.list <- validation_prep_ordinal(raw.dat, base.dat, 'S7_mental_health')

var <- prepped.list$var
norm <- prepped.list$norm

tit <- 'S7 Mental Health'

# Now plot
ggplot(data = var, mapping = aes(x = time, y = n, group = S7_mental_health, colour = S7_mental_health)) +
  geom_line() +
  geom_vline(xintercept=start.year, linetype='dotted') +
  labs(title = tit, subtitle = 'Counts by Level') +
  xlab('Year') +
  ylab('Count')

ggplot(data = norm, mapping = aes(x = time, y = prct, fill=S7_mental_health)) +
  geom_bar(stat = 'identity') +
  geom_vline(xintercept=start.year, linetype='dotted') +
  labs(title = tit) +
  xlab('Year') +
  ylab('Proportion')

if (shall.we.save) {
  ggsave(filename = 'S7_mental_health.png',
         plot = last_plot(),
         path = save.path)
}


rm(prepped.list, var, norm, tit)
```



```{r}
pivoted <- combine_and_pivot_long(df1 = base.dat, 
                                       df1.name = 'simulated', 
                                       df2 = raw.dat, 
                                       df2.name = 'raw', 
                                       var = 'S7_mental_health')

cv_ordinal_plots(pivoted.df = pivoted, 
                 var = 'S7_mental_health',
                 save = shall.we.save,
                 save.path = save.path)
```

### Spaghetti

```{r}
# raw.s <- raw.dat %>%
#   select(pidp, age, time, S7_mental_health)
# base.s <- base.dat %>%
#   select(pidp, age, time, S7_mental_health)
# 
# spag <- rbind(raw.s, base.s)
# 
# spaghetti_plot(spag, 'S7_mental_health',
#                save = shall.we.save,
#                save.path = save.path)
# 
# rm(raw.s, base.s, spag)
```

## Loneliness

```{r}
prepped.list <- validation_prep_ordinal(raw.dat, base.dat, 'loneliness')

var <- prepped.list$var
norm <- prepped.list$norm

tit <- 'Loneliness'

## loneliness only available from 2017 onwards
var <- filter(var, time >= 2017)

# Now plot
ggplot(data = var, mapping = aes(x = time, y = n, group = loneliness, colour = loneliness)) +
  geom_line() +
  geom_vline(xintercept=start.year, linetype='dotted') +
  labs(title = tit, subtitle = 'Counts by Level') +
  xlab('Year') +
  ylab('Count')

ggplot(data = norm, mapping = aes(x = time, y = prct, fill=loneliness)) +
  geom_bar(stat = 'identity') +
  geom_vline(xintercept=start.year, linetype='dotted') +
  labs(title = tit) +
  xlab('Year') +
  ylab('Proportion')

if (shall.we.save) {
  ggsave(filename = 'loneliness.png',
         plot = last_plot(),
         path = save.path)
}


rm(prepped.list, var, norm, tit)
```



```{r}
pivoted <- combine_and_pivot_long(df1 = base.dat, 
                                       df1.name = 'simulated', 
                                       df2 = raw.dat, 
                                       df2.name = 'raw', 
                                       var = 'loneliness')

pivoted <- filter(pivoted, time >= 2017)

cv_ordinal_plots(pivoted.df = pivoted, 
                 var = 'loneliness',
                 save = shall.we.save,
                 save.path = save.path)
```

### Spaghetti

```{r}
# raw.s <- raw.dat %>%
#   select(pidp, age, time, loneliness)
# base.s <- base.dat %>%
#   select(pidp, age, time, loneliness)
# 
# spag <- rbind(raw.s, base.s)
# 
# spaghetti_plot(spag, 'loneliness',
#                save = shall.we.save,
#                save.path = save.path)
# 
# rm(raw.s, base.s, spag)
```


## Education

```{r}
prepped.list <- validation_prep_ordinal(raw.dat, base.dat, 'education_state')

var <- prepped.list$var
norm <- prepped.list$norm

tit <- 'Education State'

# Now plot
ggplot(data = var, mapping = aes(x = time, y = n, group = education_state, colour = education_state)) +
  geom_line() +
  geom_vline(xintercept=start.year, linetype='dotted') +
  labs(title = tit, subtitle = 'Counts by Level') +
  xlab('Year') +
  ylab('Count')

ggplot(data = norm, mapping = aes(x = time, y = prct, fill=education_state)) +
  geom_bar(stat = 'identity') +
  geom_vline(xintercept=start.year, linetype='dotted') +
  labs(title = tit) +
  xlab('Year') +
  ylab('Proportion')

if (shall.we.save) {
  ggsave(filename = 'education_state.png',
         plot = last_plot(),
         path = save.path)
}


rm(prepped.list, var, norm, tit)
```

```{r}
pivoted <- combine_and_pivot_long(df1 = base.dat, 
                                       df1.name = 'simulated', 
                                       df2 = raw.dat, 
                                       df2.name = 'raw', 
                                       var = 'education_state')

cv_ordinal_plots(pivoted.df = pivoted, 
                 var = 'education_state',
                 save = shall.we.save,
                 save.path = save.path)
```

### Spaghetti

```{r}
# raw.s <- raw.dat %>%
#   select(pidp, age, time, education_state)
# base.s <- base.dat %>%
#   select(pidp, age, time, education_state)
# 
# spag <- rbind(raw.s, base.s)
# 
# spaghetti_plot(spag, 'education_state',
#                save = shall.we.save,
#                save.path = save.path)
# 
# rm(raw.s, base.s, spag)
```

## Parity

```{r}
base.parity <- base.dat %>%
  filter(sex == "Female")

raw.parity <- raw.dat %>%
  filter(sex == "Female")

prepped.list <- validation_prep_ordinal(raw.parity, base.parity, 'nkids_ind')

var <- prepped.list$var
norm <- prepped.list$norm

tit <- 'Parity (total no. of children)'

# Now plot
ggplot(data = var, mapping = aes(x = time, y = n, group = nkids_ind, colour = nkids_ind)) +
  geom_line() +
  geom_vline(xintercept=start.year, linetype='dotted') +
  labs(title = tit, subtitle = 'Counts by Level') +
  xlab('Year') +
  ylab('Count')

ggplot(data = norm, mapping = aes(x = time, y = prct, fill=nkids_ind)) +
  geom_bar(stat = 'identity') +
  geom_vline(xintercept=start.year, linetype='dotted') +
  labs(title = tit) +
  xlab('Year') +
  ylab('Proportion')

if (shall.we.save) {
  ggsave(filename = 'parity.png',
         plot = last_plot(),
         path = save.path)
}


rm(prepped.list, var, norm, tit)
```

```{r}
pivoted <- combine_and_pivot_long(df1 = base.parity,
                                  df1.name = 'simulated', 
                                  df2 = raw.parity, 
                                  df2.name = 'raw', 
                                  var = 'nkids_ind')

cv_ordinal_plots(pivoted.df = pivoted, 
                 var = 'nkids_ind',
                 save = shall.we.save,
                 save.path = save.path)
```

### Spaghetti

```{r}
# raw.s <- raw.parity %>%
#   select(pidp, age, time, nkids_ind)
# base.s <- base.parity %>%
#   select(pidp, age, time, nkids_ind)
# 
# spag <- rbind(raw.s, base.s)
# 
# spaghetti_plot(spag, 'nkids_ind',
#                save = shall.we.save,
#                save.path = save.path)
# 
# rm(raw.s, base.s, spag)
```

## Job Sec

```{r}
prepped.list <- validation_prep_ordinal(raw.dat, base.dat, 'job_sec')

var <- prepped.list$var
norm <- prepped.list$norm

tit <- 'Job NSSEC'

# Now plot
ggplot(data = var, mapping = aes(x = time, y = n, group = job_sec, colour = job_sec)) +
  geom_line() +
  geom_vline(xintercept=start.year, linetype='dotted') +
  labs(title = tit, subtitle = 'Counts by Level') +
  xlab('Year') +
  ylab('Count')

ggplot(data = norm, mapping = aes(x = time, y = prct, fill=job_sec)) +
  geom_bar(stat = 'identity') +
  geom_vline(xintercept=start.year, linetype='dotted') +
  labs(title = tit) +
  xlab('Year') +
  ylab('Proportion')

if (shall.we.save) {
  ggsave(filename = 'job_sec.png',
         plot = last_plot(),
         path = save.path)
}


rm(prepped.list, var, norm, tit)
```

```{r}
pivoted <- combine_and_pivot_long(df1 = base.dat,
                                  df1.name = 'simulated', 
                                  df2 = raw.dat, 
                                  df2.name = 'raw', 
                                  var = 'job_sec')

cv_ordinal_plots(pivoted.df = pivoted, 
                 var = 'job_sec',
                 save = shall.we.save,
                 save.path = save.path)
```
