---
title: "MINOS Handover Plots"
output:
  html_document:
    toc: true
    toc_float: true
    collapsed: false
    number_sections: true
    df_print: paged
    code_folding: hide
---

This notebook shows the handover plots for all pathways in the MINOS microsimulation model.

Handover plots are not strictly statistical validation, but more a type of 'sanity check' for transitioned variables. A handover plot shows the 'handover' from input data to predicted outcomes, and allows us to see at a glance if the predicted outputs are following the same trends seen in the input data.

# SETUP

```{r "setup", include=FALSE}

require(tidyverse)
require(ggplot2)
require(ggridges) # for densities over time plots. 
require(knitr)
require(here)
require(dplyr)
require(tidyr)
require(purrr)
require(gghighlight)

#workingDir <- "/home/luke/Documents/WORK/MINOS/"
workingDir <- normalizePath('../')
knitr::opts_knit$set(root.dir = workingDir)
knitr::opts_chunk$set(
  warning = FALSE,
  message = FALSE
)
rm(workingDir)
```

Source utils for some functions.

```{r}
source(here::here('minos', 'utils_datain.R'))
source(here::here('minos', 'utils_validation_vis.R'))
source(here::here('minos', 'validation', 'utils.r'))
```

## Data

```{r}
# Read raw datafiles in
raw.files <- list.files(here::here('data', 'final_US'), pattern='[0-9]{4}_US_cohort.csv', full.names = TRUE)
raw.dat <- do.call(rbind, lapply(raw.files, read.csv)) 

out.path <- here::here('output', 'glasgow_scaled/')
base.dat <- read_singular_local_out(out.path, 'baseline', drop.dead = TRUE, drop.zero.weight = TRUE)
```

## Constants

```{r}
start.year <- 2021
save.path <- here::here("plots", "handovers", 'default')
create.if.not.exists(save.path)

shall.we.save <- FALSE
```

# Age Structure

```{r}
# assign to age_bucket in raw data
cut_bins <- c(-1, 15, 19, 24, 29, 44, 59, 74, 200)
cut_labels <- c("0to15", "16to19", "20to24", "25to29", "30to44", "45to59", "60to74", "75plus")

raw.dat$age_bucket <- cut(raw.dat$age, 
                          breaks = cut_bins, 
                          labels = cut_labels)

handover_ordinal(raw.dat, base.dat, var = 'age_bucket', save = shall.we.save)
```

# Population Counts

```{r}
raw.alive <- raw.dat %>%
  group_by(time) %>%
  summarise(n = n())

base.alive <- base.dat %>%
  group_by(time) %>%
  summarise(n = n())

#handover_boxplots(raw.alive, base.alive, 'n')
handover_lineplots(raw.alive, base.alive, "n")

rm(raw.alive, base.alive)
```

# Universal Credit

```{r}
handover_ordinal(raw.dat, base.dat, var = 'universal_credit', save = shall.we.save)
```


# PATHWAYS

## Income

```{r}
# first figure out how to plot final_US
# start with hh_income

handover_boxplots(raw.dat, base.dat, 'hh_income')
handover_lineplots(raw.dat, base.dat, "hh_income")
```

### Spaghetti

```{r}
# raw.inc <- raw.dat %>%
#   select(pidp, age, time, hh_income)
# base.inc <- base.dat %>%
#   select(pidp, age, time, hh_income)
# 
# income.spag <- rbind(raw.inc, base.inc)
# 
# density_ridges(income.spag, 'hh_income',
#                save=shall.we.save, 
#                save.path=save.path)
# 
# pidp_sample <- sample(unique(income.spag$pidp), size=nrow(raw.inc)/10, replace=FALSE)
# income.spag.sample <- income.spag[which(income.spag$pidp %in% pidp_sample), ]
# spaghetti_plot(income.spag.sample, 'hh_income',
#                save = shall.we.save,
#                save.path = save.path)
# spaghetti_highlight_max_plot(income.spag.sample, 'hh_income',
#                save = shall.we.save,
#                save.path = save.path)
# 
# rm(raw.inc, base.inc, income.spag)
```

## Council Tax

```{r}
handover_boxplots(raw.dat, base.dat, 'council_tax')
handover_lineplots(raw.dat, base.dat, "council_tax")
```


## SF_12_MCS

```{r}
# sf12 boxplot handovers
handover_boxplots(raw.dat, base.dat, 'SF_12_MCS')
handover_lineplots(raw.dat, base.dat, "SF_12_MCS")
```

### Spaghetti

```{r}
raw.sf12.m <- raw.dat %>%
  select(pidp, age, time, SF_12_MCS)
base.sf12.m <- base.dat %>%
  select(pidp, age, time, SF_12_MCS)

sf12.m.spag <- rbind(raw.sf12.m, base.sf12.m)

#sf12.m.spag.sample <- sf12.m.spag[which(sf12.m.spag$pidp %in% pidp_sample), ]
spaghetti_plot(sf12.m.spag, 'SF_12_MCS',
               save = shall.we.save,
               save.path = save.path)
spaghetti_highlight_max_plot(sf12.m.spag, 'SF_12_MCS',
               save = shall.we.save,
               save.path = save.path)
  
density_ridges(sf12.m.spag, "SF_12_MCS", 
               save = shall.we.save, 
               save.path = save.path)

rm(raw.sf12.m, base.sf12.m, sf12.m.spag, sf12.m.spag.sample)
```

## SF_12_PCS

```{r}
handover_boxplots(raw.dat, base.dat, 'SF_12_PCS')
handover_lineplots(raw.dat, base.dat, "SF_12_PCS")
```

### Spaghetti

```{r}
raw.sf12.p <- raw.dat %>%
  select(pidp, age, time, SF_12_PCS)
base.sf12.p <- base.dat %>%
  select(pidp, age, time, SF_12_PCS)

sf12.p.spag <- rbind(raw.sf12.p, base.sf12.p)

spaghetti_plot(sf12.p.spag, 'SF_12_PCS',
               save = shall.we.save,
               save.path = save.path)

density_ridges(sf12.p.spag, "SF_12_PCS", 
               save = shall.we.save, 
               save.path = save.path)

rm(raw.sf12.p, base.sf12.p, sf12.p.spag)
```

### Histograms

I have a hypothesis that the longer we run through simulation, the more simulants are predicted a negative PCS value which is then clipped to a 0. Histograms over a few snapshots of time should show if this is happening.

```{r}
pcs.2021 <- base.dat %>%
  select(pidp, time, SF_12_PCS) %>%
  filter(time == 2021)

# pcs.2022 <- base.dat %>%
#   select(pidp, time, SF_12_PCS) %>%
#   filter(time == 2022)

pcs.2025 <- base.dat %>%
  select(pidp, time, SF_12_PCS) %>%
  filter(time == 2025)

pcs.2030 <- base.dat %>%
  select(pidp, time, SF_12_PCS) %>%
  filter(time == 2030)

pcs.2036 <- base.dat %>%
  select(pidp, time, SF_12_PCS) %>%
  filter(time == 2036)


merged <- rbind(pcs.2021, pcs.2025, pcs.2030, pcs.2036)
merged$time <- as.factor(merged$time)

ggplot(merged, aes(x = SF_12_PCS, group = time, colour = time, fill = time)) +
  geom_histogram() +
  labs(title = 'Distribution of SF_12_PCS')

ggplot(merged, aes(x = SF_12_PCS, group = time, colour = time, fill = time)) +
  geom_freqpoly() +
  labs(title = 'Distribution of SF_12_PCS', subtitle = 'Count')

ggplot(merged, aes(x = SF_12_PCS, y = after_stat(density), group = time, colour = time, fill = time)) +
  geom_freqpoly() +
  labs(title = 'Distribution of SF_12_PCS', subtitle = 'Density')
```


## Financial Situation

```{r}
handover_ordinal(raw.dat, base.dat, var = 'financial_situation', save = shall.we.save)
```

## Housing Quality

```{r}
handover_ordinal(raw.dat, base.dat, var = 'housing_quality', save = shall.we.save)
```

### Spaghetti

```{r}
# raw.s <- raw.dat %>%
#   select(pidp, age, time, housing_quality)
# base.s <- base.dat %>%
#   select(pidp, age, time, housing_quality)
# 
# spag <- rbind(raw.s, base.s)
# 
# spaghetti_plot(spag, 'housing_quality',
#                save = shall.we.save,
#                save.path = save.path)
# 
# rm(raw.s, base.s, spag)
```

## Neighbourhood Safety

```{r}
handover_ordinal(raw.dat, base.dat, var = 'neighbourhood_safety', save = shall.we.save)
```

### Spaghetti

```{r}
# raw.s <- raw.dat %>%
#   select(pidp, age, time, neighbourhood_safety)
# base.s <- base.dat %>%
#   select(pidp, age, time, neighbourhood_safety)
# 
# spag <- rbind(raw.s, base.s)
# 
# spaghetti_plot(spag, 'neighbourhood_safety',
#                save = shall.we.save,
#                save.path = save.path)
# 
# rm(raw.s, base.s, spag)
```

## Loneliness

```{r}
handover_ordinal(raw.dat, base.dat, var = 'loneliness', save = shall.we.save)
```

### Spaghetti

```{r}
# raw.s <- raw.dat %>%
#   select(pidp, age, time, loneliness)
# base.s <- base.dat %>%
#   select(pidp, age, time, loneliness)
# 
# spag <- rbind(raw.s, base.s)
# 
# spaghetti_plot(spag, 'loneliness',
#                save = shall.we.save,
#                save.path = save.path)
# 
# rm(raw.s, base.s, spag)
```

## Nutrition Quality

TODO: Drop negative values ONLY from waves with no data i.e. not 7,9,11

```{r}
#  nutriton quality line/boxplots.
handover_boxplots(raw.dat, base.dat, 'nutrition_quality')
handover_lineplots(raw.dat, base.dat, 'nutrition_quality')

test.pidps <- raw.dat %>%
  select(pidp)

test.base <- base.dat %>%
  filter(pidp %in% test.pidps$pidp)

handover_boxplots(raw.dat, test.base, 'nutrition_quality')
handover_lineplots(raw.dat, test.base, 'nutrition_quality')
```

### Spaghetti

```{r}
# raw.nut <- raw.dat %>%
#   select(pidp, age, time, nutrition_quality)
# base.nut <- base.dat %>%
#   select(pidp, age, time, nutrition_quality)
# 
# nut.spag <- rbind(raw.nut, base.nut)
# 
# spaghetti_plot(nut.spag, 'nutrition_quality',
#                save = shall.we.save,
#                save.path = save.path)
# 
# 
# density_ridges(nut.spag, "nutrition_quality",
#                save = T,
#                save.path = save.path)
# 
# rm(raw.nut, base.nut, nut.spag)
```

## Tobacco

### ncigs mean

TODO: Drop negative values ONLY from waves with no data i.e. not 7,9,11

```{r}
#  nutriton quality line/boxplots.
handover_boxplots(raw.dat, base.dat, 'ncigs')
handover_lineplots(raw.dat, base.dat, 'ncigs')

test.pidps <- raw.dat %>%
  select(pidp)

test.base <- base.dat %>%
  filter(pidp %in% test.pidps$pidp)

handover_boxplots(raw.dat, test.base, 'ncigs')
handover_lineplots(raw.dat, test.base, 'ncigs')
```

### Spaghetti

```{r}
# raw.nut <- raw.dat %>%
#   select(pidp, age, time, ncigs)
# base.nut <- base.dat %>%
#   select(pidp, age, time, ncigs)
# 
# nut.spag <- rbind(raw.nut, base.nut)
# 
# spaghetti_plot(nut.spag, 'ncigs',
#                save = shall.we.save,
#                save.path = save.path)
# 
# 
# density_ridges(nut.spag, "ncigs",
#                save = FALSE,
#                save.path = save.path)
# 
# rm(raw.nut, base.nut, nut.spag)
```

### ncigs Max

```{r}
raw.ncigs_max <- raw.dat %>%
  select(pidp, time, ncigs) %>%
  group_by(time) %>%
  summarise(max_ncigs = max(ncigs)) %>%
  mutate(source = 'final_US')

base.ncigs_max <- base.dat %>%
  dplyr::select(pidp, time, ncigs) %>%
  group_by(time) %>%
  summarise(max_ncigs = max(ncigs)) %>%
  mutate(source = 'baseline_output')

max_ncigs <- rbind(raw.ncigs_max, base.ncigs_max)

# Now plot
ggplot(data = max_ncigs, mapping = aes(x = time, y = max_ncigs, group = source, colour = source)) +
  geom_line() +
  geom_vline(xintercept=start.year, linetype='dotted') +
  labs(title = 'Max ncigs', subtitle = 'Full Sample') +
  xlab('Year') +
  ylab('Average')
```


## Physical Health

NOTE: At present, physical health is not predicted or transitioned.

```{r}
handover_continuous(raw.dat, base.dat, var = 'phealth')
handover_boxplots(raw.dat, base.dat, 'phealth')
handover_lineplots(raw.dat, base.dat, 'phealth')
```

### Spaghetti

```{r}
# raw.s <- raw.dat %>%
#   select(pidp, age, time, phealth)
# base.s <- base.dat %>%
#   select(pidp, age, time, phealth)
# 
# spag <- rbind(raw.s, base.s)
# 
# spaghetti_plot(spag, 'phealth',
#              save = shall.we.save,
#              save.path = save.path)
# 
# rm(raw.s, base.s, spag)
```

## Education

```{r}
handover_ordinal(raw.dat, base.dat, var = 'education_state', save = shall.we.save)
```



```{r}
pivoted <- combine_and_pivot_long(df1 = base.dat,
                                       df1.name = 'simulated',
                                       df2 = raw.dat,
                                       df2.name = 'raw',
                                       var = 'education_state')

cv_ordinal_plots(pivoted.df = pivoted,
                 var = 'education_state',
                 save = shall.we.save,
                 save.path = save.path)
```

### Spaghetti

```{r}
# raw.s <- raw.dat %>%
#   select(pidp, age, time, education_state)
# base.s <- base.dat %>%
#   select(pidp, age, time, education_state)
# 
# spag <- rbind(raw.s, base.s)
# 
# spaghetti_plot(spag, 'education_state',
#                save = shall.we.save,
#                save.path = save.path)
# 
# rm(raw.s, base.s, spag)
```

## nkids Household

```{r}
handover_boxplots(raw.dat, base.dat, 'nkids')
handover_lineplots(raw.dat, base.dat, 'nkids')
```

```{r}
raw.s <- raw.dat %>%
  select(pidp, age, time, nkids)
base.s <- base.dat %>%
  select(pidp, age, time, nkids)

spag <- rbind(raw.s, base.s)

spaghetti_plot(spag, 'nkids',
               save = shall.we.save,
               save.path = save.path)

rm(raw.s, base.s, spag)
```

## nkids Max

```{r}
# first figure out how to plot final_US
# start with hh_income
raw.nkids_max <- raw.dat %>%
  dplyr::select(pidp, time, nkids) %>%
  group_by(time) %>%
  summarise(max_nkids = max(nkids)) %>%
  mutate(source = 'final_US')

base.nkids_max <- base.dat %>%
  dplyr::select(pidp, time, nkids) %>%
  group_by(time) %>%
  summarise(max_nkids = max(nkids)) %>%
  mutate(source = 'baseline_output')

# merge before plot
max_nkids <- rbind(raw.nkids_max, base.nkids_max)

# Now plot
ggplot(data = max_nkids, mapping = aes(x = time, y = max_nkids, group = source, colour = source)) +
  geom_line() +
  geom_vline(xintercept=start.year, linetype='dotted') +
  labs(title = 'Max nkids', subtitle = 'Full Sample') +
  xlab('Year') +
  ylab('Average')
```

## Parity

```{r}
base.parity <- base.dat %>%
  filter(sex == "Female")

raw.parity <- raw.dat %>%
  filter(sex == "Female")

prepped.list <- validation_prep_ordinal(raw.parity, base.parity, 'nkids_ind')

var <- prepped.list$var
norm <- prepped.list$norm

tit <- 'Parity (total no. of children)'

# Now plot
ggplot(data = var, mapping = aes(x = time, y = n, group = nkids_ind, colour = nkids_ind)) +
  geom_line() +
  geom_vline(xintercept=start.year, linetype='dotted') +
  labs(title = tit, subtitle = 'Counts by Level') +
  xlab('Year') +
  ylab('Count')

ggplot(data = norm, mapping = aes(x = time, y = prct, fill=nkids_ind)) +
  geom_bar(stat = 'identity') +
  geom_vline(xintercept=start.year, linetype='dotted') +
  labs(title = tit) +
  xlab('Year') +
  ylab('Proportion')

if (shall.we.save) {
  ggsave(filename = 'parity.png',
         plot = last_plot(),
         path = save.path)
}


rm(prepped.list, var, norm, tit)
```

```{r}
pivoted <- combine_and_pivot_long(df1 = base.parity,
                                  df1.name = 'simulated', 
                                  df2 = raw.parity, 
                                  df2.name = 'raw', 
                                  var = 'nkids_ind')

cv_ordinal_plots(pivoted.df = pivoted, 
                 var = 'nkids_ind',
                 save = shall.we.save,
                 save.path = save.path)
```


### Spaghetti

```{r}
# raw.s <- raw.parity %>%
#   select(pidp, age, time, nkids_ind)
# base.s <- base.parity %>%
#   select(pidp, age, time, nkids_ind)
# 
# spag <- rbind(raw.s, base.s)
# 
# spaghetti_plot(spag, 'nkids_ind',
#                save = shall.we.save,
#                save.path = save.path)
# 
# rm(raw.s, base.s, spag)
```


## Alcohol (AUDITC)

```{r}
handover_ordinal(raw.dat, base.dat, var = 'auditc', save = shall.we.save)

raw.2020.alc <- raw.dat %>% 
  filter(time == 2020) %>%
  group_by(auditc) %>%
  summarise(n = n()) %>%
  mutate(prop = n / sum(n))

```

## Physical Activity

```{r}
handover_ordinal(raw.dat, base.dat, var = 'active', save = shall.we.save)

raw.2020.phys <- raw.dat %>% 
  filter(time == 2020) %>%
  group_by(active) %>%
  summarise(n = n()) %>%
  mutate(prop = n / sum(n))
```

## Material Deprivation

```{r}
#handover_boxplots(raw.dat, base.dat, 'matdep')
#handover_lineplots(raw.dat, base.dat, 'matdep')
handover_ordinal(raw.dat, base.dat, var = 'matdep', save = shall.we.save)

raw.dat$chron_disease <- as.factor(raw.dat$chron_disease)
raw.2020.cd <- raw.dat %>%
  select(time, chron_disease, age) %>%
  filter(time == 2020) %>%
  mutate(age_group = cut(age, 
                         breaks = c(0,20,30,40,50,60,70,80,90,100,120),
                         labels = c('16-19', '20-30', '30-40', '40-50', '50-60', '60-70', '70-80', '80-90', '90-100', '100+'))) %>%
  group_by(age_group, chron_disease) %>%
  summarise(n = n()) %>%
  group_by(age_group) %>%
  mutate(prop = n / sum(n),
         perc = prop * 100)
  # mutate(prop = n() / sum(n),
  #        perc = prop * 100)

raw.2020.cd

ggplot(raw.2020.cd, aes(x = age_group, y = perc, group = chron_disease, colour = chron_disease, fill = chron_disease)) +
  geom_col(position = 'dodge') +
  xlab('Age Group') +
  ylab('Proportion')
```

```{r}
# raw.s <- raw.dat %>%
#   select(pidp, age, time, matdep) %>%
#   filter(!matdep %in% miss.values)
# base.s <- base.dat %>%
#   select(pidp, age, time, matdep) %>%
#   filter(!matdep %in% miss.values)
# 
# spag <- rbind(raw.s, base.s)
# 
# spaghetti_plot(spag, 'matdep',
#                save = shall.we.save,
#                save.path = save.path)
# 
# rm(raw.s, base.s, spag)
```

## Chronic Disease

```{r}
handover_ordinal(raw.dat, base.dat, var = 'chron_disease', save = shall.we.save)
```


```{r}
# raw.s <- raw.dat %>%
#   select(pidp, age, time, chron_disease) %>%
#   filter(!chron_disease %in% miss.values)
# base.s <- base.dat %>%
#   select(pidp, age, time, chron_disease) %>%
#   filter(!chron_disease %in% miss.values)
# 
# spag <- rbind(raw.s, base.s)
# 
# spag$chron_disease <- as.numeric(spag$chron_disease)
# 
# spaghetti_plot(spag, 'chron_disease',
#                save = shall.we.save,
#                save.path = save.path)
# 
# density_ridges(spag, 'chron_disease',
#                save=shall.we.save, 
#                save.path=save.path)
# 
# pidp_sample <- sample(unique(spag$pidp), size=nrow(raw.s)/10, replace=FALSE)
# spag.sample <- spag[which(spag$pidp %in% pidp_sample), ]
# spaghetti_plot(spag.sample, 'chron_disease',
#                save = shall.we.save,
#                save.path = save.path)
# spaghetti_highlight_max_plot(spag.sample, 'chron_disease',
#                save = shall.we.save,
#                save.path = save.path)
# 
# rm(raw.s, base.s, spag)
```

## Hourly Wage

```{r}
handover_boxplots(raw.dat, base.dat, 'hourly_wage')
handover_lineplots(raw.dat, base.dat, 'hourly_wage')
```

```{r}
# raw.s <- raw.dat %>%
#   select(pidp, age, time, hourly_wage)
# base.s <- base.dat %>%
#   select(pidp, age, time, hourly_wage)
# 
# spag <- rbind(raw.s, base.s)
# 
# spaghetti_plot(spag, 'hourly_wage',
#                save = shall.we.save,
#                save.path = save.path)
# 
# # now a version limited to 0-100
# spag <- spag %>%
#   filter(hourly_wage <= 300)
# spaghetti_plot(spag, 'hourly_wage',
#                save = shall.we.save,
#                save.path = save.path)
# 
# rm(raw.s, base.s, spag)
```

```{r}
# # some basic statistics about hourly_wage variable
# print("Some basic statistics on hourly_wage. These are all for 2020.")
# raw.2020 <- raw.dat %>% filter(time == 2020)
# print('All living people in 2020')
# print(paste0("Number of people alive in 2020: ", nrow(raw.2020)))
# # number individuals with an hourly_wage > 0
# print('People not in work')
# print(paste0("Number of individuals not in paid work: ", sum(!raw.2020$S7_labour_state %in% c('FT Employed', 'PT Employed'))))
# print(paste0("Number of individuals with hourly_wage == 0: ", sum(raw.2020$hourly_wage == 0)))
# 
# # Number in work
# print('People in work')
# print(paste0("Number of individuals in paid work: ", sum(raw.2020$S7_labour_state %in% c('FT Employed', 'PT Employed'))))
# print(paste0("Number of individuals with hourly_wage > 0: ", sum(raw.2020$hourly_wage > 0)))
# 
# # Extreme hourly_wage values
# print('Extreme hourly wage values: HIGH')
# print(paste0("Number of individuals with hourly_wage > 30: ", sum(raw.2020$hourly_wage > 30)))
# print(paste0("Number of individuals with hourly_wage > 50: ", sum(raw.2020$hourly_wage > 50)))
# print(paste0("Number of individuals with hourly_wage > 100: ", sum(raw.2020$hourly_wage > 100)))
# print(paste0("Number of individuals with hourly_wage > 500: ", sum(raw.2020$hourly_wage > 500)))
# print(paste0("Number of individuals with hourly_wage > 1000: ", sum(raw.2020$hourly_wage > 1000)))
# print(paste0("Number of individuals with hourly_wage > 2000: ", sum(raw.2020$hourly_wage > 2000)))
# 
# raw.2020.work <- raw.2020 %>% filter(hourly_wage > 0)
# print('Extreme hourly wage values: LOW (non-zero)')
# print(paste0("Number of individuals with hourly_wage < 20: ", sum(raw.2020.work$hourly_wage < 20)))
# print(paste0("Number of individuals with hourly_wage < 10: ", sum(raw.2020.work$hourly_wage < 10)))
# print(paste0("Number of individuals with hourly_wage < 5: ", sum(raw.2020.work$hourly_wage < 5)))
# print(paste0("Number of individuals with hourly_wage < 1: ", sum(raw.2020.work$hourly_wage < 1)))
```

## S7 Labour State

```{r}
prepped.list <- validation_prep_ordinal(raw.dat, base.dat, 'S7_labour_state')

lab.state <- prepped.list$var
lab.state.norm <- prepped.list$norm

# Now plot
ggplot(data = lab.state, mapping = aes(x = time, y = n, group = S7_labour_state, colour = S7_labour_state)) +
  geom_line() +
  geom_vline(xintercept=start.year, linetype='dotted') +
  labs(title = 'S7 Labour State', subtitle = 'Counts by Level') +
  xlab('Year') +
  ylab('Count')

ggplot(data = lab.state.norm, mapping = aes(x = time, y = prct, fill=S7_labour_state)) +
  geom_bar(stat = 'identity') +
  geom_vline(xintercept=start.year, linetype='dotted') +
  labs(title = 'S7 Labour State') +
  xlab('Year') +
  ylab('Proportion')

if (shall.we.save) {
  ggsave(filename = 'S7_labour_state.png',
         plot = last_plot(),
         path = save.path)
}


rm(prepped.list, lab.state, lab.state.norm)
```



```{r}
pivoted <- combine_and_pivot_long(df1 = base.dat, 
                                       df1.name = 'simulated', 
                                       df2 = raw.dat, 
                                       df2.name = 'raw', 
                                       var = 'S7_labour_state')

cv_ordinal_plots(pivoted.df = pivoted, 
                 var = 'S7_labour_state',
                 save = shall.we.save,
                 save.path = save.path)
```

## Child Ages

```{r}
raw.child.ages <- raw.dat %>%
  dplyr::select(pidp, hidp, time, "child_ages", "nkids") %>%
  filter(time > 2013 & child_ages != 'childless') %>%
  group_by(time, hidp) %>%
  summarise(child_ages = find_mode(child_ages))

r.s<- strsplit(raw.child.ages$child_ages, "_")

raw.child.ages.expanded <- data.frame(time = rep(raw.child.ages$time, sapply(r.s, length)), expanded_child_ages = unlist(r.s))
raw.child.ages.expanded <- raw.child.ages.expanded %>%
  group_by(time, expanded_child_ages) %>%
  summarise(age_counts = n()) %>%
  mutate(source = 'final_US') %>%
  filter(expanded_child_ages <= 16)

base.child.ages <- base.dat %>%
  dplyr::select(pidp, hidp, time, "child_ages", "nkids") %>%
  filter(time > 2009) %>%
  group_by(time, hidp) %>%
  summarise(child_ages = find_mode(child_ages))

b.s<- strsplit(base.child.ages$child_ages, "_")

base.child.ages.expanded <- data.frame(time = rep(base.child.ages$time, sapply(b.s, length)), expanded_child_ages = unlist(b.s))
base.child.ages.expanded <- base.child.ages.expanded %>%
  group_by(time, expanded_child_ages) %>%
  summarise(age_counts = n()) %>%
  mutate(source = 'baseline')

combined <- rbind(raw.child.ages.expanded, base.child.ages.expanded)
  
ggplot(data = combined, mapping = aes(x = time, y = age_counts, group = expanded_child_ages, colour =  factor(as.numeric(expanded_child_ages)))) +
  geom_line() +
  geom_vline(xintercept = start.year) +
  labs(title = "Child Age Counts Over Time", subtitle = 'Counts by Level') +
  scale_colour_viridis_d() +
  xlab('Year') +
  ylab('Count')

ggplot(data = combined, mapping = aes(x = factor(as.numeric(expanded_child_ages)), y = age_counts, group = factor(time), colour = factor(time))) +
  geom_line() +
  geom_vline(xintercept = start.year) +
  labs(title = "Child Age Counts Over Time", subtitle = 'Counts by Level') +
  scale_colour_viridis_d() +
  xlab('Year') +
  ylab('Count')

base.child.ages.nkids <- base.dat %>%
  group_by(time, hidp) %>%
  summarise(nkids_counts = mean(nkids)) %>%
  group_by(time) %>%
  summarise(nkids_by_year = sum(nkids_counts)) %>%
  mutate(source = 'baseline')

raw.child.ages.nkids <- raw.dat %>%
  group_by(time, hidp) %>%
  summarise(nkids_counts = mean(nkids)) %>%
  group_by(time) %>%
  summarise(nkids_by_year = sum(nkids_counts)) %>%
  mutate(source = 'final_US')

combined.nkids <- rbind(base.child.ages.nkids, raw.child.ages.nkids)

ggplot(data = combined.nkids, mapping = aes(x = time, y = nkids_by_year, group = source, colour = source)) +
  geom_line() +
  labs(title = "nkids Count Over Time", subtitle = 'Counts by Level') +
  xlab('Year') +
  ylab('Count')

```

```{r}

```

