---
title: "Mental Wellbeing Pathways"
output: html_notebook
---

# Setup

```{r "setup", include=FALSE}

require(tidyverse)
require(ggplot2)
require(purrr)

workingDir <- "/home/luke/Documents/WORK/MINOS/"
knitr::opts_knit$set(root.dir = workingDir)
rm(workingDir)
```

Source utils for some functions.
```{r}
source('Minos/minos/utils_datain.R')
```

## Data

```{r}
output.path <- 'Minos/output/default_config/'
baseline.path <- paste0(output.path, 'baseline')
base.path <- get_latest_runtime_subdirectory(baseline.path)

# read in all the output data files
base.files <- list.files(base.path,
                         pattern = '[0-9]{4}.csv',
                         full.names = TRUE)
data <- do.call(rbind, lapply(base.files, read.csv))
```

# Analysis

## SF 12

```{r}
sf12 <- data %>% 
  select(pidp, time, SF_12_MCS)

# calculate and plot mean over time
sf12.byyr <- data %>% group_by(time) %>%
  summarise(SF_12_MCS = mean(SF_12_MCS))

ggplot(data = sf12.byyr, mapping = aes(x = time, y = SF_12_MCS)) +
  geom_line()
```

```{r}
# Lets overlay some histograms at 3 time points - 2018 (before model), 2020 (pathways kick in?), 2030 (long term)
sf12.2018 <- sf12 %>% filter(time == 2018)
sf12.2020 <- sf12 %>% filter(time == 2020)
sf12.2030 <- sf12 %>% filter(time == 2030)

sf12.joined <- rbind(sf12.2018, sf12.2020, sf12.2030)
sf12.joined$time <- as.factor(sf12.joined$time)

ggplot(data = sf12.joined, mapping = aes(x = SF_12_MCS, group = time, fill = time, color = time)) +
  geom_histogram(position='dodge')
```

TODO: Why are we getting the same exact values from 2020 - 2030?

```{r}
print("2018:")
sprintf("Min: %f", min(sf12.2018$SF_12_MCS))
sprintf("Max: %f", max(sf12.2018$SF_12_MCS))
sprintf("Mean: %f", mean(sf12.2018$SF_12_MCS))
print("2020:")
sprintf("Min: %f", min(sf12.2020$SF_12_MCS))
sprintf("Max: %f", max(sf12.2020$SF_12_MCS))
sprintf("Mean: %f", mean(sf12.2020$SF_12_MCS))
print("2030:")
sprintf("Min: %f", min(sf12.2030$SF_12_MCS))
sprintf("Max: %f", max(sf12.2030$SF_12_MCS))
sprintf("Mean: %f", mean(sf12.2030$SF_12_MCS))
```

## hh_income

TODO: PLOT THE RAW DATA!!!

```{r}
income <- data %>% 
  select(pidp, time, hh_income)

# calculate and plot mean over time
income.byyr <- data %>% group_by(time) %>%
  summarise(hh_income = mean(hh_income))

ggplot(data = income.byyr, mapping = aes(x = time, y = hh_income)) +
  geom_line()
```

Again lets try overlaid histograms to see distributions over time.

```{r}
# Lets overlay some histograms at 3 time points - 2018 (before model), 2020 (pathways kick in?), 2030 (long term)
income.2018 <- income %>% filter(time == 2018)
income.2020 <- income %>% filter(time == 2020)
income.2030 <- income %>% filter(time == 2030)

income.joined <- rbind(income.2018, income.2020, income.2030)

income.joined$time <- as.factor(income.joined$time)
income.joined$hh_income <- as.numeric(income.joined$hh_income)

ggplot(data = income.joined, mapping = aes(x = hh_income, group = time, fill = time, color = time)) +
  geom_histogram(bins = 50, position='dodge')
```


Check out the min/max for each time point, looks like it spreads out massively.
```{r}
print("2018:")
sprintf("Min: %f", min(income.2018$hh_income))
sprintf("Max: %f", max(income.2018$hh_income))
sprintf("Mean: %f", mean(income.2018$hh_income))
print("2020:")
sprintf("Min: %f", min(income.2020$hh_income))
sprintf("Max: %f", max(income.2020$hh_income))
sprintf("Mean: %f", mean(income.2020$hh_income))
print("2030:")
sprintf("Min: %f", min(income.2030$hh_income))
sprintf("Max: %f", max(income.2030$hh_income))
sprintf("Mean: %f", mean(income.2030$hh_income))
```

## ncigs

DONE: Fixed problem where the rescale factor was still being applied in prediction but not in the estimation of the model.
DONE: Fixed line in the r_utils prediction method where the non-smokers were being predicted as smokers.
TODO: Fix the input data issue where lots of these vars are being reported as missing still (negative numbers). This should be in the run script somewhere.

```{r}
ncigs <- data %>% 
  select(pidp, time, ncigs)

# calculate and plot mean over time
ncigs.byyr <- data %>% group_by(time) %>%
  summarise(ncigs = mean(ncigs))

ggplot(data = ncigs.byyr, mapping = aes(x = time, y = ncigs)) +
  geom_line()
```

```{r}
# Lets overlay some histograms at 3 time points - 2018 (before model), 2020 (pathways kick in?), 2030 (long term)
ncigs.2018 <- ncigs %>% filter(time == 2018)
ncigs.2020 <- ncigs %>% filter(time == 2020)
ncigs.2030 <- ncigs %>% filter(time == 2030)

ncigs.joined <- rbind(ncigs.2018, ncigs.2020, ncigs.2030)
ncigs.joined$time <- as.factor(ncigs.joined$time)

ggplot(data = ncigs.joined, mapping = aes(x = ncigs, group = time, fill = time, color = time)) +
  geom_histogram(position='dodge')
```

```{r}
# Lets also look at the number of smokers vs non-smokers
smokers.count <- ncigs %>% 
  group_by(time) %>%
  summarise(non.smoker = sum(ncigs == 0),
            smoker = sum(ncigs > 0)) %>%
  pivot_longer(cols = non.smoker:smoker,
               names_to = 'smoking_status',
               values_to = 'count')

ggplot(data = smokers.count, mapping = aes(x = time, y = count, group = smoking_status, color = smoking_status)) +
  geom_line()
```

## Housing Quality

```{r}
# plot counts of each state over time (will only change with the replenishing but good to see)
housing.state <- data %>% 
  group_by(time, housing_quality) %>%
  count()

# set column types
housing.state$housing_quality <- as.factor(housing.state$housing_quality)

ggplot(data = housing.state, mapping = aes(x = time, y = n, group = housing_quality, color = housing_quality)) +
  geom_line()
```

## Neighbourhood Safety

```{r}
# plot counts of each state over time (will only change with the replenishing but good to see)
neighbour.state <- data %>% 
  group_by(time, neighbourhood_safety) %>%
  count()

# set column types
neighbour.state$neighbourhood_safety <- as.factor(neighbour.state$neighbourhood_safety)

ggplot(data = neighbour.state, mapping = aes(x = time, y = n, group = neighbourhood_safety, color = neighbourhood_safety)) +
  geom_line()
```

## Loneliness

```{r}
# plot counts of each state over time (will only change with the replenishing but good to see)
loneliness.state <- data %>% 
  group_by(time, loneliness) %>%
  count()

# set column types
loneliness.state$loneliness <- as.factor(loneliness.state$loneliness)

ggplot(data = loneliness.state, mapping = aes(x = time, y = n, group = loneliness, color = loneliness)) +
  geom_line()
```


```{r}

```


