---
title: "Equivalent Income Outcome Visualisation - Batch out"
output:
  html_document:
    toc: true
    toc_float: true
    collapsed: false
    number_sections: true
    df_print: paged
    code_folding: hide
---

# SETUP

```{r "setup", include=FALSE}

require(tidyverse)
require(ggplot2)
require(here)
require(dplyr)
require(tidyr)
require(purrr)

#workingDir <- "/home/luke/Documents/WORK/MINOS/"
workingDir <- normalizePath('../')
knitr::opts_knit$set(root.dir = workingDir)
knitr::opts_chunk$set(
  warning = FALSE,
  message = FALSE
)
rm(workingDir)
```

```{r, include=FALSE}
source(here::here('minos', 'utils_datain.R'))
source(here::here('minos', 'utils_validation_vis.R'))
source(here::here('minos', 'validation', 'utils.r'))
```

# Data

## BATCH DATA

```{r}
# S7.var.list <- c('hh_income', 'equivalent_income',  # Income variables
#                  'S7_housing_quality', 'S7_neighbourhood_safety', 'S7_physical_health', 'S7_mental_health', 'S7_labour_state', 'loneliness',  # SIPHER 7 variables
#                  'ethnicity', 'age', 'region', 'job_sec', 'education_state', 'nkids_ind', 'housing_tenure', 'urban')
# out.path.batch <- here::here('output', 'SIPHER7_batch/')
# 
# base.batch <- read_batch_out_all_years(out.path.batch, 'baseline', start.year = 2021, var.list = S7.var.list, verbose=FALSE)
# wage.batch <- read_batch_out_all_years(out.path.batch, 'livingWageIntervention', start.year = 2021, var.list = c('income_boosted', S7.var.list), verbose=FALSE)
# energy.batch <- read_batch_out_all_years(out.path.batch, 'energyDownlift', start.year = 2021, var.list = c('income_boosted', S7.var.list), verbose=FALSE)
# child.batch <- read_batch_out_all_years(out.path.batch, 'hhIncomeChildUplift', start.year = 2021, var.list = c('income_boosted', S7.var.list), verbose=FALSE)
# pov.batch <- read_batch_out_all_years(out.path.batch, 'hhIncomePovertyLineChildUplift', start.year = 2021, var.list = c('income_boosted', S7.var.list), verbose=FALSE)

out.path.arc <- here::here('output', 'SIPHER7_batch_ARC/')

base.batch <- read.csv(paste0(out.path.arc, 'baseline_batch_aggregated.csv'))
wage.batch <- read.csv(paste0(out.path.arc, 'wage_batch_aggregated.csv'))
energy.batch <- read.csv(paste0(out.path.arc, 'energy_batch_aggregated.csv'))
child.batch <- read.csv(paste0(out.path.arc, 'child_batch_aggregated.csv'))
pov.batch <- read.csv(paste0(out.path.arc, 'pov_batch_aggregated.csv'))
```

## Calculate Age Group

```{r}
calc_age_group <- function(batch.dat) {
  batch.dat <- batch.dat %>%
    mutate(age.group = cut(age, 
                            breaks = c(15, 30, 45, 60, 75, 120),
                            labels = c('16-30', '30-45', '45-60', '60-75', '75+')))
  return(batch.dat)
}

base.batch <- calc_age_group(base.batch)
wage.batch <- calc_age_group(wage.batch)
energy.batch <- calc_age_group(energy.batch)
child.batch <- calc_age_group(child.batch)
pov.batch <- calc_age_group(pov.batch)
```

## Calculate Income Quintile

```{r}
calc_income_quintile <- function(batch.dat) {
  batch.dat <- batch.dat %>%
    mutate(income.quint = cut(batch.dat$hh_income, breaks=c(quantile(batch.dat$hh_income, probs = seq(0, 1, by = 0.20))), 
                          labels=c(1,2,3,4,5), include.lowest=TRUE))
}

base.batch <- calc_income_quintile(base.batch)
wage.batch <- calc_income_quintile(wage.batch)
energy.batch <- calc_income_quintile(energy.batch)
child.batch <- calc_income_quintile(child.batch)
pov.batch <- calc_income_quintile(pov.batch)
```

# Batch Baseline

## Household Income

```{r}
base.bat.sub <- base.batch %>%
  select(pidp, time, run_id, hh_income, weight) %>%
  group_by(run_id, time) %>%
  summarise(hh_income = weighted.mean(hh_income, w = weight, na.rm=TRUE))

base.bat.sub$run_id <- as.factor(base.bat.sub$run_id)

big.run.id <- base.bat.sub$run_id[which.max(base.bat.sub$hh_income)]

base.bat.sub12 <- base.bat.sub %>%
  filter(run_id != big.run.id)

ggplot(data = base.bat.sub, aes(x = time, y = hh_income, group=run_id, color = run_id)) +
  geom_line() +
  labs(title = 'Household Income: Individual Runs')

ggplot(data = base.bat.sub12, aes(x = time, y = hh_income, group=run_id, color = run_id)) +
  geom_line() +
  labs(title = 'Household Income: Individual Runs')

ggplot(data = base.bat.sub, aes(x = time, y = hh_income)) +
  geom_smooth() +
  labs(title = 'Household Income: Smoothed mean')

ggplot(data = base.bat.sub12, aes(x = time, y = hh_income)) +
  geom_smooth() +
  labs(title = 'Household Income: Smoothed mean')

base.bat.sub2 <- base.bat.sub %>%
  group_by(time) %>%
  summarise(var = mean(hh_income),
         min = min(hh_income),
         max = max(hh_income))

base.bat.sub22 <- base.bat.sub12 %>%
  group_by(time) %>%
  summarise(var = mean(hh_income),
         min = min(hh_income),
         max = max(hh_income))

ggplot(data = base.bat.sub2, aes(x = time, y = var)) +
  geom_line() +
  geom_ribbon(aes(ymin = min, ymax = max), 
                alpha = 0.1,
                linetype = 'dashed') +
  labs(title = 'Household Income: Min - Max')

ggplot(data = base.bat.sub22, aes(x = time, y = var)) +
  geom_line() +
  geom_ribbon(aes(ymin = min, ymax = max), 
                alpha = 0.1,
                linetype = 'dashed') +
  labs(title = 'Household Income: Min - Max')
```


## Equivalent Income

```{r}
base.bat.sub <- base.batch %>%
  select(pidp, time, run_id, equivalent_income, weight) %>%
  group_by(run_id, time) %>%
  summarise(equivalent_income = weighted.mean(equivalent_income, w = weight, na.rm=TRUE))

base.bat.sub$run_id <- as.factor(base.bat.sub$run_id)

big.run.id <- base.bat.sub$run_id[which.max(base.bat.sub$equivalent_income)]

base.bat.sub12 <- base.bat.sub %>%
  filter(run_id != big.run.id)

ggplot(data = base.bat.sub, aes(x = time, y = equivalent_income, group=run_id, color = run_id)) +
  geom_line() +
  labs(title = 'Equivalent Income: Individual Runs')

ggplot(data = base.bat.sub12, aes(x = time, y = equivalent_income, group=run_id, color = run_id)) +
  geom_line() +
  labs(title = 'Equivalent Income: Individual Runs')

ggplot(data = base.bat.sub, aes(x = time, y = equivalent_income)) +
  geom_smooth() +
  labs(title = 'Equivalent Income: Smoothed mean')

ggplot(data = base.bat.sub12, aes(x = time, y = equivalent_income)) +
  geom_smooth() +
  labs(title = 'Equivalent Income: Smoothed mean')

base.bat.sub2 <- base.bat.sub %>%
  group_by(time) %>%
  summarise(var = mean(equivalent_income),
         min = min(equivalent_income),
         max = max(equivalent_income))

base.bat.sub22 <- base.bat.sub12 %>%
  group_by(time) %>%
  summarise(var = mean(equivalent_income),
         min = min(equivalent_income),
         max = max(equivalent_income))

ggplot(data = base.bat.sub2, aes(x = time, y = var)) +
  geom_line() +
  geom_ribbon(aes(ymin = min, ymax = max), 
                alpha = 0.1,
                linetype = 'dashed') +
  labs(title = 'Equivalent Income: Min - Max')

ggplot(data = base.bat.sub22, aes(x = time, y = var)) +
  geom_line() +
  geom_ribbon(aes(ymin = min, ymax = max), 
                alpha = 0.1,
                linetype = 'dashed') +
  labs(title = 'Equivalent Income: Min - Max')
```

# Comparisons

## Function

```{r}
equivalent_income_comparison_fullpop_batch <- function(base.bat, int.bat, int.name, save=FALSE, save.path=NULL) {
  base.subset <- base.bat %>%
    select(pidp, time, run_id, equivalent_income, weight) %>%
    group_by(time, run_id) %>%
    summarise(equivalent_income = weighted.mean(equivalent_income, w = weight))
  int.subset <- int.bat %>%
    select(pidp, time, run_id, equivalent_income, weight) %>%
    group_by(time, run_id) %>%
    summarise(equivalent_income = weighted.mean(equivalent_income, w = weight))
  
  base.subset$scenario <- 'Baseline'
  int.subset$scenario <- int.name
  
  combined <- rbind(base.subset, int.subset)
  
  p <- ggplot(combined, aes(x = time, y = equivalent_income, group = scenario, color = scenario)) +
    geom_smooth() +
    labs(title = paste0('Equivalent Income: ', int.name), subtitle = '10 Runs') +
    xlab('Year') +
    ylab('Equivalent Income (£)')
  
  print(p)
}
```

```{r}
equivalent_income_comparison_fullpop_batch(base.batch, energy.batch, 'EnergyCrisis')
equivalent_income_comparison_fullpop_batch(base.batch, wage.batch, 'LivingWage')
equivalent_income_comparison_fullpop_batch(base.batch, child.batch, 'AllChild')
equivalent_income_comparison_fullpop_batch(base.batch, pov.batch, 'PovertyChild')
```

```{r}
base.subset <- base.batch %>%
  select(pidp, time, run_id, equivalent_income, weight) %>%
  group_by(time, run_id) %>%
  summarise(equivalent_income = weighted.mean(equivalent_income, w = weight)) %>%
  mutate(scenario = 'Baseline')

wage.subset <- wage.batch %>%
  select(pidp, time, run_id, equivalent_income, weight) %>%
  group_by(time, run_id) %>%
  summarise(equivalent_income = weighted.mean(equivalent_income, w = weight)) %>%
  mutate(scenario = 'LivingWage')

energy.subset <- energy.batch %>%
  select(pidp, time, run_id, equivalent_income, weight) %>%
  group_by(time, run_id) %>%
  summarise(equivalent_income = weighted.mean(equivalent_income, w = weight)) %>%
  mutate(scenario = 'EnergyCrisis')

child.subset <- child.batch %>%
  select(pidp, time, run_id, equivalent_income, weight) %>%
  group_by(time, run_id) %>%
  summarise(equivalent_income = weighted.mean(equivalent_income, w = weight)) %>%
  mutate(scenario = 'AllChild')

pov.subset <- pov.batch %>%
  select(pidp, time, run_id, equivalent_income, weight) %>%
  group_by(time, run_id) %>%
  summarise(equivalent_income = weighted.mean(equivalent_income, w = weight)) %>%
  mutate(scenario = 'PovertyChild')

all.combined <- rbind(base.subset, wage.subset, energy.subset, child.subset, pov.subset)
all.combined$scenario <- factor(all.combined$scenario, levels = c('Baseline', 'LivingWage', 'EnergyCrisis', 'AllChild', 'PovertyChild'))

ggplot(data = all.combined, aes(x = time, y = equivalent_income, group = scenario, color = scenario)) +
  geom_smooth() +
  labs(title = 'Equivalent Income Comparison', subtitle = 'Whole Population') +
  xlab('Year') +
  ylab('Equivalent Income (£)')
```

# Treated Population

## Function

```{r}
equivalent_income_comparison_treated_batch <- function(base.bat, int.bat, int.name, save=FALSE, save.path=NULL) {
  base.sub <- base.bat %>%
    select(pidp, time, run_id, equivalent_income) %>%
    rename(baseline = equivalent_income)
  int.sub <- int.bat %>%
    select(pidp, time, run_id, equivalent_income, income_boosted, weight) %>%
    set_names(c('pidp', 'time', 'run_id', int.name, 'income_boosted', 'weight'))
  
  merged <- merge(base.sub, int.sub, by = c('pidp', 'time', 'run_id'))
  
  boosted.pidps <- int.sub %>%
    filter(income_boosted == 'True') %>%
    select(pidp)
  
  boosted <- merged %>%
    filter(pidp %in% boosted.pidps$pidp) %>%
    filter(income_boosted == 'True' | time == 2020) %>%
    select(-income_boosted) %>%
    pivot_longer(cols = baseline:.data[[int.name]],
                 names_to = 'scenario',
                 values_to = 'equivalent_income') %>%
    group_by(time, scenario, run_id) %>%
    summarise(equivalent_income = weighted.mean(equivalent_income, w=weight))
    
  
  p <- ggplot(data = boosted, aes(x = time, y = equivalent_income, group = scenario, color = scenario)) +
    geom_smooth() +
    labs(title = paste0('Equivalent Income: ', int.name), subtitle = 'Treated Population') +
    xlab('Year') +
    ylab('Equivalent Income (£)')
  
  print(p)
}
```

```{r}
equivalent_income_comparison_treated_batch(base.batch, wage.batch, 'LivingWage')
equivalent_income_comparison_treated_batch(base.batch, energy.batch, 'EnergyDownlift')
equivalent_income_comparison_treated_batch(base.batch, child.batch, 'AllChild')
equivalent_income_comparison_treated_batch(base.batch, pov.batch, 'PovertyChild')
```


# DETAILED ANALYSIS

For this, we're going to look at the difference in equivalent income and try to explain it by looking at the pathway variables. What we want to see is that as income is uplifted, the various pathways show a positive shift and that in part explains the difference in equivalent income. 

# Income and Equivalent Income

```{r}
income_equivinc_change_batch <- function(base.batch, int.batch, int.name) {
  base.inc <- base.batch %>%
    select(pidp, time, run_id, hh_income, equivalent_income, weight) %>%
    group_by(time, run_id) %>%
    summarise(base_income = weighted.mean(hh_income, w = weight, na.rm = TRUE),
              base_equiv_income = weighted.mean(equivalent_income, w = weight, na.rm = TRUE))
  
  int.inc <- int.batch %>%
    select(pidp, time, run_id, hh_income, equivalent_income, weight) %>%
    group_by(time, run_id) %>%
    summarise(energy_income = weighted.mean(hh_income, w = weight, na.rm = TRUE),
              energy_equiv_income = weighted.mean(equivalent_income, w = weight, na.rm = TRUE))
  
  combined <- merge(base.inc, int.inc, by = c('time', 'run_id'))
  
  combined$diff_income <- combined$energy_income - combined$base_income
  combined$diff_equiv_income <- combined$energy_equiv_income - combined$base_equiv_income
  
  combined <- combined %>%
    pivot_longer(cols = diff_income:diff_equiv_income,
                 names_prefix = 'diff_',
                 names_to = 'variable',
                 values_to = 'diff')
  
  combined2 <- combined %>%
    group_by(time, variable) %>%
    summarise(mean.diff = mean(diff))
  
  print(combined2)
  
  ggplot(combined, aes(x = time, y = diff, group = variable, color = variable)) +
    geom_smooth() +
    geom_hline(yintercept = 0, linetype = 'dashed') +
    labs(title = 'Change in Income and Equivalent Income', 
         subtitle = int.name)
}

income_equivinc_change_batch(base.batch, energy.batch, 'Energy Crisis')
income_equivinc_change_batch(base.batch, wage.batch, 'Living Wage')
income_equivinc_change_batch(base.batch, child.batch, 'All Child')
income_equivinc_change_batch(base.batch, pov.batch, 'Poverty Child')
```

# Equivalent Income Change

```{r}
equivinc_change_batch <- function(base.batch, int.batch, int.name) {
  base.inc <- base.batch %>%
    select(pidp, time, run_id, hh_income, equivalent_income, weight) %>%
    group_by(time, run_id) %>%
    summarise(base_equiv_income = weighted.mean(equivalent_income, w = weight, na.rm = TRUE))
  
  int.inc <- int.batch %>%
    select(pidp, time, run_id, hh_income, equivalent_income, weight) %>%
    group_by(time, run_id) %>%
    summarise(energy_equiv_income = weighted.mean(equivalent_income, w = weight, na.rm = TRUE))
  
  combined <- merge(base.inc, int.inc, by = c('time', 'run_id'))
  
  combined$diff_equiv_income <- combined$energy_equiv_income - combined$base_equiv_income
  
  #print(combined)
  
  ggplot(combined, aes(x = time, y = diff_equiv_income)) +
    geom_smooth() +
    geom_hline(yintercept = 0, linetype = 'dashed') +
    labs(title = 'Percent change: Income vs Equivalent Income',
         subtitle = int.name) +
    xlab('Year') +
    ylab('Percent Change')
}

equivinc_change_batch(base.batch, energy.batch, 'Energy Crisis')
equivinc_change_batch(base.batch, wage.batch, 'Living Wage')
equivinc_change_batch(base.batch, child.batch, 'All Child')
equivinc_change_batch(base.batch, pov.batch, 'Poverty Child')
```

## By Subpopulation

```{r}
equivinc_change_batch_subpop <- function(base.batch, int.batch, int.name, group.var) {
  base.inc <- base.batch %>%
    select(pidp, time, run_id, equivalent_income, weight, all_of(group.var)) %>%
    group_by(time, run_id, .data[[group.var]]) %>%
    summarise(base_equiv_income = weighted.mean(equivalent_income, w = weight, na.rm = TRUE))
  
  int.inc <- int.batch %>%
    select(pidp, time, run_id, equivalent_income, weight, all_of(group.var)) %>%
    group_by(time, run_id, .data[[group.var]]) %>%
    summarise(int_equiv_income = weighted.mean(equivalent_income, w = weight, na.rm = TRUE))
  
  combined <- merge(base.inc, int.inc, by = c('time', 'run_id', group.var))
  combined[[group.var]] <- as.factor(combined[[group.var]])
  
  combined$diff_equiv_income <- combined$int_equiv_income - combined$base_equiv_income
  
  combined <- combined %>%
    group_by(time, .data[[group.var]]) %>%
    summarise(mean_diff_equiv_income = mean(diff_equiv_income))
  
  ggplot(combined, aes(x = time, y = mean_diff_equiv_income, group = .data[[group.var]], color = .data[[group.var]])) +
    geom_smooth() +
    geom_hline(yintercept = 0, linetype = 'dashed') +
    labs(title = paste0('Equivalent Income change by ', group.var), subtitle = int.name) +
    xlab('Year') +
    ylab('Equivalent Income (£s)')
}

equivinc_change_batch_subpop(base.batch, energy.batch, 'Energy Crisis', group.var = 'income.quint')
equivinc_change_batch_subpop(base.batch, wage.batch, 'Living Wage', group.var = 'income.quint')
equivinc_change_batch_subpop(base.batch, child.batch, 'All Child', group.var = 'income.quint')
equivinc_change_batch_subpop(base.batch, pov.batch, 'Poverty Child', group.var = 'income.quint')
```


# Percent Change

Proportional difference? Percentage difference in income and equivalent income over time?

```{r}
income_equivinc_percent_change_batch <- function(base.batch, int.batch, int.name) {
  base.inc <- base.batch %>%
    select(pidp, time, run_id, hh_income, equivalent_income, weight) %>%
    group_by(time, run_id) %>%
    summarise(base_income = weighted.mean(hh_income, w = weight, na.rm = TRUE),
              base_equiv_income = weighted.mean(equivalent_income, w = weight, na.rm = TRUE))
  
  int.inc <- int.batch %>%
    select(pidp, time, run_id, hh_income, equivalent_income, weight) %>%
    group_by(time, run_id) %>%
    summarise(energy_income = weighted.mean(hh_income, w = weight, na.rm = TRUE),
              energy_equiv_income = weighted.mean(equivalent_income, w = weight, na.rm = TRUE))
  
  combined <- merge(base.inc, int.inc, by = c('time', 'run_id'))
  
  combined$diff_income <- combined$energy_income - combined$base_income
  combined$diff_equiv_income <- combined$energy_equiv_income - combined$base_equiv_income
  
  combined <- combined %>%
    group_by(time) %>%
    summarise(mean_income = mean(base_income),
              mean_equiv_income = mean(base_equiv_income),
              mean_diff_income = mean(diff_income),
              mean_diff_equiv_income = mean(diff_equiv_income)) %>%
    mutate(percent_change_income = (mean_diff_income / mean_income) * 100,
           percent_change_equiv_income = (mean_diff_equiv_income / mean_equiv_income) * 100) %>%
    select(-mean_income, -mean_equiv_income, -mean_diff_income, -mean_diff_equiv_income) %>%
    pivot_longer(cols = percent_change_income:percent_change_equiv_income,
                 names_prefix = 'percent_change_',
                 names_to = 'variable',
                 values_to = 'change')
  
  ggplot(combined, aes(x = time, y = change, group = variable, color = variable)) +
    geom_smooth() +
    geom_hline(yintercept = 0, linetype = 'dashed') +
    labs(title = 'Percent change: Income vs Equivalent Income',
         subtitle = int.name) +
    xlab('Year') +
    ylab('Percent Change')
}

income_equivinc_percent_change_batch(base.batch, energy.batch, 'Energy Crisis')
income_equivinc_percent_change_batch(base.batch, wage.batch, 'Living Wage')
income_equivinc_percent_change_batch(base.batch, child.batch, 'All Child')
income_equivinc_percent_change_batch(base.batch, pov.batch, 'Poverty Child')
```

## By Subpopulation

```{r}
income_equivinc_percent_change_batch_subpop <- function(base.batch, int.batch, int.name, filter.var, subpop) {
  print(paste0('Calculating income and equivalent income for ', filter.var, ' == ', subpop))
  
  base.inc <- base.batch %>%
    select(pidp, time, run_id, hh_income, equivalent_income, weight, all_of(filter.var)) %>%
    filter(.data[[filter.var]] == subpop) %>%
    group_by(time, run_id) %>%
    summarise(base_income = weighted.mean(hh_income, w = weight, na.rm = TRUE),
              base_equiv_income = weighted.mean(equivalent_income, w = weight, na.rm = TRUE))
  
  int.inc <- int.batch %>%
    select(pidp, time, run_id, hh_income, equivalent_income, weight, all_of(filter.var)) %>%
    filter(.data[[filter.var]] == subpop) %>%
    group_by(time, run_id) %>%
    summarise(energy_income = weighted.mean(hh_income, w = weight, na.rm = TRUE),
              energy_equiv_income = weighted.mean(equivalent_income, w = weight, na.rm = TRUE))
  
  combined <- merge(base.inc, int.inc, by = c('time', 'run_id'))
  
  combined$diff_income <- combined$energy_income - combined$base_income
  combined$diff_equiv_income <- combined$energy_equiv_income - combined$base_equiv_income
  
  combined <- combined %>%
    group_by(time) %>%
    summarise(mean_income = mean(base_income),
              mean_equiv_income = mean(base_equiv_income),
              mean_diff_income = mean(diff_income),
              mean_diff_equiv_income = mean(diff_equiv_income)) %>%
    mutate(percent_change_income = (mean_diff_income / mean_income) * 100,
           percent_change_equiv_income = (mean_diff_equiv_income / mean_equiv_income) * 100) %>%
    select(-mean_income, -mean_equiv_income, -mean_diff_income, -mean_diff_equiv_income) %>%
    pivot_longer(cols = percent_change_income:percent_change_equiv_income,
                 names_prefix = 'percent_change_',
                 names_to = 'variable',
                 values_to = 'change')
  
  ggplot(combined, aes(x = time, y = change, group = variable, color = variable)) +
    geom_smooth() +
    geom_hline(yintercept = 0, linetype = 'dashed') +
    labs(title = paste0('Percent change: ', filter.var, ' == ', subpop),
         subtitle = int.name) +
    xlab('Year') +
    ylab('Percent Change')
}

income_equivinc_percent_change_batch_subpop(base.batch, energy.batch, int.name = 'Energy Crisis', filter.var = 'ethnicity', subpop = 'PAK')
income_equivinc_percent_change_batch_subpop(base.batch, energy.batch, int.name = 'Energy Crisis', filter.var = 'urban', subpop = '1')
income_equivinc_percent_change_batch_subpop(base.batch, energy.batch, int.name = 'Energy Crisis', filter.var = 'urban', subpop = '2')
income_equivinc_percent_change_batch_subpop(base.batch, energy.batch, int.name = 'Energy Crisis', filter.var = 'income.quint', subpop = '1')
income_equivinc_percent_change_batch_subpop(base.batch, energy.batch, int.name = 'Energy Crisis', filter.var = 'income.quint', subpop = '5')
```

## All Subgroups

```{r}
equivinc_percent_change_batch_subpop <- function(base.batch, int.batch, int.name, group.var) {
  base.inc <- base.batch %>%
    select(pidp, time, run_id, equivalent_income, weight, all_of(group.var)) %>%
    group_by(time, run_id, .data[[group.var]]) %>%
    summarise(base_equiv_income = weighted.mean(equivalent_income, w = weight, na.rm = TRUE))
  
  int.inc <- int.batch %>%
    select(pidp, time, run_id, equivalent_income, weight, all_of(group.var)) %>%
    group_by(time, run_id, .data[[group.var]]) %>%
    summarise(int_equiv_income = weighted.mean(equivalent_income, w = weight, na.rm = TRUE))
  
  combined <- merge(base.inc, int.inc, by = c('time', 'run_id', group.var))
  combined[[group.var]] <- as.factor(combined[[group.var]])
  
  combined$diff_equiv_income <- combined$int_equiv_income - combined$base_equiv_income
  
  combined <- combined %>%
    group_by(time, .data[[group.var]]) %>%
    summarise(mean_equiv_income = mean(base_equiv_income),
              mean_diff_equiv_income = mean(diff_equiv_income)) %>%
    mutate(percent_change_equiv_income = (mean_diff_equiv_income / mean_equiv_income) * 100) %>%
    select(-mean_equiv_income, -mean_diff_equiv_income)# %>%
    #pivot_longer(cols = percent_change_income:percent_change_equiv_income,
    #             names_prefix = 'percent_change_',
    #             names_to = 'variable',
    #             values_to = 'change')
  
  ggplot(combined, aes(x = time, y = percent_change_equiv_income, group = .data[[group.var]], color = .data[[group.var]])) +
    geom_smooth() +
    geom_hline(yintercept = 0, linetype = 'dashed') +
    labs(title = paste0('Percent change by ', group.var), subtitle = int.name) +
    xlab('Year') +
    ylab('Percent Change')
}

S7_ordinal_pathway_vis_batch <- function(base.bat, int.bat, int.name, var) {
  base.hous <- base.bat %>%
    select(pidp, time, run_id, all_of(var)) %>%
    group_by(time, run_id, .data[[var]]) %>%
    count() %>%
    group_by(time, run_id) %>%
    mutate(total = sum(n)) %>%
    mutate(prop = n / total) %>%
    select(-n, -total) %>%
    mutate(source = 'Baseline')
  
  inc.hous <- int.bat %>%
    select(pidp, time, run_id, all_of(var)) %>%
    group_by(time, run_id, .data[[var]]) %>%
    count() %>%
    group_by(time, run_id) %>%
    mutate(total = sum(n)) %>%
    mutate(prop = n / total) %>%
    select(-n, -total) %>%
    mutate(source = int.name)
  
  combined <- rbind(base.hous, inc.hous)
  combined[[var]] <- as.factor(combined[[var]])
  
  p1 <- ggplot(combined, aes(x = time, y = prop, group = interaction(.data[[var]], source), color = .data[[var]], linetype = source)) +
    geom_smooth()
  
  print(p1)
  
  base.hous2 <- base.bat %>%
    select(pidp, time, run_id, all_of(var)) %>%
    group_by(time, run_id, .data[[var]]) %>%
    count() %>%
    group_by(time, run_id) %>%
    mutate(total = sum(n)) %>%
    mutate(prop = (n / total) * 100) %>%
    select(-n, -total) %>%
    rename(Baseline = prop)
  
  int.hous2 <- int.bat %>%
    select(pidp, time, run_id, all_of(var)) %>%
    group_by(time, run_id, .data[[var]]) %>%
    count() %>%
    group_by(time, run_id) %>%
    mutate(total = sum(n)) %>%
    mutate(prop = (n / total) * 100) %>%
    select(-n, -total) %>%
    rename(int = prop)
  
  combined2 <- merge(base.hous2, int.hous2, by = c('time', 'run_id', var))
  
  combined2[[var]] <- as.factor(combined2[[var]])
  
  combined2$diff <- combined2$int - combined2$Baseline
  
  p2 <- ggplot(combined2, aes(x = time, y = diff, group = .data[[var]], color = .data[[var]]), fill = .data[[var]]) +
    geom_smooth() +
    labs(title = paste0(int.name, ': Change from Baseline')) +
    xlab('Year') +
    ylab('Change')
  
  print(p2)
}
```

### Energy Crisis

```{r}
equivinc_percent_change_batch_subpop(base.batch, energy.batch, int.name = 'Energy Crisis', group.var = 'income.quint')
equivinc_percent_change_batch_subpop(base.batch, energy.batch, int.name = 'Energy Crisis', group.var = 'ethnicity')
equivinc_percent_change_batch_subpop(base.batch, energy.batch, int.name = 'Energy Crisis', group.var = 'urban')
equivinc_percent_change_batch_subpop(base.batch, energy.batch, int.name = 'Energy Crisis', group.var = 'age.group')
equivinc_percent_change_batch_subpop(base.batch, energy.batch, int.name = 'Energy Crisis', group.var = 'region')
equivinc_percent_change_batch_subpop(base.batch, energy.batch, int.name = 'Energy Crisis', group.var = 'job_sec')
equivinc_percent_change_batch_subpop(base.batch, energy.batch, int.name = 'Energy Crisis', group.var = 'education_state')
equivinc_percent_change_batch_subpop(base.batch, energy.batch, int.name = 'Energy Crisis', group.var = 'nkids_ind')
equivinc_percent_change_batch_subpop(base.batch, energy.batch, int.name = 'Energy Crisis', group.var = 'housing_tenure')

S7_ordinal_pathway_vis_batch(base.batch, energy.batch, 'EnergyCrisis', 'S7_housing_quality')
S7_ordinal_pathway_vis_batch(base.batch, energy.batch, 'EnergyCrisis', 'S7_neighbourhood_safety')
S7_ordinal_pathway_vis_batch(base.batch, energy.batch, 'EnergyCrisis', 'S7_mental_health')
S7_ordinal_pathway_vis_batch(base.batch, energy.batch, 'EnergyCrisis', 'S7_physical_health')
S7_ordinal_pathway_vis_batch(base.batch, energy.batch, 'EnergyCrisis', 'loneliness')
S7_ordinal_pathway_vis_batch(base.batch, energy.batch, 'EnergyCrisis', 'S7_labour_state')
```


### Living Wage

```{r}
equivinc_percent_change_batch_subpop(base.batch, wage.batch, int.name = 'Living Wage', group.var = 'income.quint')
equivinc_percent_change_batch_subpop(base.batch, wage.batch, int.name = 'Living Wage', group.var = 'ethnicity')
equivinc_percent_change_batch_subpop(base.batch, wage.batch, int.name = 'Living Wage', group.var = 'urban')
equivinc_percent_change_batch_subpop(base.batch, wage.batch, int.name = 'Living Wage', group.var = 'age.group')
equivinc_percent_change_batch_subpop(base.batch, wage.batch, int.name = 'Living Wage', group.var = 'region')
equivinc_percent_change_batch_subpop(base.batch, wage.batch, int.name = 'Living Wage', group.var = 'job_sec')
equivinc_percent_change_batch_subpop(base.batch, wage.batch, int.name = 'Living Wage', group.var = 'education_state')
equivinc_percent_change_batch_subpop(base.batch, wage.batch, int.name = 'Living Wage', group.var = 'nkids_ind')
equivinc_percent_change_batch_subpop(base.batch, wage.batch, int.name = 'Living Wage', group.var = 'housing_tenure')

S7_ordinal_pathway_vis_batch(base.batch, wage.batch, 'Living Wage', 'S7_housing_quality')
S7_ordinal_pathway_vis_batch(base.batch, wage.batch, 'Living Wage', 'S7_neighbourhood_safety')
S7_ordinal_pathway_vis_batch(base.batch, wage.batch, 'Living Wage', 'S7_mental_health')
S7_ordinal_pathway_vis_batch(base.batch, wage.batch, 'Living Wage', 'S7_physical_health')
S7_ordinal_pathway_vis_batch(base.batch, wage.batch, 'Living Wage', 'loneliness')
S7_ordinal_pathway_vis_batch(base.batch, wage.batch, 'Living Wage', 'S7_labour_state')
```

### All Child

```{r}
equivinc_percent_change_batch_subpop(base.batch, child.batch, int.name = 'AllChild', group.var = 'income.quint')
equivinc_percent_change_batch_subpop(base.batch, child.batch, int.name = 'AllChild', group.var = 'ethnicity')
equivinc_percent_change_batch_subpop(base.batch, child.batch, int.name = 'AllChild', group.var = 'urban')
equivinc_percent_change_batch_subpop(base.batch, child.batch, int.name = 'AllChild', group.var = 'age.group')
equivinc_percent_change_batch_subpop(base.batch, child.batch, int.name = 'AllChild', group.var = 'region')
equivinc_percent_change_batch_subpop(base.batch, child.batch, int.name = 'AllChild', group.var = 'job_sec')
equivinc_percent_change_batch_subpop(base.batch, child.batch, int.name = 'AllChild', group.var = 'education_state')
equivinc_percent_change_batch_subpop(base.batch, child.batch, int.name = 'AllChild', group.var = 'nkids_ind')
equivinc_percent_change_batch_subpop(base.batch, child.batch, int.name = 'AllChild', group.var = 'housing_tenure')

S7_ordinal_pathway_vis_batch(base.batch, child.batch, 'AllChild', 'S7_housing_quality')
S7_ordinal_pathway_vis_batch(base.batch, child.batch, 'AllChild', 'S7_neighbourhood_safety')
S7_ordinal_pathway_vis_batch(base.batch, child.batch, 'AllChild', 'S7_mental_health')
S7_ordinal_pathway_vis_batch(base.batch, child.batch, 'AllChild', 'S7_physical_health')
S7_ordinal_pathway_vis_batch(base.batch, child.batch, 'AllChild', 'loneliness')
S7_ordinal_pathway_vis_batch(base.batch, child.batch, 'AllChild', 'S7_labour_state')
```

### Poverty Child

```{r}
equivinc_percent_change_batch_subpop(base.batch, pov.batch, int.name = 'PovertyChild', group.var = 'income.quint')
equivinc_percent_change_batch_subpop(base.batch, pov.batch, int.name = 'PovertyChild', group.var = 'ethnicity')
equivinc_percent_change_batch_subpop(base.batch, pov.batch, int.name = 'PovertyChild', group.var = 'urban')
equivinc_percent_change_batch_subpop(base.batch, pov.batch, int.name = 'PovertyChild', group.var = 'age.group')
equivinc_percent_change_batch_subpop(base.batch, pov.batch, int.name = 'PovertyChild', group.var = 'region')
equivinc_percent_change_batch_subpop(base.batch, pov.batch, int.name = 'PovertyChild', group.var = 'job_sec')
equivinc_percent_change_batch_subpop(base.batch, pov.batch, int.name = 'PovertyChild', group.var = 'education_state')
equivinc_percent_change_batch_subpop(base.batch, pov.batch, int.name = 'PovertyChild', group.var = 'nkids_ind')
equivinc_percent_change_batch_subpop(base.batch, pov.batch, int.name = 'PovertyChild', group.var = 'housing_tenure')

S7_ordinal_pathway_vis_batch(base.batch, pov.batch, 'PovertyChild', 'S7_housing_quality')
S7_ordinal_pathway_vis_batch(base.batch, pov.batch, 'PovertyChild', 'S7_neighbourhood_safety')
S7_ordinal_pathway_vis_batch(base.batch, pov.batch, 'PovertyChild', 'S7_mental_health')
S7_ordinal_pathway_vis_batch(base.batch, pov.batch, 'PovertyChild', 'S7_physical_health')
S7_ordinal_pathway_vis_batch(base.batch, pov.batch, 'PovertyChild', 'loneliness')
S7_ordinal_pathway_vis_batch(base.batch, pov.batch, 'PovertyChild', 'S7_labour_state')
```




```{r}

```

