---
title: "IJM Papers Notebook"
output:
  pdf_document: default
  html_document:
    df_print: paged
---

# Before Running this Notebook. Use the branch IJM_paper_June_2025.


1.  In an Unix terminal clone the MINOS GitHub repository www.github.com/Leeds-MRG/Minos. Once downloaded, move into the Minos directory and switch to the required branch using command 'git checkout IJM_paper_June_2025'.

2. Follow MINOS README instructions to install the required conda environment and datasets. This includes using Understanding Society data version 20 http://doi.org/10.5255/UKDA-SN-6614-20.

3. Activate the conda environment minos_conda_micromamba produced by these instructions.

4. Run make IJM_data in unix terminal to process all UKHLS data required to run this notebook.

5. Run this notebook. This will take a few days to run the full MICE algorithm. A cached option is available on request. I recommend a machine with at least 16GB of RAM to run this notebook.

6. All figures and tables will be saved into folder `./IJM_June_2025_plots_and_tables`.

```{r setup}
# Setting working directory to top of MINOS repository.
library(here)
knitr::opts_knit$set(root.dir = here::here("../IJM_Minos/"))
getwd()
```

```{r "preamble"}
# Importing packages. May need to install some packages.
source(here::here("minos", "transitions", "utils.R"))
source(here::here("minos", "transitions", "transition_model_functions.R"))
source(here::here("minos", "transitions", "paper_1_plots.R"))

library(dplyr)
library(texreg)
library(lme4)
library(glmnet)
library(mice)
library(sjPlot)
library(visreg)
library(ggplot2)
library(ggpattern)
library(VIM)
library(caret)
library(tidyverse)
library(performance)
library(broom.mixed)
library(ggridges)
library(ggmice)
library(MASS)
library(qpcR)
library(cv)
library(Rcpp)

# Set save directories.
save.path <- "IJM_June_2025_plots_and_tables/"
create.if.not.exists(save.path)
#raw.data.dir <- "data/raw_US/"
raw.data.dir  <- "data/composite_US/"
mice.data.dir <- "data/composite_US/"
final.data.dir <- mice.data.dir
# set.seed(8) # set seed if require fixed MICE results.
```

# Section 2: Baseline SF-12 MCS Model

This section formats raw Understanding Society (UKHLS) data and fits an Ordinary Least Squares model estimating Short Form 12 Mental Component Score (SF-12 MCS).

```{r "raw_data_processing"}

# Load Understanding Society data for the years 2011-2013.
filelist <- list.files(raw.data.dir,
                       include.dirs = FALSE,
                       full.names = TRUE,
                       pattern = '[0-9]{4}_US_cohort.csv')[3:5]#[21:23] # get files for 2011-2013.
raw.data <- do.call(rbind, lapply(filelist, read.csv))

# baseline OLS model formula. 
raw_model_formula_string <- "I(scale(log((SF_12)+10))) ~ factor(sex) + 
                  relevel(factor(ethnicity), ref='WBI') + 
                  scale(age) + 
                  factor(education_state) + 
                  factor(labour_state) + 
                  relevel(factor(NSSEC), ref=1) +
                  relevel(factor(region), ref='London') +
                  scale(hh_income)"

# Calculate required variables for regression to run. 
raw_model_formula <- as.formula(raw_model_formula_string)
variables <- all.vars(raw_model_formula)

# Get only needed variables and replace missing codes with NA.
raw.data <- update_column_names(raw.data)
raw.data <- raw.data[, append(variables, c("time", 'pidp','hidp', 'weight'))]
raw.data <- replace.missing(raw.data)

# Use raw data both with and without incomplete columns containing missing data removed.
full.raw.data<- raw.data
raw.data <- drop_na(raw.data)

sf12.mean <- mean(log(raw.data$SF_12+10))
sf12.std <- sqrt(var(log(raw.data$SF_12+10)))
```

This section fits the OLS model estimating SF-12 MCS and provides model coefficients in a LATEX table.

```{r "OLS"}

# Fit SF-12 MCS baseline OLS model.
sf12.lm <- lm(raw_model_formula_string,
              data= raw.data)

#Save Coefficients.
write_coefs <- T
if (write_coefs)
{
  texreg_file <- paste0(save.path, 'table_2_SF12_OLS_coefficients.txt')
  tex_label <- paste0("table: baseline_OLS_coefficients") 
  tex_headers <- c(texreg::names2latex("Baseline SF_12 OLS"))
  tex_caption <- texreg::names2latex(get_tex_table_caption("SF_12", "ols"))
  ols_coef_names <- c("Intercept", "Sex: Male vs Female",
                  "Ethnicity: BAN vs WBI",
                  "Ethnicity: BLA vs WBI",
                  "Ethnicity: BLC vs WBI",
                  "Ethnicity: CHI vs WBI",
                  "Ethnicity: IND vs WBI",
                  "Ethnicity: MIX vs WBI",
                  "Ethnicity: OAS vs WBI",
                  "Ethnicity: OBL vs WBI",
                  "Ethnicity: OTH vs WBI",
                  "Ethnicity: PAK vs WBI",
                  "Ethnicity: WHO vs WBI",
                  "Age",
                  "Education State: 1 vs 0",
                  "Education State: 2 vs 0",
                  "Education State: 3 vs 0",
                  "Education State: 5 vs 0",
                  "Education State: 6 vs 0",
                  "Education State: 7 vs 0",
                  "Labour State: FT Education vs Family Care",
                  "Labour State: FT Employment vs Family Care",
                  "Labour State: Job Seeking vs Family Care",
                  "Labour State: Not Working vs Family Care",
                  "Labour State: PT Employed vs Family Care",
                  "NSSEC: 0 vs. 1",
                  "NSSEC: 2 vs. 1",
                  "NSSEC: 3 vs. 1",
                  "NSSEC: 4 vs. 1",
                  "NSSEC: 5 vs. 1",
                  "NSSEC: 6 vs. 1",
                  "NSSEC: 7 vs. 1",
                  "NSSEC: 8 vs. 1",
                  "Region: East Midlands vs London",
                  "Region: East of England vs London",
                  "Region: North East vs London",
                  "Region: North West vs London",
                  "Region: Northern Ireland vs London",
                  "Region: Scotland vs London",
                  "Region: South East vs London",
                  "Region: South West vs London",
                  "Region: Wales vs London",
                  "Region: West Midlands vs London",
                  "Region: Yorkshire & Humber vs London",
                  "Household Income")
  texreg(sf12.lm, # what model to save coefs for. 
         file=texreg_file,  # where to save.
         custom.model.names = tex_headers, # title of table.
         custom.coef.names = ols_coef_names,
         stars = c(0.001, 0.01, 0.05), # p-value significance symbols. 
         digits=4, # p values significant figures.
         caption=tex_caption, # \caption command option. 
         label = tex_label, # \label command option. 
         dcolumn=T,# nice column alignment. 
         booktabs=T, # nice hlines. (recommended)
         tabular=T,# tabular env.
         single.row = T, # nicer one row formatting.
         longtable=T, # allows tables to wrap over pages
         use.packages=F, # don't add \usepackage commands to allow for direct importing of files as inputs
         fontsize='small') # tiny font
}
```


This section estimates the root mean squared error (RMSE) for the OLS model.

```{r raw cross val}
# Baseline cross val.
# Estimating the root mean squared error score of the baseline OLS model using five-fold cross-validation.

trControl <- trainControl(method = "cv", number=5, trim=T, verboseIter = TRUE, savePredictions = TRUE)

raw.cross.val.sf12.model <- train(as.formula(raw_model_formula_string), data = raw.data,
               method = "lm",
               trControl = trControl)


raw.RMSE.statistics <- raw.cross.val.sf12.model$pred %>% 
  group_by(Resample) %>%
  mutate(obs =  exp(sf12.std * obs + sf12.mean) - 10) %>%
  mutate(pred =  exp(sf12.std * pred + sf12.mean) - 10) %>%
  summarise(output_RMSE=caret::RMSE(pred, obs)) %>%
  summarise(mean = mean(output_RMSE), std = sd(output_RMSE))

print("Raw RMSE Statistics: ")
print(raw.RMSE.statistics$mean)
print(raw.RMSE.statistics$std)


#raw.sf12.obs <- exp(sf12.std * raw.cross.val.sf12.model$pred$obs  + sf12.mean) - 10
#raw.sf12.preds <- exp(sf12.std * raw.cross.val.sf12.model$pred$pred  + sf12.mean) - 10

#print(caret::RMSE(raw.sf12.preds, raw.sf12.obs))
#print(sd((raw.sf12.obs-raw.sf12.preds)**2))

#print(raw.cross.val.sf12.model$results$RMSE)
#print(raw.cross.val.sf12.model$results$RMSESD)
#raw.cross.val.sf12.preds <- exp(sf12.mean + sf12.std* predict(raw.cross.val.sf12.model, newdata=mice.data))-10
#print(rmse2(raw.data$SF_12, raw.cross.val.sf12.preds))
```

# Section 3: Presentation of the OLS model

This section produces diagnostics for the OLS model providing evidence for why this model fails and how it can be improved.

```{r}

# Diagnostic plots for OLS presentation. 
# Plot coefficient forest plot, 
raw_forest_plot(sf12.lm, paste0(save.path, "figure_3a_presentation_forest.pdf"))
#log_forest_plot(sf12.lm, paste0(save.path, "figure_3a_presentation_forest.pdf"))
residual_density_plot(res=resid(sf12.lm), file_name=paste0(save.path, "figure_3b_presentation_residual_density.pdf"), guide="normal")
qq_plot(resid(sf12.lm), paste0(save.path, "figure_3c_presentation_qq.pdf"))

# Creating scale-location plot using model residual errors.
squareRootRes <- sqrt(abs(scale(resid(sf12.lm))))
fitted_residuals <- as.data.frame(cbind(fitted(sf12.lm), squareRootRes))
colnames(fitted_residuals) <- c("fitted", "sqrt_residuals")
fitted_residual_plot(fitted_residuals, paste0(save.path, "figure_3d_presentation_scale_location_plot.pdf"))

# Performing nwcasting estimating SF-12 MCS scores from 2014-2020 using 2013 data.
start.data <- raw.data[which(raw.data$time==2013),]
start.data.colnames <- colnames(start.data)
start.data.colnames[which( colnames(start.data)=="job_sec" )] <- "NSSEC"
start.data.colnames[which( colnames(start.data)=="hh_netinc" )] <- "hh_income"
start.data.colnames[which( colnames(start.data)=="labour_state_raw" )] <- "labour_state"
colnames(start.data) <- start.data.colnames
handover.data <- start.data[, c("pidp", "SF_12", "hidp", "time")]
rolling.data <- start.data 

sf12.mean <- mean(log(raw.data$SF_12+10))
sf12.std <- sqrt(var(log(raw.data$SF_12+10)))

for (i in 1:8){
  rolling.data$SF_12 <- ((exp(sf12.mean + sf12.std * predict(sf12.lm, rolling.data))-10))
#  start.data$SF_12 <- predict(sf12.lm, rolling.data)
  rolling.data[, 'time'] <- rolling.data[, 'time'] +1
  handover.data <- rbind(handover.data, rolling.data[, c("pidp", "hidp", "SF_12", "time")])
}

# Plotting handovers using ridgeline plots.
handover_boxplots(full.raw.data, handover.data, "SF_12", save.path, "ols_SF12_boxplot")
density_ridges(full.raw.data, "SF_12", save=TRUE, save.path=save.path, filename.tag = "figure_4a_ols_raw_ridges")
density_ridges(handover.data, "SF_12", save=TRUE, save.path=save.path, filename.tag = "figure_4b_ols_handover_ridges")
```

# Section 4: Missingness

This section processes Understanding Society data again including further variables required for multiple imputation chained equations (MICE) imputation. The missing data structure for Understanding Society data is also provided.

```{r mice preprocessing}
# Load in raw data again preprocessing for MICE imputation.
mice.filelist <- list.files(mice.data.dir,
                       include.dirs = FALSE,
                       full.names = TRUE,
                       pattern = '[0-9]{4}_US_cohort.csv')
mice.data <- do.call(rbind, lapply(mice.filelist, read.csv))
mice.data <- update_column_names(mice.data)

# Define the regression model formula for the OLS model using MICE imputation.
# Note more variables are included due to imputation that cannot be used in the baseline model.
mice_formula_string <- "I(scale(log(SF_12+10))) ~ 
                        factor(sex) + 
                        relevel(factor(ethnicity), ref='WBI') + 
                        scale(age) + 
                        factor(education_state) + 
                        factor(labour_state) + 
                        relevel(factor(NSSEC), ref='1') +
                        relevel(factor(region), ref='London') +
                        scale(hh_income) + 
                        scale(I(hh_income**2)) +
                        relevel(factor(housing_quality), ref='Low') +
                        factor(neighbourhood_safety) + 
                        factor(loneliness) +
                        nutrition_quality +
                        ncigs"

# Get required UKHLS variables and replace missing value codes.
mice_model_formula <- as.formula(mice_formula_string)
variables <- all.vars(mice_model_formula)
mice.data <- replace.missing(mice.data)
full.mice.data <- mice.data
# Preserving key columns that cannot be imputed. These are used later.
# Preserving time, sample weights, and identifiers.


mice.pidp <- mice.data[which(mice.data$time %in% seq(2011,2018)), "pidp"]
mice.hidp <- mice.data[which(mice.data$time %in% seq(2011,2018)), "hidp"]
mice.time <- mice.data[which(mice.data$time %in% seq(2011,2018)), "time"]
mice.weights <- mice.data[which(mice.data$time %in% seq(2011,2018)), "weight"]

mice.2013.pidp <- mice.data[which(mice.data$time %in% c(2011, 2012, 2013)), "pidp"]
mice.2013.hidp <- mice.data[which(mice.data$time %in% c(2011, 2012, 2013)), "hidp"]
mice.2013.time <- mice.data[which(mice.data$time %in% c(2011, 2012, 2013)), "time"]
mice.2013.weights <- mice.data[which(mice.data$time %in% c(2011, 2012, 2013)), "weight"]

mice.2018.pidp <- mice.data[which(mice.data$time %in% c(2016, 2017, 2018)), "pidp"]
mice.2018.hidp <- mice.data[which(mice.data$time %in% c(2016, 2017, 2018)), "hidp"]
mice.2018.time <- mice.data[which(mice.data$time %in% c(2016, 2017, 2018)), "time"]
mice.2018.weights <- mice.data[which(mice.data$time %in% c(2016, 2017, 2018)), "weight"]
```


This section performs MICE imputation and saves model coefficients.

```{r MICE}

# Plotting missing data structure for 2011-2013 UKHLS data.
aggr_columns <- c("SF_12",
                 "NSSEC",
                 "education_state",
                 "labour_state", 
                 "ethnicity", 
                 "hh_income",
                 "neighbourhood_safety",
                 "loneliness",
                 "ncigs",
                 'nutrition_quality'
)
aggr_labels <- c("SF-12 MSC",
                 "NSSEC",
                 "Education State",
                 "Labour State", 
                 "Ethnicity", 
                 "Household Income",
                 "Neighbourhood Safety",
                 "Loneliness",
                 "Number of cigarettes",
                 'Nutrition Quality'
)
pdf(paste0(save.path, "figure_5a_total_missingness_structure1.pdf"))
aggr(mice.data[,aggr_columns], sortVars=T, prop=T, combined=F,varheight=T, oma=c(10,5,1,2), gap=0, 
     ylabs=c("Percentage of Missing Values", "Combinations of Missing Values"), labels=aggr_labels)
dev.off()

# Defining columns that are IMPUTED in MICE imputation.
imp_columns <- c("SF_12",
                 'sex',
                 "NSSEC",
                 "education_state",
                 "labour_state", 
                 "region", 
                 "ethnicity", 
                 "age", 
                 "time", 
                 "hh_income",
                 "housing_quality",
                 "neighbourhood_safety",
                 "loneliness",
                 "ncigs",
                 'nutrition_quality'
)

# Defining all columns used in MICE imputation. Not all columns are imputed. All columns are used to predict imputed values.
mice_columns <- c("age", 
                  "region", 
                  #"heating", 
                  "NSSEC", 
                  "ncigs",
                  "education_state",            
                  "ethnicity",
                  "loneliness",
                  "sex", 
                  "SF_12",
                  #"SF_12p",
                  #"smoker",
                  "nkids",       
                  "behind_on_bills",
                  "financial_situation",
                  "future_financial_situation",
                  "likely_move",
                  "ghq_depression",
                  "ghq_happiness",
                  "clinical_depression", 
                  "scsf1",
                  "health_limits_social",
                  #"hhsize",
                  #"housing_tenure",
                  #"urban", 
                  "housing_quality",
                  "hh_income",
                  "neighbourhood_safety",
                  "labour_state",
                  #"yearly_energy",
                  "nutrition_quality"
                  #"hh_comp", 
                  #"marital_status"
)

# Categorical variables must be declared for the MICE package to work.
mice.data$ethnicity <- factor(mice.data$ethnicity)
mice.data$region <- factor(mice.data$region)
mice.data$NSSEC <- factor(mice.data$NSSEC)
mice.data$education_state <- factor(mice.data$education_state)
mice.data$loneliness <- factor(mice.data$loneliness)
mice.data$ethnicity <- factor(mice.data$ethnicity)
mice.data$sex <- factor(mice.data$sex)

mice.data$ghq_happiness <- factor(mice.data$ghq_happiness)
mice.data$ghq_depression <- factor(mice.data$ghq_depression)
mice.data$clinical_depression <- factor(mice.data$clinical_depression)
mice.data$scsf1 <- factor(mice.data$scsf1)
mice.data$health_limits_social <- factor(mice.data$health_limits_social)
mice.data$housing_quality <- factor(mice.data$housing_quality)
mice.data$loneliness <- factor(mice.data$loneliness)
mice.data$neighbourhood_safety <- factor(mice.data$neighbourhood_safety)
mice.data$labour_state <- factor(mice.data$labour_state)


# MICE imputation is time intensive. This option allows for reloading previous MICE imputation for faster plotting.
# Setting this to F means results will take at least 2 days.
load_cache <- T
if (load_cache) {
  mice_set <- readRDS("data/transitions/MICE_set.rds")
} else {
  # Number of mice imputations and number of imputation steps per population.
  n_iter <- 10
  max_iter <- 10
  #minimum iterations for debugging.
  #n_iter <- 1
  #max_iter <- 1
  # run MICE algorithm.
  mice_set <- mice(data = mice.data[mice.data$time %in%  seq(2011, 2018), mice_columns],
                   m = n_iter, maxit = max_iter,
                   remove.collinear=T)
  
  # future mice is parallelised version of MICE.
  #mice_set <- with_progress(futuremice(data = mice.data[, mice_columns], #method=method,
  #                m = n_iter, maxit = max_iter,
  #                 remove.collinear=T, quiet=F,
  #                 progressor = progressr::handlers("progress")))
  create.if.not.exists(here::here("data", "transitions"))
  saveRDS(mice_set, here::here("data","transitions", "MICE_set.rds"))
}

```


This section applies the OLS SF-12 MCS model to all 30 MICE imputed populations. 
These 30 models are pooled together producing a final set of model coefficients estimating SF-12 MCS.
Diagnostic plots assessing MICE convergence and model goodness of fit are also provided.

```{r mice_output}

# Extract imputed data from mids object produced by MICE() function.
mice.long <- complete(mice_set, action = "long", include=T) #
# Reassign variables that could not be imputed. Weights and IDs.
mice.long$pidp <- mice.pidp
mice.long$hidp <- mice.hidp
mice.long$weight <- mice.weights
mice.long$time <- mice.time
mice.long <- update_column_names(mice.long)
mice_set.full <- as.mids(mice.long)

# Looking at data from 2011-2013.
mice.long.subset <- mice.long[which(mice.long$time %in% c(2011, 2012, 2013)), ]


# Bug in as.mids function that can't cast mice.long.subset to a mids object. nice fix here.
# https://stats.stackexchange.com/questions/138769/something-wrong-with-as-mids-from-mice-package-in-r
as.mids2 <- function (data, .imp = 1, .id = 2) 
    {
      # paste added to get numerical value if .imp is factor
      ini <- mice(data[data[, .imp] == 0, -c(.imp, .id)], m = max(as.numeric(paste(data[, .imp]))), maxit = 0)
      names <- names(ini$imp)
          if (!is.null(.id)) {
            rownames(ini$data) <- data[data[, .imp] == 0, .id]
          }
          for (i in 1:length(names)) {
            # -1 removed and paste added to get numerical value if .imp is factor
            for (m in 1:(max(as.numeric(paste(data[, .imp]))))) {
              if (!is.null(ini$imp[[i]])) {
                indic <- data[, .imp] == m & is.na(data[data[, .imp] == 0, names[i]])
                ini$imp[[names[i]]][m] <- data[indic, names[i]]
          }
        }
      }
      return(ini)
}

# cast data to MIDS object so data can be pooled.
mice_set.subset <- as.mids2(mice.long.subset) 

# Make MICE convergence plot.
pdf(paste0(paste0(save.path,"figure_5b_ols_mice_convergence.pdf")))
#print(plot(mice_set, SF_12 = SF_12 ~ .it | .ms))
MICE_trace_plot <- plot_trace(mice_set, "SF_12") + theme(legend.position="none")
MICE_trace_plot$data$vrb <- "SF-12 MCS"
plot(MICE_trace_plot)
dev.off()

# Fit OLS model to all 30 MICE populations and pool together into one model.
mice.sf12.lm <- with(mice_set.subset, lm(as.formula(mice_formula_string)))
final.pool<- pool(mice.sf12.lm)

# Summary statistics for the pooled OLS model.
pooled_lm <- mice.sf12.lm$analyses[[1]]
pool.sum <- summary(final.pool)
pooled_lm$coefficients = pool.sum$estimate
mice.preds<- predict(pooled_lm)
pool.r.squared(final.pool) # getting r squared.

# mids object can't make most of the summary plots needed.
# Cast mids object to an lm predict object.
# Use a dummy lm model and overwrite model coefficients, standard errors, and t/p values.
mice.lm.object <- summary(lm(mice_formula_string, data = complete(mice_set.subset)))
mice.lm.object$coefficients[,1] <- pool.sum$estimate
mice.lm.object$coefficients[,2] <- pool.sum$std.error
mice.lm.object$coefficients[,3] <- pool.sum$statistic
mice.lm.object$coefficients[,4] <- pool.sum$p.value

# Making residual density plot for pooled OLS model. 
res <- as.data.frame(predict(pooled_lm))
real <- as.data.frame(mice.data$SF_12)
res$type <- c("Predicted")
real$type <- c("Real")
colnames(res) <- c("SF12", 'type')
colnames(real) <- c("SF12", 'type')
hist.data <- rbind(res,real)
hist.data <- tidyr::drop_na(hist.data)

res <- as.data.frame(resid(pooled_lm))
residual_density_plot(res, paste0(save.path,'mice_ols_densities.pdf'), guide='normal')

# making forest plots and qq plot for MICE model diagnostics.
#forest_plot(mice.lm.object, paste0(save.path,'figure_5c_mice_SF12_forest.pdf'))
mice_forest_plot(mice.lm.object, paste0(save.path,'figure_5c_mice_SF12_forest.pdf'))
qq_plot(resid(mice.lm.object), paste0(save.path, "figure_5d_mice_qq.pdf"))

# Writing pooled MICE OLS model coefficients to a LATEX table.
write_coefs <- T
if (write_coefs)
{
  mice_coefs_names <- c("Intercept", "Sex: Male vs Female",
                   "Ethnicity: BAN vs WBI",
                   "Ethnicity: BLA vs WBI",
                   "Ethnicity: BLC vs WBI",
                   "Ethnicity: CHI vs WBI",
                   "Ethnicity: IND vs WBI",
                   "Ethnicity: MIX vs WBI",
                   "Ethnicity: OAS vs WBI",
                   "Ethnicity: OBL vs WBI",
                   "Ethnicity: OTH vs WBI",
                   "Ethnicity: PAK vs WBI",
                   "Ethnicity: WHO vs WBI",
                   "Age",
                   "Education State: 1 vs 0",
                   "Education State: 2 vs 0",
                   "Education State: 3 vs 0",
                   "Education State: 5 vs 0",
                   "Education State: 6 vs 0",
                   "Education State: 7 vs 0",
                   "Labour State: FT Education vs Family Care",
                   "Labour State: FT Employment vs Family Care",
                   "Labour State: Job Seeking vs Family Care",
                   "Labour State: Not Working vs Family Care",
                   "Labour State: PT Employed vs Family Care",
                   "NSSEC: 0 vs. 1",
                   "NSSEC: 2 vs. 1",
                   "NSSEC: 3 vs. 1",
                   "NSSEC: 4 vs. 1",
                   "NSSEC: 5 vs. 1",
                   "NSSEC: 6 vs. 1",
                   "NSSEC: 7 vs. 1",
                   "NSSEC: 8 vs. 1",
                   "Region: East Midlands vs London",
                   "Region: East of England vs London",
                   "Region: North East vs London",
                   "Region: North West vs London",
                   "Region: Northern Ireland vs London",
                   "Region: Scotland vs London",
                   "Region: South East vs London",
                   "Region: South West vs London",
                   "Region: Wales vs London",
                   "Region: West Midlands vs London",
                   "Region: Yorkshire & Humber vs London",
                   "Household Income",
                   "Household Income Squared",
                   "Housing Quality: High vs Low",
                   "Housing Quality: Medium vs Low",
                   "Neighbourhood Safety: 2 vs 1",
                   "Neighbourhood Safety: 3 vs 1",
                   "Loneliness: 2 vs 1",
                   "Loneliness: 3 vs 1",
                   "Nutrition Quality",
                   "Number of Cigarettes")
  
  texreg_file <- paste0(save.path, 'table_5_SF12_MICE_pool_OLS_coefficients.txt')
  tex_label <- paste0("table: MICE_pool_OLS_coefficients") 
  tex_headers <- c(texreg::names2latex("MICE SF_12 OLS Pool"))
  tex_caption <- texreg::names2latex(get_tex_table_caption("SF_12", "ols"))    
  texreg(final.pool, # what model to save coefs for. 
         file=texreg_file,  # where to save.
         custom.model.names = tex_headers, # title of table.
         custom.coef.names = mice_coefs_names,
         stars = c(0.001, 0.01, 0.05), # p-value significance symbols. 
         digits=4, # p values significant figures.
         caption=tex_caption, # \caption command option. 
         label = tex_label, # \label command option. 
         dcolumn=T,# nice column alignment. 
         booktabs=T, # nice hlines. (recommended)
         tabular=T,# tabular env.
         single.row = T, # nicer one row formatting.
         longtable=T, # allows tables to wrap over pages
         use.packages=F, # don't add \usepackage commands to allow for direct importing of files as inputs
         fontsize='small') # tiny font
}
```

# Section 5: Validation and Uncertainty

This section describes how the OLS model is validated as well as methods for testing uncertainty due to missing data and model coefficients.

This section applies five fold cross validation to the OLS model using MICE imputed data. This model is used to forecast from 2013-2020 comparing model output against real data using 'nowcasting'.

## Uncertainty due to calibration data.

```{r mice cross validated nowcasting}
# Apply five fold cross-validation to the OLS model using MICE data.
#trControl <- trainControl(method = "cv", number=5, returnData=F, trim=T, verboseIter = TRUE, savePredictions = TRUE)

mice.sf12.mean <- mean(log(complete(mice_set, 1)$SF_12+10))
mice.sf12.std <- sqrt(var(log(complete(mice_set, 1)$SF_12+10)))


mice.cross.val.sf12.model <- train(as.formula(mice_formula_string), data = complete(mice_set.subset, 1, include=F),
               method = "lm",
               trControl = trControl)



mice.RMSE.statistics <- mice.cross.val.sf12.model$pred %>% 
  group_by(Resample) %>%
  mutate(obs =  exp(mice.sf12.std * obs + mice.sf12.mean) - 10) %>%
  mutate(pred =  exp(mice.sf12.std * pred + mice.sf12.mean) - 10) %>%
  summarise(output_RMSE=caret::RMSE(pred, obs)) %>%
  summarise(mean = mean(output_RMSE), std = sd(output_RMSE))

print("MICE RMSE Statistics: ")
print(mice.RMSE.statistics$mean)
print(mice.RMSE.statistics$std)

#print(mice.cross.val.sf12.model$results$RMSE)
#print(mice.cross.val.sf12.model$results$RMSESD)

#mice.cross.val.sf12.preds <- exp(mice.sf12.mean + mice.sf12.std* predict(mice.cross.val.sf12.model, newdata=mice.data))-10
#rmse2(complete(mice_set.subset, 1)$SF_12, mice.cross.val.sf12.preds)
#print(RMSE(mice.cross.val.sf12.model))

# saving cross-validation OLS model coefficients.
write_coefs <- T
if (write_coefs)
{
  texreg_file <- paste0(save.path, 'table_6_SF12_cross_val_OLS_coefficients.txt')
  tex_label <- paste0("table: ols_cross_val_coefficients") 
  tex_headers <- c(texreg::names2latex("5-Fold Cross Validated SF_12 OLS"))
  tex_caption <- texreg::names2latex(get_tex_table_caption("cv_SF_12", "ols"))    
  texreg(summary(mice.cross.val.sf12.model), # what model to save coefs for. 
         file=texreg_file,  # where to save.
         custom.model.names = tex_headers, # title of table.
         custom.coef.names = mice_coefs_names,
         stars = c(0.001, 0.01, 0.05), # p-value significance symbols. 
         digits=4, # p values significant figures.
         caption=tex_caption, # \caption command option. 
         label = tex_label, # \label command option. 
         dcolumn=T,# nice column alignment. 
         booktabs=T, # nice hlines. (recommended)
         tabular=T,# tabular env.
         single.row = T, # nicer one row formatting.
         longtable=T, # allows tables to wrap over pages
         use.packages=F, # don't add \usepackage commands to allow for direct importing of files as inputs
         fontsize='small') # tiny font
}


# Process MICE imputed data so it can be run using the lm predict function.
# Allows nowcasting to be performed.
crossval.mice.data <- complete(mice_set.full, 1, include = F)
crossval.mice.data <- replace.missing(crossval.mice.data)
crossval.mice.data <- drop_na(crossval.mice.data)
crossval.mice.data <- update_column_names(crossval.mice.data)


# Use the cross-validted OLS model to perform nowcasting from 2013 to 2020.
start.data <- crossval.mice.data[which(crossval.mice.data$time==2013),]
rolling.data <- start.data
handover.data <- rolling.data[, c("pidp", "hidp", "SF_12", "time")]

for (i in 1:8){
  rolling.data$SF_12 <- exp(mice.sf12.mean + mice.sf12.std * predict(mice.cross.val.sf12.model, rolling.data))-10
  rolling.data$SF_12 <- rolling.data$SF_12
  rolling.data[, 'time'] <- rolling.data[, 'time'] +1
  handover.data <- rbind(handover.data, rolling.data[, c("pidp", 'hidp', "SF_12", "time")])
}

# Plot nowcasting results.
handover_boxplots(mice.data[which(mice.data$time>=2014),], handover.data, "SF_12", save.path, "crossval_SF12_boxplot")
density_ridges(mice.data[which(mice.data$time>=2014),], "SF_12", save=TRUE, save.path=save.path, filename.tag = "figure_6a_crossval_mice_raw_ridges")
density_ridges(handover.data[which(handover.data$time>=2014),], "SF_12", save=TRUE, save.path=save.path, filename.tag = "figure_6b_crossval_mice_validation_ridges")

```

## Uncertainty due to model coefficients

This section tests OLS model uncertainty due to model coefficients. Model coefficients are randomly sampled from a multi-variate Normal distribution. 
Multiple randomised models are used to predict SF-12 MCS and compared to determine any significant differences.

```{r random_coefficients}

# Get predict lm model object. Use this object and randomise its model coefficients.
randomised.mice.model.data <- data.frame()
random.mice.lm.object <- lm(mice_formula_string, data = complete(mice_set.subset, 1))


for (i in 1:100) {
  # randomise OLS model coefficients using multivariate random Normal sampling.
  model.choice <- random.mice.lm.object
  model.choice$coefficients <- MASS::mvrnorm(n=1, mu=mice.lm.object$coefficients[, 1], Sigma=vcov(mice.lm.object))

  # Perform nowcasting from 2013-2020 using randomised coefficients
  random.start.data <- crossval.mice.data[which(crossval.mice.data$time==2013),]
  for (j in 1:7){
    random.start.data$SF_12 <- exp(mice.sf12.mean + mice.sf12.std *predict(model.choice, random.start.data))-10
  }
  # estimate SF-12 MCS distribution in 2020 for each randomised model using kernel density estimation.
  individual.density <- density(random.start.data$SF_12)
  new.data.frame <- cbind(individual.density$x, individual.density$y, i)
  colnames(new.data.frame) <- c("SF_12", "Density", "run_id")
  randomised.mice.model.data <- rbind(randomised.mice.model.data, new.data.frame)

}
# Plot SF-12 MCS predicted distributions for each of the 100 models with randomised coefficients.
p <- ggplot(randomised.mice.model.data, aes(x=SF_12, y=Density, group=factor(run_id))) +
     geom_line(alpha=0.1) + ylim(0, 0.15) + xlim(15,60) + xlab("SF-12 MCS") + ylab("Probabilities Densities")
ggsave(paste0(save.path, "/", "figure_7a_randomised_coefficients_2020_density.pdf"))
```


### LASSO and variable selection. 

Model coefficients are tested further using variable selection. The least absolute shrinkage and selection operator (LASSO) method is used to 
identify any model coefficients used in the OLS model that are not statistically significant and could be removed to create a more parsimonious model.

```{r lasso}

# Format MICE data to work with glmnet package.
lasso.data <- tidyr::drop_na(complete(mice_set.subset))
X <- model.matrix(as.formula(mice_formula_string), data=lasso.data)
y <- lasso.data$SF_12
weight <- lasso.data$weight

# apply cross-validated LASSO algorithm.
cv.lasso <- cv.glmnet(X, y, family = "gaussian", weights = weight)
lasso <- glmnet(X, y, alpha = 1,  family = "gaussian", weights = weight)

# Plotting optimal parameter choice for the LASSO using cross-validation using 1se and minimum error rules.
pdf(paste0(save.path, 'figure_8_ols_cv_lasso_2013.pdf'))
plot(cv.lasso, xlab="L1 Regularisation Constraint (log(lambda))", ylab="Mean Squared Error")
dev.off()

# Get two sets of coefficients chosen using minimum error and 1 standard error rules.
lasso.min.coefs <- coef(cv.lasso, s=cv.lasso$lambda.min)
lasso.min.coefs <- lasso.min.coefs[-c(2),] # remove wierd bug where intecept printed twice.
lasso.1se.coefs <- coef(cv.lasso, s=cv.lasso$lambda.1se)
lasso.1se.coefs <- lasso.1se.coefs[-c(2),] # remove wierd bug where intecept printed twice.

lasso_model_names <- c("Minimum Error", "First Standard Error")

# Save to LATEX text file.
texreg_file <- paste0(save.path, 'table_8_SF12_Lasso_coefficients.txt')
tex_label <- paste0("table: sf12_lasso_coefficients") 
tex_headers <- c(texreg::names2latex("Minimum Error"), texreg::names2latex("First Standard Error"))
tex_caption <- texreg::names2latex(get_tex_table_caption("SF_12", "lasso"))    
lasso.min <-createTexreg(coef.names=mice_coefs_names, coef = lasso.min.coefs)
lasso.1se <-createTexreg(coef.names=mice_coefs_names, coef = lasso.1se.coefs)
texreg(c(lasso.min, lasso.1se), # what model to save coefs for. 
       file=texreg_file,  # where to save.
       custom.model.names = tex_headers, # title of table.
       caption=tex_caption, # \caption command option. 
       label = tex_label, # \label command option. 
       dcolumn=T,# nice column alignment. 
       booktabs=T, # nice hlines. (recommended)
       tabular=T,# tabulr env.
       single.row = T, # nicer one row formatting.
       longtable=T, # allows tables to wrap over pages
       use.packages=F, # don't add \usepackage commands to allow for direct importing of files as inputs
       fontsize='small') # tiny font
```


This section explores application of sample weights in the OLS model using sample weights from different years of UKHLS data to determine
any difference in model structure and prediction. 
The aim is to determine if model coefficients change over time due to change in demographics reflected in sample weights.
Weighted regressions are compared using 2013 sample weights, 2013 sample weights projected to 2018, and 2018 sample weights.

```{r weighted_ols}

# Get 2016-2018 UKHLS MICE imputed data.
mice_set.subset.2016_2018 <- mice.long[which(mice.long$time %in% c(2016, 2017, 2018)), ]
mice_set.subset.2016_2018$pidp <- mice.2018.pidp
mice_set.subset.2016_2018$hidp <- mice.2018.hidp
mice_set.subset.2016_2018$weight <- mice.2018.weights
mice_set.subset.2016_2018$time <- mice.2018.time
mice_set.subset.2016_2018 <- as.mids(mice_set.subset.2016_2018)


# Get 2011-2013 sample weights projected into 2016-2018 using cell-based reweighting.
# Reweighting done on age, sex, and ethnicity based on data from Office for National Statistics midyear demographic estimates.
extrapolated_weights.filelist <- list.files("data/extrapolated_weights/",
                       include.dirs = FALSE,
                       full.names = TRUE,
                       pattern = 'extrapolated_weights_data_[0-9]{4}.csv')[1:3]# get files for 2016-2018.



# Add extrapolated 2016-2018 weights to 2011-2013 MICE data.
extrapolated.weights.data <- do.call(rbind, lapply(extrapolated_weights.filelist, read.csv))
extrapolated.weights.data <- replace.missing(extrapolated.weights.data)
extrapolated.weights <- extrapolated.weights.data[, c("plus_5_weight")]

mice_set.subset.2011_2013.updated_weights <- mice.long[which(mice.long$time %in% c(2011, 2012, 2013)), ]
mice_set.subset.2011_2013.updated_weights$pidp <- mice.2013.pidp
mice_set.subset.2011_2013.updated_weights$hidp <- mice.2013.hidp
mice_set.subset.2011_2013.updated_weights$weight <- extrapolated.weights
mice_set.subset.2011_2013.updated_weights$time <- mice.2013.time
mice_set.subset.2011_2013.updated_weights <- as.mids2(mice_set.subset.2011_2013.updated_weights)

```


More weighted regression using MICE pooled data.
Producing LATEX table comparing OLS model coefficients using different sample weights.

```{r weighted_regressions}

# Fit linear regression on 2011-2013 MICE data using 2011-2013 and 2016-2018 extrapolated weights to compare any differences between models.
# weighted regression for 2016-2018 using 2011-2013 models and projected weights
sf12.lm.weighted.2013 <- pool(with(mice_set.subset.2011_2013.updated_weights, lm(as.formula(mice_formula_string), weights = weight)))

#  weighted regression for 2016-2018 using 2018 data.
sf12.lm.weighted.2018 <- pool(with(mice_set.subset.2016_2018, lm(as.formula(mice_formula_string), weights = weight)))

# Write two model coefficients to LATEX text file.
texreg_file <- paste0(save.path, 'table_7_projected_weights_coefficients.txt')
tex_label <- paste0("table: sf12_projected_weights_coefficients") 
tex_headers <- c(texreg::names2latex("SF_12 2018 With 2013 Extrapolated Weights"), texreg::names2latex("SF_12 2018 With Weights"))
tex_caption <- texreg::names2latex(get_tex_table_caption("SF_12", "projectied_ols"))    
texreg(list(sf12.lm.weighted.2013,sf12.lm.weighted.2018), # what model to save coefs for. 
       file=texreg_file,  # where to save.
       custom.model.names = tex_headers, # title of table.
       custom.coef.names = mice_coefs_names,
       stars = c(0.001, 0.01, 0.05), # p-value significance symbols. 
       digits=4, # p values significant figures.
       caption=tex_caption, # \caption command option. 
       label = tex_label, # \label command option. 
       dcolumn=T,# nice column alignment. 
       booktabs=T, # nice hlines. (recommended)
       tabular=T,# tabular env.
       single.row = T, # nicer one row formatting.
       longtable=T, # allows tables to wrap over pages
       use.packages=F, # don't add \usepackage commands to allow for direct importing of files as inputs
       fontsize='small') # tiny font
```

# Section 6: Heterogeneity using Generalised Linear Mixed models.

This section aims to estimate longitudinal heterogeneity within individuals over time using generalised linear mixed modelling.
A GLMM model using individual person random intercepts is fitted and assessed using model diagnostics from previous uncertainty and presentation sections.

This model is assessed using repeated diagnostic plots and cross-validation methods. 

```{r "glmm"}

# Preprocessing MICE data to use in GLMM.
reflect <- T
yeo_johnson <- F
include_weights <- T
depend <- "SF_12"
dependent_data <- complete(mice_set.subset)$SF_12

glmm.mice.long.subset <- complete(mice_set.subset, "long", include=T)

if (reflect) {
    max_value <- nanmax(mice.data[[depend]])
    glmm.mice.long.subset[, c(depend)] <- max_value - glmm.mice.long.subset[, c(depend)] + 0.001
  }
if (yeo_johnson)
{
  yj <- yeojohnson(glmm.mice.long.subset[["SF_12"]])
  glmm.mice.long.subset[["SF_12"]] <- predict(yj)
  
  min_value <- nanmin(glmm.mice.long.subset [[depend]])
  glmm.mice.long.subset[[depend]] <- glmm.mice.long.subset[[depend]] - min_value + 0.001
}

# Order MICE data by time. Add lagged dependent variable. Take 2011-2013 data.
glmm.mice.long.subset <- glmm.mice.long.subset %>%
           group_by(pidp) %>%
            mutate(last = lag(.data[["SF_12"]], order_by = time)) %>%
            rename_with(.fn = ~paste0('SF_12_', .), .cols = last)  # add the dependent as prefix to the calculated diff
glmm.mice.long.subset <- glmm.mice.long.subset[glmm.mice.long.subset$time %in% c(2011, 2012, 2013), ]
glmm.mice.long.subset$.imp <- as.numeric(glmm.mice.long.subset$.imp)
glmm.mice.long.subset <- as.data.frame(glmm.mice.long.subset)
glmm.mice.set <- as.mids2(glmm.mice.long.subset)

# define GLMM model formula
glmm_model_formula_string <- "I(log(SF_12+10)) ~ I(log(SF_12_last)+10) +
                  factor(sex) + 
                  relevel(factor(ethnicity), ref='WBI') + 
                  scale(age) + 
                  factor(education_state) + 
                  factor(labour_state) + 
                  relevel(factor(NSSEC), ref='1') +
                  relevel(factor(region), ref='London') +
                  scale(hh_income) + 
                  I(scale(hh_income**2)) +
                  relevel(factor(housing_quality), ref='Low') +
                  factor(neighbourhood_safety) +
                  factor(loneliness) + 
                  nutrition_quality + 
                  ncigs + time +
                  (1|pidp)"

# apply GLMM to pooled MICE data.
sf12.glmm.model <- with(glmm.mice.set, glmer(glmm_model_formula_string,  
               nAGQ=0, # fast but inaccurate optimiser. nAGQ=1 takes a few weeks.
               family=Gamma(link='log')#, weights=weight# gamma family with log link. no weights for MICE sample.
               ))
# pool model results.
sf12.glmm.pool <- pool(sf12.glmm.model)

# get Nakagawa R-squared for GLMMs.
print(r2_nakagawa(sf12.glmm.model$analyses[[1]]))


# Cast MICE mids object to nlmer predict object allowing for diagnostic plots.
mice.glmm.object <- sf12.glmm.model$analyses[[1]]
mice.glmm.object@beta <- sf12.glmm.pool$pooled$estimate
mice.glmm.object@beta <- - mice.glmm.object@beta

# save GLMM pooled coefficients to LATEX text file.
write_coefs <- T
if (write_coefs)
{
  texreg_file <- paste0(save.path, 'table_9_SF_12_GLMM_coefficients.txt')
  tex_label <- paste0("table: GLMM_SF_12_coefficients") 
  tex_headers <- c(texreg::names2latex("SF_12 GLMM"))
  tex_caption <- texreg::names2latex(get_tex_table_caption("SF_12", "glmm"))    
  texreg(sf12.glmm.pool, # what model to save coefs for. 
         file=texreg_file,  # where to save.
         custom.model.names = tex_headers, # title of table.
         custom.coef.names = c("SF_12 Previous", mice_coefs_names, "time"),
         stars = c(0.001, 0.01, 0.05), # p-value significance symbols. 
         digits=4, # p values significant figures.
         caption=tex_caption, # \caption command option. 
         label = tex_label, # \label command option. 
         dcolumn=T,# nice column alignment. 
         booktabs=T, # nice hlines. (recommended)
         tabular=T,# tabular env.
         single.row = T, # nicer one row formatting.
         longtable=T, # allows tables to wrap over pages
         use.packages=F, # don't add \usepackage commands to allow for direct importing of files as inputs
         fontsize='small') # tiny font
}

# Transform SF-12 MCS data back to correct distribution scale for diagnostic plots.
if (yeo_johnson == T) {
  glmm.fitted <- (max_value - predict(yj, predict(mice.glmm.object, type='response') + min_value
                                    , inverse=T))#
} else {
  glmm.fitted <-  max_value - (exp(predict(mice.glmm.object, type='response')) - 10)

}

```

```{r}
# Make GLMM diagnostic plots. qq plots, scale-location plots, and coefficient forest plots.
qq_plot(scale(residuals(mice.glmm.object, type='deviance')), paste0(save.path, "figure_9c_glmm_qq.pdf")) # also have pearson type residuals.
residual_density_plot(res=residuals(mice.glmm.object) , file_name=paste0(save.path, "figure_9b_glmm_residual_density.pdf"), guide="normal")

squareRootRes <- sqrt(residuals(mice.glmm.object, type='pearson')**2)

fitted_residuals <- as.data.frame(cbind(glmm.fitted, squareRootRes))
colnames(fitted_residuals) <- c("fitted", "sqrt_residuals")
fitted_residual_plot(fitted_residuals, paste0(save.path, "figure_9d_glmm_scale_location_plot.pdf"))

gamma_forest_plot(mice.glmm.object, paste0(save.path, "figure_9a_glmm_forest.pdf"))
#log_forest_plot(plot.mice.glmm.object, paste0(save.path, "figure_9a_glmm_forest.pdf"))
mice.glmm.object@beta <- - mice.glmm.object@beta # flip coefficients back for handovers.

```

Performing nowcasting using the updated GLMM model.

```{r glmm_handovers}
# Process MICE data for nowcasting by removing incomplete rows.
crossval.glmm.data <- replace.missing(complete(mice_set.full, 1)[, append(variables, c("time", 'pidp', 'hidp', 'weight'))])
crossval.glmm.data <- crossval.glmm.data[which(crossval.glmm.data$time>=2013),]
crossval.glmm.data <- drop_na(crossval.glmm.data)

# define function clipping SF_12 MCS data to SF-12 MCS being smaller than 0.
cppFunction('NumericVector rcpp_clip( NumericVector x, double a, double b){
    return clamp( a, x, b ) ;
}')

#get 2013 start data for nowcasting. 
start.data <- complete(glmm.mice.set, 1)
start.data <- start.data[which(start.data$time==2013),]
start.data$SF_12 <- max_value - start.data$SF_12

# Process SF-12 using YJ transform so predict function works properly.
if (yeo_johnson == T) {
start.data$SF_12 <- max_value - predict(yj, start.data$SF_12 +min_value, inverse=T)
start.data <- drop_na(start.data)
} 
handover.data <- start.data
rolling.data <- start.data

# Perform nowcasting from 2013-2021 using GLMM model.
for (i in 1:8){
  if (yeo_johnson == T) {
      #rolling.data$SF_12 <- predict(mice.glmm.object, rolling.data, type='response',allow.new.levels=T)
      #rolling.data$SF_12 <- max_value - rolling_data$SF_12
      rolling.data$SF_12 <- exp(predict(mice.glmm.object, rolling.data, type='response', allow.new.levels=T))-10
      rolling.data$SF_12_last <- rolling.data$SF_12                           
      #rolling.data$SF_12 <- max_value - predict(yj,  rolling.data$SF_12 +min_value+ rnorm(nrow(rolling.data), 0, 0.3), inverse=T)
      rolling.data$SF_12 <- max_value - predict(yj,  rolling.data$SF_12 +min_value+ rnorm(nrow(rolling.data), 0, 0.3), inverse=T)
  }
  else {
    #rolling.data$SF_12 <- max_value - predict(mice.glmm.object, rolling.data, type='response',allow.new.levels=T) + rnorm(nrow(rolling.data), 0, 1)
    #rolling.data$SF_12 <- max_value - rolling.data$SF_12
    rolling.data$SF_12 <- (exp(predict(mice.glmm.object, rolling.data, type='response',allow.new.levels=T))-10)# + rnorm(nrow(rolling.data), 0, 5))
    
    #rd.mean <- median(rolling.data$SF_12, na.rm=T)
    #rolling.data$SF_12 <- rolling.data$SF_12 * 1.05
    #rolling.data$SF_12 <- rolling.data$SF_12 - ((1.05-1)*rd.mean)
    rolling.data$SF_12_last <- rolling.data$SF_12
    
  }
  rolling.data$SF_12 <- max_value - rolling.data$SF_12
  rolling.data$SF_12 <- rcpp_clip(rolling.data$SF_12, 0, 100)
  rolling.data[, 'time'] <- rolling.data[, 'time'] +1
  handover.data <- rbind(handover.data, rolling.data)
  #rolling.data$SF_12 <- max_value - predict(yj,  rolling.data$SF_12 +min_value+ rnorm(nrow(rolling.data), 0, 0.3), inverse=T))
}

# Plot nowcasting results.
handover_boxplots(mice.data[which(mice.data$time>= 2014),], handover.data, "SF_12", save.path, "figure_10b_glmm_SF12_boxplot")
density_ridges(mice.data[which(mice.data$time>= 2014),], "SF_12", save=TRUE, save.path=save.path, filename.tag = "glmm_raw_ridges")
density_ridges(handover.data, "SF_12", save=TRUE, save.path=save.path, filename.tag = "figure_10a_glmm_handover_ridges")

```

Five-fold cross-validation applied to GLMM model estimating final RMSE score.

```{r glmm_crossval}

# Special function needed to apply GLMM using five fold cross-validation.
fit.glmm.to.each.fold <- function(mice.fold.data) {
  sf12.glmm.model <- with(mice.fold.data, glmer(glmm_model_formula_string,  
               nAGQ=0, # fast but inaccurate optimiser. nAGQ=1 takes forever..
               family=Gamma(link='log')#, weights=weight# gamma family with log link.
               ))
  
  sf12.glmm.pool <- pool(sf12.glmm.model)
  
  # mice objects dont go in forest plot annoyingly. move coefficients over to a
  # dummy lm that sjPlot::plot_models can read.
  mice.glmm.object <- sf12.glmm.model$analyses[[1]]
  mice.glmm.object@beta <- sf12.glmm.pool$pooled$estimate
  #attr(mice.glmm.object, "beta") <- sf12.glmm.pool$estimate
  #mice.glmm.object@ <- sf12.glmm.pool$std.error
  #mice.glmm.object$coefficients[,3] <- sf12.glmm.pool$statistic
  #mice.glmm.object$coefficients[,4] <- sf12.glmm.pool$p.value
  print(r2_nakagawa(sf12.glmm.model$analyses[[1]]))
return(mice.glmm.object)
}

#split mice sets into 5 based on pidps
pidps <- complete(mice_set.subset, 1)$pidp
pidp_chunks <- groupKFold(pidps, k=5)
pidp_chunks1 <- unique(pidps[pidp_chunks$Fold1])
pidp_chunks2 <- unique(pidps[pidp_chunks$Fold2])
pidp_chunks3 <- unique(pidps[pidp_chunks$Fold3])
pidp_chunks4 <- unique(pidps[pidp_chunks$Fold4])
pidp_chunks5 <- unique(pidps[pidp_chunks$Fold5])

# Taking desired subset of pidps for each fold.
glmm.mice.long.subset.fold1 <- filter(glmm.mice.long.subset, !pidp %in% pidp_chunks1)
glmm.mice.long.subset.fold2 <- filter(glmm.mice.long.subset, !pidp %in% pidp_chunks2)
glmm.mice.long.subset.fold3 <- filter(glmm.mice.long.subset, !pidp %in% pidp_chunks3)
glmm.mice.long.subset.fold4 <- filter(glmm.mice.long.subset, !pidp %in% pidp_chunks4)
glmm.mice.long.subset.fold5 <- filter(glmm.mice.long.subset, !pidp %in% pidp_chunks5)

# convert back to mice mids objects to apply pooled GLMM modelling.
glmm.mice.set.fold1 <- as.mids2(glmm.mice.long.subset.fold1)
glmm.mice.set.fold2 <- as.mids2(glmm.mice.long.subset.fold2)
glmm.mice.set.fold3 <- as.mids2(glmm.mice.long.subset.fold3)
glmm.mice.set.fold4 <- as.mids2(glmm.mice.long.subset.fold4)
glmm.mice.set.fold5 <- as.mids2(glmm.mice.long.subset.fold5)

# Fit glmms to each fold of MICE data.
sf12.glmm.fold1 <- fit.glmm.to.each.fold(glmm.mice.set.fold1)
sf12.glmm.fold2 <- fit.glmm.to.each.fold(glmm.mice.set.fold2)
sf12.glmm.fold3 <- fit.glmm.to.each.fold(glmm.mice.set.fold3)
sf12.glmm.fold4 <- fit.glmm.to.each.fold(glmm.mice.set.fold4)
sf12.glmm.fold5 <- fit.glmm.to.each.fold(glmm.mice.set.fold5)

# Get cross-validation test data for each fold.
glmm.mice.long.subset.test1 <- drop_na(filter(glmm.mice.long.subset, pidp %in% pidp_chunks1))
glmm.mice.long.subset.test2 <- drop_na(filter(glmm.mice.long.subset, pidp %in% pidp_chunks2))
glmm.mice.long.subset.test3 <- drop_na(filter(glmm.mice.long.subset, pidp %in% pidp_chunks3))
glmm.mice.long.subset.test4 <- drop_na(filter(glmm.mice.long.subset, pidp %in% pidp_chunks4))
glmm.mice.long.subset.test5 <- drop_na(filter(glmm.mice.long.subset, pidp %in% pidp_chunks5))


# calculate RMSE for each fold and take mean and variance for RMSE.
# RMSE1 <- rmse2(max_value - exp(predict(sf12.glmm.fold1, glmm.mice.long.subset.test1, type='response', allow.new.levels=T)) + 10,
#                max_value - glmm.mice.long.subset.test1$SF_12)
# RMSE2 <- rmse2(max_value - exp(predict(sf12.glmm.fold2, glmm.mice.long.subset.test2, type='response', allow.new.levels=T)) + 10,
#                max_value - glmm.mice.long.subset.test2$SF_12)
# RMSE3 <- rmse2(max_value - exp(predict(sf12.glmm.fold3, glmm.mice.long.subset.test3, type='response', allow.new.levels=T)) + 10,
#                max_value - glmm.mice.long.subset.test3$SF_12)
# RMSE4 <- rmse2(max_value - exp(predict(sf12.glmm.fold4, glmm.mice.long.subset.test4, type='response', allow.new.levels=T)) + 10,
#                max_value - glmm.mice.long.subset.test4$SF_12)
# RMSE5 <- rmse2(max_value - exp(predict(sf12.glmm.fold5, glmm.mice.long.subset.test5, type='response', allow.new.levels=T)) + 10,
#                max_value - glmm.mice.long.subset.test5$SF_12)
# rmse_glmm_values <- c(RMSE1, RMSE2, RMSE3, RMSE4, RMSE5)
# print(mean(rmse_glmm_values))
# print(var(rmse_glmm_values))


# RMSE1 <- caret::RMSE(predict(sf12.glmm.fold1, glmm.mice.long.subset.test1, type='response', allow.new.levels=T), log(glmm.mice.long.subset.test1$SF_12 + 10))
# RMSE2 <- caret::RMSE(predict(sf12.glmm.fold2, glmm.mice.long.subset.test2, type='response', allow.new.levels=T), log(glmm.mice.long.subset.test2$SF_12 + 10))
# RMSE3 <- caret::RMSE(predict(sf12.glmm.fold3, glmm.mice.long.subset.test3, type='response', allow.new.levels=T), log(glmm.mice.long.subset.test3$SF_12 + 10))
# RMSE4 <- caret::RMSE(predict(sf12.glmm.fold4, glmm.mice.long.subset.test4, type='response', allow.new.levels=T), log(glmm.mice.long.subset.test4$SF_12 + 10))
# RMSE5 <- caret::RMSE(predict(sf12.glmm.fold5, glmm.mice.long.subset.test5, type='response', allow.new.levels=T), log(glmm.mice.long.subset.test5$SF_12 + 10))


RMSE1 <- rmse2(max_value - exp(predict(sf12.glmm.fold1, glmm.mice.long.subset.test1, type='response', allow.new.levels=T)) + 10,
                max_value - glmm.mice.long.subset.test1$SF_12)
RMSE2 <- rmse2(max_value - exp(predict(sf12.glmm.fold2, glmm.mice.long.subset.test2, type='response', allow.new.levels=T)) + 10,
                max_value - glmm.mice.long.subset.test2$SF_12)
RMSE3 <- rmse2(max_value - exp(predict(sf12.glmm.fold3, glmm.mice.long.subset.test3, type='response', allow.new.levels=T)) + 10,
                max_value - glmm.mice.long.subset.test3$SF_12)
RMSE4 <- rmse2(max_value - exp(predict(sf12.glmm.fold4, glmm.mice.long.subset.test4, type='response', allow.new.levels=T)) + 10,
                max_value - glmm.mice.long.subset.test4$SF_12)
RMSE5 <- rmse2(max_value - exp(predict(sf12.glmm.fold5, glmm.mice.long.subset.test5, type='response', allow.new.levels=T)) + 10,
                max_value - glmm.mice.long.subset.test5$SF_12)

rmse_glmm_values <- c(RMSE1, RMSE2, RMSE3, RMSE4, RMSE5)
print(mean(rmse_glmm_values))
print(sd(rmse_glmm_values))

```

```{r}

# 
# glmm_crossval_test <- train(as.formula(glmm_model_formula_string), data = complete(glmm.mice.set, 1),
#                method = glmer,
#                nAGQ=0, # fast but inaccurate optimiser. nAGQ=1 takes forever..
#                family=Gamma(link='log'), #, weights=weight# gamma family with log link.
#                na.action  = na.pass,
#                trControl = trControl)
```

```{r}



# 
# mice.RMSE.statistics <- mice.cross.val.sf12.model$pred %>% 
#   group_by(Resample) %>%
#   mutate(obs =  exp(obs) - 10) %>%
#   mutate(pred =  exp(pred) - 10) %>%
#   summarise(output_RMSE=caret::RMSE(pred, obs)) %>%
#   summarise(mean = mean(output_RMSE), std = sd(output_RMSE))
# 
# print("MICE RMSE Statistics: ")
# print(mice.RMSE.statistics)


```