---
title: "WS7 Table 1"
output: html_notebook
---

Creating requested table 1 for "flagship" paper.


```{r}
library(dplyr)
library(here)
library(tibble)
library(xtable)
```


#Schema

Tenure type

All?
owner outright
mortgage
private rental
housing association
social housing

Household type
All
with children
without children?
with pensioners

In poverty
All
with children
without children
with pensioners


```{r}

# load in data


#data <- read.csv(here::here("data", "composite_US", "2020_US_cohort.csv"))
data <- read.csv(here::here("data", "scaled_manchester_US", "2020_US_cohort.csv"))
data <- data %>% filter(housing_tenure > 0)

#recast housing tenure for a tidy table.
data$housing_tenure_simple <- data$housing_tenure
# https://www.understandingsociety.ac.uk/documentation/mainstage/variables/tenure_dv/
data[which(data$housing_tenure_simple == 1), "housing_tenure_simple"] <- "1 - Owned Outright"
data[which(data$housing_tenure_simple == 2), "housing_tenure_simple"] <- "2 - Mortgaged"
data[which(data$housing_tenure_simple == 3), "housing_tenure_simple"] <- "5 - Social housing"
data[which(data$housing_tenure_simple == 4), "housing_tenure_simple"] <- "4 - Housing association"
data[which(data$housing_tenure_simple == 5), "housing_tenure_simple"] <- "3 - Private Rental"
data[which(data$housing_tenure_simple == 6), "housing_tenure_simple"] <- "3 - Private Rental"
data[which(data$housing_tenure_simple == 7), "housing_tenure_simple"] <- "3 - Private Rental" # binning other into private rental for now. 
data[which(data$housing_tenure_simple == 8), "housing_tenure_simple"] <- "3 - Private Rental" # binning other into private rental for now. 

data[which(data$heating == 0), "heating"] <- "0 - Not Comfortable"
data[which(data$heating == 1), "heating"] <- "1 - Comfortable"


tenure_data_table_subgroup <- function(df, pop_size, include_tenure_column, count_type, group_name){
tenure_table1 <- df %>%
          count(housing_tenure_simple) %>%
          mutate(prct = 100*n/pop_size) %>%
          mutate("n_total" = paste0(as.character(n), " " , "(", as.character(round(100*n/pop_size, 2)), ")")) %>%
          mutate("Group"= group_name) %>%
          select("housing_tenure_simple","Group", "n_total")
          #rbind(c("Total", nrow(data), 100)) %>%

colnames(tenure_table1) <- c("Housing Tenure", "Group", count_type)

#print(tenure_table1)


# getting the required second column for each housing tenure type. 
tenure_table2 <- df %>%
                  group_by(housing_tenure_simple) %>%
                      count(heating) %>%
                        filter(heating == "0 - Not Comfortable") %>%
  # ungrouping here to give percentage of the entire population rather than percentage of each housing tenure. can use either by hashing this column.
                    ungroup() %>% 
                      mutate("n_total" = paste0(as.character(n), " " , "(", as.character(round(100*n/sum(n), 2)), ")")) %>%
          mutate("Group"= "n (% PTC)") %>% #"Number of Poor Thermal Comfort Adults in Subpopulation (% of Subpopulation)"
          select("housing_tenure_simple","Group", "n_total")
colnames(tenure_table2) <- c("Housing Tenure", "Group", count_type)

#print(tenure_table2)


tenure_table <- rbind(tenure_table1, tenure_table2)
tenure_table <- tenure_table %>% arrange(`Housing Tenure`)

if(!include_tenure_column){
  tenure_table <- tenure_table %>% select(count_type)
}
return(tenure_table)
}

# "Number of Adults (% of Entire Adult Population)"
tenure_table1 <- tenure_data_table_subgroup(data, nrow(data), T, "All", "n (% total)")
housing_tenure_list <- tenure_table1$`Housing Tenure`
tenure_table1 <- tenure_table1 %>% select("Group", "All")
tenure_table2 <- tenure_data_table_subgroup(data %>% filter(nkids>0), nrow(data), F, "With Children", "n (% total)") # children.
tenure_table3 <- tenure_data_table_subgroup(data %>% filter(nkids<=0), nrow(data), F, "Without Children", "n (% total)") # no children
tenure_table4 <- tenure_data_table_subgroup(data%>% filter(age>65), nrow(data), F, "Pensioners", "n (% total)") # pensioners. need a better measures of a 'pensioner'. see npensioners_dv variable.

# NOTE THE TOTAL POPULATION CHANGES HERE. LOOKING AT SMALLER POPULATION nrow(poverty_data) RATHER THAN FULL POPULATION nrow(data)
#"Number of Adults (% of Entire Adult Population in Relative Poverty)" 
poverty_data<- data %>% filter(hh_income < 0.6*median(hh_income)) # standard relative poverty definition.
tenure_table5 <- tenure_data_table_subgroup(poverty_data, nrow(poverty_data), T, "All Poverty", "n (% all poverty)")
tenure_table5 <- tenure_table5 %>% select("Group", "All Poverty")
tenure_table6 <- tenure_data_table_subgroup((poverty_data %>% filter(nkids>0)), nrow(poverty_data), F, "Poverty With Children",  "n (% all poverty)") # children.
tenure_table7 <- tenure_data_table_subgroup(poverty_data %>% filter(nkids<=0), nrow(poverty_data), F, "Poverty Without Children", "n (% all poverty)") # no children
tenure_table8 <- tenure_data_table_subgroup(poverty_data%>% filter(age>65), nrow(poverty_data), F, "Poverty With Pensioners", "n (% all poverty)") # pensioners. need a better measures of a 'pensioner'. see npensioners_dv variable.

final_tenure_table <- rbind(tenure_table1,tenure_table2,tenure_table3,tenure_table4,tenure_table5,tenure_table6,tenure_table7,tenure_table8)


output_table <- xtable(t(final_tenure_table), caption="Testing table 1 for SIPHER flagship paper.", align = "|l|l|l|l|l|l|l|l|l|l|l|")


addtorow <- list()
addtorow$pos <- list(0)
addtorow$command <- paste0('\\textbackslash Housing Tenure ', paste0(' & \\multicolumn{2}{|l}{', sort(unique(data$housing_tenure_simple)), '}', collapse=''), '\\\\')


#print(output_table, file='test.tex', include.colnames=F)
print(output_table, add.to.row=addtorow, file='test.tex', include.colnames=F, hline.after=c(-1,0,1,5,6,10))


final_tenure_table$housing_tenure <- housing_tenure_list
write.csv(t(final_tenure_table), file="test.csv") # names arg drops column names


```

```{r}


#Household type
#All
#with children
#without children?
#with pensioners

#print("Total Households: ")
#print(length(unique(data$hidp)))

n_total_households <- length(unique(data$hidp))

children_data <- data %>% 
                  filter(nkids>0)
n_children_households <-length(unique(children_data$hidp))

#print("Total Households with Children 16yo and Under: ")
#print(length(unique(children_data$hidp)))

childless_data <- data %>% 
                  filter(nkids<=0)
n_childless_households <-  length(unique(childless_data$hidp))

#print("Total Households without Children 16yo and Under: ")
#print(length(unique(children_data$hidp)))

pensioner_data <- data %>%  # need a better condition that this.. see npensioner_dv variable
                  filter(age>65)
n_pensioner_households <- length(unique(pensioner_data$hidp))

#print("Total Households With Any Adults Over 65yo (Loose definition of pensioner): ")
#print(length(unique(pensioner_data$hidp)))

household_type_table <- rbind(c("Total Households", n_total_households, 100), 
      c("Total Households with Children 16yo and Under: ", n_children_households, n_children_households * 100 /n_total_households), 
      c("Total Households without Children 16yo and Under: ", n_childless_households, n_childless_households* 100 /n_total_households),
      c("Total Households With Any Adults Over 65yo (Loose definition of pensioner): ", n_pensioner_households,  n_pensioner_households * 100 /n_total_households))
colnames(household_type_table) <- c("Category", "Number of Unique Households (hidps)", "Percentage of Total Households")
print(as.tibble(household_type_table))
```

```{r}

#In poverty
#All
#with children
#without children
#with pensioners


#using simple relative poverty definition for now. 
poverty_data <- data %>% filter(hh_income < 0.6*median(hh_income))
n_total_poverty_households <- length(unique(data$hidp))

#print("Total Relative Poverty Households: ")
#print(length(unique(data$hidp)))

poverty_children_data <- poverty_data %>% 
                  filter(nkids>0)
n_children_poverty_households <-length(unique(poverty_children_data$hidp))

#print("Total Relative Poverty Households with Children 16yo and Under: ")
#print(length(unique(children_data$hidp)))

poverty_childless_data <- poverty_data %>% 
                  filter(nkids<=0)
n_childless_poverty_households <-  length(unique(poverty_childless_data$hidp))

#print("Total Relative Poverty Households without Children 16yo and Under: ")
#print(length(unique(childless_data$hidp)))

poverty_pensioner_data <- poverty_data %>%  # need a better condition that this.. see npensioner_dv variable
                  filter(age>65)
n_pensioner_poverty_households <- length(unique(poverty_pensioner_data$hidp))

#print("Total  Relative Poverty Households With Any Adults Over 65yo (Loose definition of pensioner): ")
#print(length(unique(pensioner_data$hidp)))


poverty_household_type_table <- rbind(c("Total Households", n_total_poverty_households, 20, 100, 20), 
      c("Total Households with Children 16yo and Under: ", n_children_poverty_households, 20, n_children_poverty_households * 100 /n_total_poverty_households, 20), 
      c("Total Households without Children 16yo and Under: ", n_childless_poverty_households, 20, n_childless_poverty_households* 100 /n_total_poverty_households, 20),
      c("Total Households With Any Adults Over 65yo (Loose definition of pensioner): ", n_pensioner_poverty_households,  20, n_pensioner_poverty_households * 100 /n_total_poverty_households, 20))
colnames(poverty_household_type_table) <- c("Category", "Number of Unique Households (hidps)", "Number of households in Poor Thermal Comfort", "Percentage of Total Households")
print(as.tibble(poverty_household_type_table))
```



# Unit house retrofit costs. 
# find paper talking about range of energy savings for different data using NEED datasets. bridgen/hodgkin? pretty sure its in the latter at least. see other nature refs for any details.

https://www.instituteforgovernment.org.uk/sites/default/files/publications/tackling-energy-efficiency-problem.pdf
References NEED data.

https://assets.publishing.service.gov.uk/media/5a82338f40f0b62305b93052/BEIS_Update_of_Domestic_Cost_Assumptions_031017.pdf
2017 BEIS retrofit costing. 




