---
title: "WS7 Table 1"
output: html_notebook
---

Creating requested table 1 for "flagship" paper.


```{r}
library(dplyr)
library(here)
library(tibble)
library(xtable)
```


#Schema

Tenure type

All?
owner outright
mortgage
private rental
housing association
social housing

Household type
All
with children
without children?
with pensioners

In poverty
All
with children
without children
with pensioners


```{r}

# load in data
# either composite or synthpop data
data <- read.csv(here::here("data", "composite_US", "2020_US_cohort.csv"))
#data <- read.csv(here::here("data", "scaled_manchester_US", "2020_US_cohort.csv"))
data <- data %>% filter(housing_tenure > 0)

#recast housing tenure for a tidy table. neat strings rather than int codes. also binning some things per ws7 definition.
data$housing_tenure_simple <- data$housing_tenure
# https://www.understandingsociety.ac.uk/documentation/mainstage/variables/tenure_dv/
data[which(data$housing_tenure_simple == 1), "housing_tenure_simple"] <- "1 - Owned Outright"
data[which(data$housing_tenure_simple == 2), "housing_tenure_simple"] <- "2 - Mortgaged"
data[which(data$housing_tenure_simple == 3), "housing_tenure_simple"] <- "5 - Social housing"
data[which(data$housing_tenure_simple == 4), "housing_tenure_simple"] <- "4 - Housing association"
data[which(data$housing_tenure_simple == 5), "housing_tenure_simple"] <- "3 - Private Rental"
data[which(data$housing_tenure_simple == 6), "housing_tenure_simple"] <- "3 - Private Rental"
data[which(data$housing_tenure_simple == 7), "housing_tenure_simple"] <- "3 - Private Rental" # binning other into private rental for now. 
data[which(data$housing_tenure_simple == 8), "housing_tenure_simple"] <- "3 - Private Rental" # binning other into private rental for now. 

# Do same for heating as well.
data[which(data$heating == 0), "heating"] <- "0 - Not Comfortable"
data[which(data$heating == 1), "heating"] <- "1 - Comfortable"


# functino to process data into rows of final data frame
tenure_data_table_subgroup <- function(df, pop_size, include_tenure_column, count_type, group_name){
  "
  df - data frame
  pop_size - population size. used to calculate percentages. need to be specific about which population you want here. 
    typically either the total population or the population in relative poverty.
  include_tenure_column - 
  count_type - 
  group_name - 
  "
  

# calculate first set of four rows. percentages of the entire population in
# all
# with children
# without children
# pensioners
row_table1 <- df %>%
          count(housing_tenure_simple) %>%
          mutate(prct = 100*n/pop_size) %>%
          mutate("n_total" = paste0(as.character(n), " " , "(", as.character(round(100*n/pop_size, 2)), ")")) %>%
          mutate("Group"= group_name) %>%
          select("housing_tenure_simple","Group", "n", "n_total")
          #rbind(c("Total", nrow(data), 100)) %>%

colnames(row_table1) <- c("Housing Tenure", "Group", "n", count_type)

#print(tenure_table1)


# getting the required second column for each housing tenure type. 
row_table2 <- df %>%
                  group_by(housing_tenure_simple) %>%
                      count(heating) %>%
                        filter(heating == "0 - Not Comfortable") %>%
  # ungrouping here to give percentage of the entire population rather than percentage of each housing tenure. can use either by hashing this column.
                    ungroup() %>% 
                      #mutate("n_total" = paste0(as.character(n), " " , "(", as.character(round(100*n/sum(n), 2)), ")")) %>%
                      mutate("n_total" = paste0(as.character(n), " " , "(", as.character(round(100*n/row_table1$n, 2)), ")")) %>%
          mutate("Group"= "n (% PTC)") %>% #"Number of Poor Thermal Comfort Adults in Subpopulation (% of Subpopulation)"
          select("housing_tenure_simple","Group", "n", "n_total")
colnames(row_table2) <- c("Housing Tenure", "Group", "n", count_type)

#print(tenure_table2)

row_table <- rbind(row_table1, row_table2)
row_table <- row_table %>% arrange(`Housing Tenure`)

  
if(!include_tenure_column){
  row_table <- row_table %>% select(count_type, "n")
}
return(row_table)
}


# functino to process data into rows of final data frame
tenure_data_table_weighted_subgroup <- function(df, pop_size, include_tenure_column, count_type, group_name){
  "
  df - data frame
  pop_size - population size. used to calculate percentages. need to be specific about which population you want here. 
    typically either the total population or the population in relative poverty.
  include_tenure_column - 
  count_type - 
  group_name - 
  "
  

# calculate first set of four rows. percentages of the entire population in
# all
# with children
# without children
# pensioners
row_table1 <- df %>%
          count(housing_tenure_simple) %>%
          mutate(prct = 100*n/pop_size) %>%
          mutate("n_total" = paste0(as.character(n), " " , "(", as.character(round(100*n/pop_size, 2)), ")")) %>%
          mutate("Group"= group_name) %>%
          select("housing_tenure_simple","Group", "n", "n_total")
          #rbind(c("Total", nrow(data), 100)) %>%

colnames(row_table1) <- c("Housing Tenure", "Group", "n", count_type)

#print(tenure_table1)


# getting the required second column for each housing tenure type. 
row_table2 <- df %>%
                  group_by(housing_tenure_simple) %>%
                      count(heating) %>%
                        filter(heating == "0 - Not Comfortable") %>%
  # ungrouping here to give percentage of the entire population rather than percentage of each housing tenure. can use either by hashing this column.
                    ungroup() %>% 
                      #mutate("n_total" = paste0(as.character(n), " " , "(", as.character(round(100*n/sum(n), 2)), ")")) %>%
                      mutate("n_total" = paste0(as.character(n), " " , "(", as.character(round(100*n/row_table1$n, 2)), ")")) %>%
          mutate("Group"= "n (% PTC)") %>% #"Number of Poor Thermal Comfort Adults in Subpopulation (% of Subpopulation)"
          select("housing_tenure_simple","Group", "n", "n_total")
colnames(row_table2) <- c("Housing Tenure", "Group", "n", count_type)

#print(tenure_table2)

row_table <- rbind(row_table1, row_table2)
row_table <- row_table %>% arrange(`Housing Tenure`)

  
if(!include_tenure_column){
  row_table <- row_table %>% select(count_type, "n")
}
return(row_table)
}


# "Number of Adults (% of Entire Adult Population)"
tenure_table1 <- tenure_data_table_subgroup(data, nrow(data), T, "All", "n (% total)")

sub_population_sizes1 <- tenure_table1$n
sub_population_sizes1 <- sub_population_sizes1[seq(1, length(sub_population_sizes1), 2)]

housing_tenure_list <- tenure_table1$`Housing Tenure`
## tenure_table1 <- tenure_table1 %>% select("Group", "All")
tenure_table2 <- tenure_data_table_subgroup(data %>% filter(nkids>0), sub_population_sizes1, F, "With Children", "n (% total)") # children.
tenure_table3 <- tenure_data_table_subgroup(data %>% filter(nkids<=0), sub_population_sizes1, F, "Without Children", "n (% total)") # no children
tenure_table4 <- tenure_data_table_subgroup(data%>% filter(age>65), sub_population_sizes1, F, "Pensioners", "n (% total)") # pensioners. need a better measures of a 'pensioner'. see npensioners_dv variable.

sub_population_sizes2 <- tenure_table2$n
sub_population_sizes2 <- sub_population_sizes2[seq(1, length(sub_population_sizes2), 2)]

sub_population_sizes3 <- tenure_table3$n
sub_population_sizes3 <- sub_population_sizes3[seq(1, length(sub_population_sizes3), 2)]

sub_population_sizes4 <- tenure_table4$n
sub_population_sizes4 <- sub_population_sizes4[seq(1, length(sub_population_sizes4), 2)]

tenure_table1$n <- NULL
tenure_table2$n <- NULL
tenure_table3$n <- NULL
tenure_table4$n <- NULL

# NOTE THE TOTAL POPULATION CHANGES HERE. LOOKING AT SMALLER POPULATION nrow(poverty_data) RATHER THAN FULL POPULATION nrow(data)
#"Number of Adults (% of Entire Adult Population in Relative Poverty)" 
poverty_data<- data %>% filter(hh_income < 0.6*median(hh_income)) # standard relative poverty definition.
tenure_table5 <- tenure_data_table_subgroup(poverty_data, sub_population_sizes1, T, "All Poverty", "n (% all poverty)")


sub_population_sizes5 <- tenure_table5$n
sub_population_sizes5 <- sub_population_sizes5[seq(1, length(sub_population_sizes5), 2)]


tenure_table5 <- tenure_table5 %>% select("Group", "All Poverty")
tenure_table6 <- tenure_data_table_subgroup((poverty_data %>% filter(nkids>0)), sub_population_sizes5, F, "Poverty With Children",  "n (% all poverty)") # children.
tenure_table7 <- tenure_data_table_subgroup(poverty_data %>% filter(nkids<=0), sub_population_sizes5, F, "Poverty Without Children", "n (% all poverty)") # no children
tenure_table8 <- tenure_data_table_subgroup(poverty_data%>% filter(age>65), sub_population_sizes5, F, "Poverty With Pensioners", "n (% all poverty)") # pensioners. need a better measures of a 'pensioner'. see npensioners_dv variable.


tenure_table5$n <- NULL
tenure_table6$n <- NULL
tenure_table7$n <- NULL
tenure_table8$n <- NULL

final_tenure_table <- cbind(tenure_table1,tenure_table2,tenure_table3,tenure_table4,tenure_table5,tenure_table6,tenure_table7,tenure_table8)
#colnames(final_tenure_table)[1] <- "Housing Tenure"

output_table <- xtable(t(final_tenure_table), caption="Testing table 1 for SIPHER flagship paper.", align = "|l|l|l|l|l|l|l|l|l|l|l|")


addtorow <- list()
addtorow$pos <- list(0)
addtorow$command <- paste0('\\textbackslash Housing Tenure ', paste0(' & \\multicolumn{2}{|l}{', sort(unique(data$housing_tenure_simple)), '}', collapse=''), '\\\\')


#print(output_table, file='test.tex', include.colnames=F)
print(output_table, add.to.row=addtorow, file='test.tex', include.colnames=F, hline.after=c(-1,0,1,5,6,10))


#final_tenure_table$housing_tenure <- housing_tenure_list
write.csv(t(final_tenure_table), file="test.csv") # names arg drops column names


```

```{r}


#Household type
#All
#with children
#without children?
#with pensioners

#print("Total Households: ")
#print(length(unique(data$hidp)))

n_total_households <- length(unique(data$hidp))

children_data <- data %>% 
                  filter(nkids>0)
n_children_households <-length(unique(children_data$hidp))

#print("Total Households with Children 16yo and Under: ")
#print(length(unique(children_data$hidp)))

childless_data <- data %>% 
                  filter(nkids<=0)
n_childless_households <-  length(unique(childless_data$hidp))

#print("Total Households without Children 16yo and Under: ")
#print(length(unique(children_data$hidp)))

pensioner_data <- data %>%  # need a better condition that this.. see npensioner_dv variable
                  filter(age>65)
n_pensioner_households <- length(unique(pensioner_data$hidp))

#print("Total Households With Any Adults Over 65yo (Loose definition of pensioner): ")
#print(length(unique(pensioner_data$hidp)))

household_type_table <- rbind(c("Total Households", n_total_households, 100), 
      c("Total Households with Children 16yo and Under: ", n_children_households, n_children_households * 100 /n_total_households), 
      c("Total Households without Children 16yo and Under: ", n_childless_households, n_childless_households* 100 /n_total_households),
      c("Total Households With Any Adults Over 65yo (Loose definition of pensioner): ", n_pensioner_households,  n_pensioner_households * 100 /n_total_households))
colnames(household_type_table) <- c("Category", "Number of Unique Households (hidps)", "Percentage of Total Households")
print(as.tibble(household_type_table))
```

```{r}

#In poverty
#All
#with children
#without children
#with pensioners


#using simple relative poverty definition for now. 
poverty_data <- data %>% filter(hh_income < 0.6*median(hh_income))
n_total_poverty_households <- length(unique(data$hidp))

#print("Total Relative Poverty Households: ")
#print(length(unique(data$hidp)))

poverty_children_data <- poverty_data %>% 
                  filter(nkids>0)
n_children_poverty_households <-length(unique(poverty_children_data$hidp))

#print("Total Relative Poverty Households with Children 16yo and Under: ")
#print(length(unique(children_data$hidp)))

poverty_childless_data <- poverty_data %>% 
                  filter(nkids<=0)
n_childless_poverty_households <-  length(unique(poverty_childless_data$hidp))

#print("Total Relative Poverty Households without Children 16yo and Under: ")
#print(length(unique(childless_data$hidp)))

poverty_pensioner_data <- poverty_data %>%  # need a better condition that this.. see npensioner_dv variable
                  filter(age>65)
n_pensioner_poverty_households <- length(unique(poverty_pensioner_data$hidp))

#print("Total  Relative Poverty Households With Any Adults Over 65yo (Loose definition of pensioner): ")
#print(length(unique(pensioner_data$hidp)))


poverty_household_type_table <- rbind(c("Total Households", n_total_poverty_households, 20, 100, 20), 
      c("Total Households with Children 16yo and Under: ", n_children_poverty_households, 20, n_children_poverty_households * 100 /n_total_poverty_households, 20), 
      c("Total Households without Children 16yo and Under: ", n_childless_poverty_households, 20, n_childless_poverty_households* 100 /n_total_poverty_households, 20),
      c("Total Households With Any Adults Over 65yo (Loose definition of pensioner): ", n_pensioner_poverty_households,  20, n_pensioner_poverty_households * 100 /n_total_poverty_households, 20))
colnames(poverty_household_type_table) <- c("Category", "Number of Unique Households (hidps)", "Number of households in Poor Thermal Comfort", "Percentage of Total Households")
print(as.tibble(poverty_household_type_table))
```



# Unit house retrofit costs. 
# find paper talking about range of energy savings for different data using NEED datasets. bridgen/hodgkin? pretty sure its in the latter at least. see other nature refs for any details.

https://www.instituteforgovernment.org.uk/sites/default/files/publications/tackling-energy-efficiency-problem.pdf
References NEED data.

https://assets.publishing.service.gov.uk/media/5a82338f40f0b62305b93052/BEIS_Update_of_Domestic_Cost_Assumptions_031017.pdf
2017 BEIS retrofit costing. 




 ns are right. subgrouping by column or row?  100% population for everyone in all column rather than % of the entire population. e.g. 5613/11322 approx 50%
 
1472 households want this to be the total percentage of total All housholds above. 1472/11322

same for children. want percentage of all households in above column 191/1054.

doing percentages from bottom half of top  half.

for second column want percentage of all households with poor thermal comfort 284/11322.

same through for each row. for pensioners want 112/5613.

same for second set of columns. would then compare these percentages for each row in both cases. e.g. expect higher percentage of pensioner households in fuel poverty than in general population.



1472 households want this to be the total percentage of total All housholds above. 1472/11322
same for children. want percentage of all households in above column 191/1054.
second column first four rows looks right.
second column bottom four rows looks right.