---
title: "Correlation Analysis - SF-12"
output:
  html_document:
    toc: true
    toc_float: true
    collapsed: false
    number_sections: true
    df_print: paged
    code_folding: hide
---


# SETUP

```{r "setup", include=FALSE}

library(tidyverse)
library(ggplot2)
library(ggridges) # for densities over time plots. 
library(knitr)
library(here)
library(kableExtra)

#workingDir <- "/home/luke/Documents/WORK/MINOS/"
workingDir <- normalizePath('../')
knitr::opts_knit$set(root.dir = workingDir)
knitr::opts_chunk$set(
  warning = FALSE,
  message = FALSE
)
rm(workingDir)
```

Source utils for some functions.

```{r, include=FALSE}
source(here::here('minos', 'utils_datain.R'))
```

## Data

```{r}
# Raw files have mismatched number of columns from the early to the late files (BHPS to UKHLS)
# therefore have to build the raw.files list a little more involved to ensure we only get 2009 onwards

# raw.files1 <- list.files(here::here('data', 'raw_US'), pattern='2009_US_cohort.csv', full.names = TRUE)
# raw.files2 <- list.files(here::here('data', 'raw_US'), pattern='201[4-9]{1}_US_cohort.csv', full.names = TRUE)
# raw.files3 <- list.files(here::here('data', 'raw_US'), pattern='202[0-9]{1}_US_cohort.csv', full.names = TRUE)
# 
# #raw.files <- c(raw.files1, raw.files2, raw.files3)
# raw.files <- c(raw.files2, raw.files3)

```


```{r, include=FALSE}
# Read raw datafiles in
#raw.files <- list.files(here::here('data', 'raw_US'), pattern='2[0-9]{3}_US_cohort.csv', full.names = TRUE)
raw.files <- list.files(here::here('data', 'raw_US'), pattern='[0-9]{4}_US_cohort.csv', full.names = TRUE)

raw.dat <- lapply(raw.files, function(file) {
  # Read the file
  df <- read.csv(file)
  
  # Standardize the 'ethnicity' column to character (or choose numeric if preferred)
  if ("ethnicity" %in% names(df)) {
    df$ethnicity <- as.character(df$ethnicity)
  }
  
  return(df)
}) %>%
  bind_rows()


# Process the data
raw.dat <- raw.dat %>%
  group_by(pidp) %>%
  # First replace those missing inapplicable (-8) with NA
  mutate(across(starts_with('hcond'), ~ na_if(., -8))) %>%
  # Forward fill missing values for hcond variables
  #mutate(across(starts_with("hcond"), ~ tidyr::replace_na(.))) %>%
  fill(starts_with("hcond"), .direction = "down") %>% 
  # Create the chronic_disease variable
  mutate(
    chronic_disease = if_any(starts_with("hcond"), ~ . == 1) * 1
  )

raw.dat <- raw.dat %>%
  filter(time > 2013) %>%
  filter(weight > 0) %>%  # remove all 0 weight individuals
  filter(SF_12 >= 0,
         sex %in% c('Male', 'Female'),
         age >= 16) %>% 
  mutate(age_group = cut(age, 
                         breaks = c(0,16,20,26,46,61,120), 
                         labels = c('0-15', '16-19', '20-25', '26-45', '46-60', '61+'),
                         include.lowest = TRUE,
                         right = FALSE),
         white_british = ifelse(ethnicity == 'WBI', 1, 0))


```

# FUNCTIONS

```{r}
prep_future_data <- function(data, var) {
  d1 <- data %>%
    select(pidp, time, .data[[var]], weight, age, sex, white_british, region, chronic_disease) %>%
    mutate(time = time - 1)
  
  d2 <- data %>%
    select(pidp, time, SF_12)
  
  d.merged <- merge(x = d1, y = d2, by = c('pidp', 'time'))
  
  return(d.merged)
}


generate_odds_ratios <- function(data, var) {
  # Create formula object for model from strings
  form <- formula(paste0(var, ' ~ high_risk + age + sex + white_british + chronic_disease'))
  
  model <- glm(form, 
               family = 'binomial', 
               data=data,
               weights = weight)
  options(scipen=999)
  print(summary(model))
  
  # Calculate odds ratio and confidence intervals
  odds_ratio = exp(coef(model)[[2]])
  confints = confint(model)
  odds.conf.low = exp(confints[[2]])
  odds.conf.high = exp(confints[[(length(confints) / 2) + 2]])
  
  return(list(odds_ratio, odds.conf.low, odds.conf.high))
}


odds_ratio_bin <- function(data, threshold, var, age_group, future = FALSE) {
  
  # If we want to look at future hospitalisation, needs some prep
  if(future) {
    data <- prep_future_data(data, var)
  }
  
  # Handle missing values in all variables (negative) and make sure var is factor
  data <- data %>%
    filter(.data[[var]] >= 0) %>%
    mutate(!!var := factor(.data[[var]]))
  
  # Recode hosp to binary 0/1, and create a binary from SF_12 for above/below
  #  threshold
  if (var == 'hosp_visits') {
    data$hosp_visits <- ifelse(data$hosp_visits == 1, 1, 0)
  }
  below <- paste0("Below ", threshold) # create labels dynamically from the threshold
  above <- paste0("Above ", threshold)
  data$high_risk <- ifelse(data$SF_12 < threshold, below , above)
  
  # Some info for the chisq result
  print(paste0('Threshold is ', threshold))
  print(paste0('Variable is ', var))
  print(paste0('Analysis is for future 12 months? ', future))
  
  # use function above to generate the model and calculate odds ratios
  output_list <- generate_odds_ratios(data, var)
  
  odds_ratio <- output_list[[1]]
  odds.conf.low <- output_list[[2]]
  odds.conf.high <- output_list[[3]]
  
  if(threshold == 45.6) {
    schema = '30-day'
  } else if (threshold == 48.9) {
    schema = '12-month'
  }
  
  if(future) {
    admission = 'Next 12 months'
  } else {
    admission = 'Previous 12 months'
  }
  
  if(var == 'hosp_visits') {
    return_df <- data.frame(HospitalAdmission = admission, 
                            threshold = schema, 
                            OR = odds_ratio, 
                            conf.low = odds.conf.low,
                            conf.high = odds.conf.high,
                            row.names = NULL)
  }
  
  if(var == 'gp_visits') {
    return_df <- data.frame(GPVisit = admission,
                            threshold = schema, 
                            OR = odds_ratio, 
                            conf.low = odds.conf.low,
                            conf.high = odds.conf.high,
                            row.names = NULL)
  }
  
  return(return_df)
}

plot_odds_ratios_single <- function(df_list, key_col = 'HospitalAdmission') {
  # merge df_list into one df
  merged <- do.call(rbind, df_list)
  
  if ('HospitalAdmission' %in%  colnames(merged)) {
    merged$HospitalAdmission <- factor(merged$HospitalAdmission, levels = c('Previous 12 months', 'Next 12 months'))
  } else if ('GPVisit' %in% colnames(merged)) {
    merged$GPVisit <- factor(merged$GPVisit, levels = c('Previous 12 months', 'Next 12 months'))
  }
  # Ensure factor type of variables and give proper labels
  #merged[[key_col]] <- factor(merged[[key_col]], levels = c('Previous 12 months', 'Next 12 months'))
  merged$threshold <- factor(merged$threshold, levels = c('12-month'))
  
  p1 <- ggplot(merged, aes(x = factor(threshold), y = OR, color = .data[[key_col]], fill = .data[[key_col]])) +
    geom_point(position = position_dodge(width = 0.5), size = 3) +    # Plot points with dodge for separation
    geom_errorbar(aes(ymin = conf.low, ymax = conf.high),              # Error bars for confidence intervals
                  position = position_dodge(width = 0.5), width = 0.2) +
    #geom_hline(yintercept = 1, linetype='dashed') +
    labs(x = "Depressive Disorder Threshold", y = "Odds Ratio", color = key_col, fill = key_col) +
    theme_minimal() +
    theme(legend.position = "right") +  # Place the legend on the right
    scale_color_manual(values = c("Next 12 months" = "blue", "Previous 12 months" = "red")) +  # Colors for future and non-future
    scale_fill_manual(values = c("Next 12 months" = "blue", "Previous 12 months" = "red"))
  
  print(p1)
}

plot_odds_ratios_combined <- function(df_list) {
  # Combine the list of dataframes into one
  merged <- do.call(rbind, df_list)
  
  # Ensure factor type of variables and give proper labels
  merged$HospitalAdmission <- factor(merged$HospitalAdmission, levels = c('Previous 12 months', 'Next 12 months'))
  merged$GPVisit <- factor(merged$GPVisit, levels = c('Previous 12 months', 'Next 12 months'))
  merged$threshold <- factor(merged$threshold, levels = c('12-month'))
  
  # Create a new variable to indicate plot grouping
  merged$PlotGroup <- ifelse(!is.na(merged$HospitalAdmission), "Hospital Admission", "GP Visit")
  merged$x_position <- ifelse(merged$PlotGroup == "Hospital Admission", 1, 2) # Assign x-positions
  
  # Update x-axis labels
  x_labels <- c("Hospital Admission", "GP Visit")
  
  p <- ggplot(merged, aes(x = factor(x_position), y = OR, color = threshold, fill = threshold)) +
    geom_point(position = position_dodge(width = 0.5), size = 3) +    # Points with dodge
    geom_errorbar(aes(ymin = conf.low, ymax = conf.high),             # Error bars for confidence intervals
                  position = position_dodge(width = 0.5), width = 0.2) +
    geom_vline(xintercept = 1.5, linetype = "dashed", color = "black") +  # Dashed vertical line separating groups
    geom_hline(yintercept = 0) +
    labs(x = NULL, y = "Odds Ratio", color = "Threshold", fill = "Threshold") +
    scale_x_discrete(labels = x_labels) +
    scale_color_manual(values = c("blue", "red")) +  # Customize colors
    scale_fill_manual(values = c("blue", "red")) +
    theme_minimal() +
    theme(
      legend.position = "right",               # Legend on the right
      axis.text.x = element_text(size = 10)   # Adjust x-axis label size
    )
  
  print(p)
}

```




# Odds Ratios - BINARY


## Hospital Visits

```{r}
prev <- odds_ratio_bin(data = raw.dat, threshold = 48.9, var = 'hosp_visits', future = FALSE)
future <- odds_ratio_bin(data = raw.dat, threshold = 48.9, var = 'hosp_visits', future = TRUE)

df_list <- list(prev, future)
plot_odds_ratios_single(df_list, key_col = 'HospitalAdmission')
```


## GP Visits

```{r}
prev <- odds_ratio_bin(data = raw.dat, threshold = 48.9, var = 'gp_visits', future = FALSE)
future <- odds_ratio_bin(data = raw.dat, threshold = 48.9, var = 'gp_visits', future = TRUE)

df_list <- list(prev, future)
plot_odds_ratios_single(df_list, key_col = 'GPVisit')
```

## Combined Hosp GP Plot

```{r}
prev_hosp <- odds_ratio_bin(data = raw.dat, threshold = 48.9, var = 'hosp_visits', future = FALSE)
future_hosp <- odds_ratio_bin(data = raw.dat, threshold = 48.9, var = 'hosp_visits', future = TRUE)

prev_gp <- odds_ratio_bin(data = raw.dat, threshold = 48.9, var = 'gp_visits', future = FALSE)
future_gp <- odds_ratio_bin(data = raw.dat, threshold = 48.9, var = 'gp_visits', future = TRUE)

df_list <- list(prev_hosp, future_hosp, prev_gp, future_gp)
#plot_odds_ratios_combined(df_list)

```

# Odds Ratios - ALL FACTOR LEVELS

## GP Visits

```{r}

odds_ratio_one_level <- function(data, threshold, var, target_gp_level, future = FALSE) {
  
  # Some info for the chisq result
  print(paste0('Threshold is ', threshold))
  print(paste0('Variable is ', var))
  print(paste0('Analysis is for future 12 months? ', future))
  print(paste0('Target gp_visits is: ', target_gp_level))
  
  # If we want to look at future hospitalisation, needs some prep
  if(future) {
    data <- prep_future_data(data, var)
  }
  
  # Handle missing values in all variables (negative) and make sure var is factor
  data <- data %>%
    filter(.data[[var]] >= 0) %>%
    mutate(!!var := factor(.data[[var]])) %>%
    mutate(gp_visits = ifelse(gp_visits == target_gp_level, 1, 0))
  
  below <- paste0("Below ", threshold) # create labels dynamically from the threshold
  above <- paste0("Above ", threshold)
  data$high_risk <- ifelse(data$SF_12 < threshold, below , above)
  
  # use function above to generate the model and calculate odds ratios
  output_list <- generate_odds_ratios(data, var)
  
  odds_ratio <- output_list[[1]]
  odds.conf.low <- output_list[[2]]
  odds.conf.high <- output_list[[3]]
  
  if(future) {
    admission = 'Next 12 months'
  } else {
    admission = 'Previous 12 months'
  }
  
  if(var == 'gp_visits') {
    return_df <- data.frame(Admission = admission,
                            GPVisits = target_gp_level,
                            OR = odds_ratio, 
                            conf.low = odds.conf.low,
                            conf.high = odds.conf.high,
                            Future = future,
                            row.names = NULL)
  }
  
  return(return_df)
}


odds_ratio_all_levels <- function(data) {
  df_list <- lapply(0:4, function(i) {
    list(
      gp_past = odds_ratio_one_level(data = data,
                                    threshold = 48.9,
                                    var = 'gp_visits',
                                    target_gp_level = i,
                                    future = FALSE),
      gp_future = odds_ratio_one_level(data = data,
                                      threshold = 48.9,
                                      var = 'gp_visits',
                                      target_gp_level = i,
                                      future = TRUE)
    )
  })
  # Row-bind the gp_past data frames together
  gp_past_all_levels <- do.call(rbind, lapply(df_list, `[[`, 'gp_past'))
  
  # Row-bind the gp_future data frames together
  gp_future_all_levels <- do.call(rbind, lapply(df_list, `[[`, 'gp_future'))
  
  # Return both sets of data frames
  return(list(gp_past_all_levels, gp_future_all_levels))
}

all_levels_results_gp <- odds_ratio_all_levels(data = raw.dat)

```


```{r}
library(ggplot2)
library(dplyr)

plot_gp_odds_ratios <- function(results_gp) {
  # Combine the two dataframes into one
  combined_results <- bind_rows(results_gp[[1]], results_gp[[2]])
  
  # Create the plot
  p <- ggplot(combined_results, aes(x = factor(GPVisits), y = OR, color = Future)) +
    # Add points for the Odds Ratios
    geom_point(position = position_dodge(0.5), size = 1) +
    # Add error bars for the confidence intervals
    geom_errorbar(aes(ymin = conf.low, ymax = conf.high), 
                  width = 0.2, 
                  position = position_dodge(0.5)) +
    # Add dashed line at OR == 1 to show positive / negative relationship
    geom_hline(yintercept = 1, linetype = 'dashed') +
    # Customize colors
    scale_color_manual(values = c("FALSE" = "blue", "TRUE" = "green"),
                       labels = c("Non-Future", "Future")) +
    # Customize labels and theme
    labs(
      title = "Odds Ratios of GP Visits",
      x = "Frequency of GP Visits (0-4)",
      y = "Odds Ratio (OR)",
      color = "Group"
    ) +
    theme_minimal() +
    theme(
      legend.position = "right",
      axis.text.x = element_text(size = 12),
      axis.title = element_text(size = 14),
      plot.title = element_text(size = 16, face = "bold")
    )
  
  # Print the plot
  return(p)
}

# Example usage:
plot_gp_odds_ratios(all_levels_results_gp)

```



# Sample Statistics

Going to separate the pop into 2 groups for this. Those under the 45.6 and those above.

```{r}
# load in summary stats utils script for functions
source('utils_summary_stats.R')

miss.values <- c(-10, -9, -8, -7, -3, -2, -1,
                 -10., -9., -8., -7., -3., -2., -1.)

#data <- read.csv('../data/raw_US/2014_US_cohort.csv')

continuous_vars <- c("age", "hh_netinc", "SF_12")
categorical_vars_before <- c("sex", "education_state", "region", "ethnicity", "universal_credit", "marstat", "labour_state_raw", "emp_type")
categorical_vars_after <- c("sex", "education_state", "region", "ethnicity", "universal_credit", "marital_status", "labour_state", "age_group")

data <- raw.dat %>%
  group_by(pidp) %>%
  fill(labour_state_raw) %>%  # forward filling the labour_state_raw variable before subsetting the year
  ungroup() %>%
  filter(time == 2014) %>%
  select(all_of(continuous_vars), all_of(categorical_vars_before), 'weight') %>%
  filter(rowSums(across(all_of(continuous_vars), ~ .x %in% miss.values)) == 0) %>%
  filter(rowSums(across(all_of(categorical_vars_before), ~ .x %in% miss.values)) == 0) %>%
  mutate(
    marital_status = case_when(
      marstat == 1 ~ "Single",
      marstat %in% c(2, 3, 10) ~ "Partnered",
      marstat %in% c(4, 5, 7, 8) ~ "Separated",
      marstat %in% c(6, 9) ~ "Widowed",
      TRUE ~ NA_character_  # Handle unexpected values
      )
  ) %>%
  mutate(
    labour_state = case_when(
    labour_state_raw %in% c("Employed", "Self-employed") & emp_type %in% c(1, -7, -9) ~ "FT Employed",
    labour_state_raw %in% c("Employed", "Self-employed") & emp_type == 2 ~ "PT Employed",
    labour_state_raw %in% c("Unemployed", "Short-term Working") ~ "Job Seeking",
    labour_state_raw %in% c("Student", "Government Training") ~ "FT Education",
    labour_state_raw %in% c("Family Care") ~ "Family Care",
    labour_state_raw %in% c("Retired", "Maternity Leave", "Sick/Disabled") ~ "Not Working",
    TRUE ~ NA_character_  # Handle unexpected values
    )) %>%
  mutate(age_group = cut(age, 
                         breaks = c(0,16,20,26,46,61,70,120), 
                         labels = c('0-15', '16-19', '20-25', '26-45', '46-60', '61-70', '70+'),
                         include.lowest = TRUE,
                         right = FALSE),
         white_british = ifelse(ethnicity == 'WBI', 1, 0)
         )
```

## Gender

```{r}
# Generate stratified summary statistics by gender (sex)
summary_by_gender <- generate_summary(data, strat_var = "sex", continuous_vars, categorical_vars_after, weight_col = "weight")

# Print the summary tables
print_summary(summary_by_gender, file_prefix = "gender")
```

## Thresholds

### 48.9 (12-month)

```{r}
data.mod <- data %>%
  mutate(under.12.month = SF_12 < 48.9)

summary.48.9 <- generate_summary(data.mod, strat_var = "under.12.month", continuous_vars, categorical_vars_after, weight_col = "weight")

# Print the summary tables
print_summary(summary.48.9, file_prefix = "Under 48.9")
```







```{r}

```






# DEFUNKT

## Odds Ratio Age Filtered

```{r}
# Function to aid in the filtering for the odds_ratio and chisq function below
filter_helper <- function(data, target_var, target_level) {
  if (target_var == 'age_group') {
    # Check for possible age_group values
    stopifnot(target_level %in% c('all', '16-19', '20-25', '26-45', '46-60', '61+'))
  }
  if (target_var == 'gp_visits') {
    # Check for possible gp_visits values
    stopifnot(target_level %in% c('all', 1:5))
  }
  if (target_level == 'all') {
    return(data)
  } else {
    return(data %>% filter(.data[[target_var]] == target_level))
  }
}


odds_ratio_and_chisq_filtered <- function(data, threshold, var, target_age_group = 'all', target_gp_level = 'all', future = FALSE) {
  
  # Some info for the chisq result
  print(paste0('Threshold is ', threshold))
  print(paste0('Variable is ', var))
  print(paste0('Analysis is for future 12 months? ', future))
  print(paste0('Target age_group is: ', target_age_group))
  print(paste0('Target gp_visits is: ', target_gp_level))
  
  # If we want to look at future hospitalisation, needs some prep
  if(future) {
    data <- prep_future_data(data, var)
  }
  
  #return(data)
  
  # Handle missing values in all variables (negative) and make sure var is factor
  data <- data %>%
    filter(.data[[var]] >= 0,
           SF_12 >= 0) %>%
    mutate(!!var := factor(.data[[var]])) %>%
    filter_helper(., 'age_group', target_age_group) %>%
    filter_helper(., 'gp_visits', target_gp_level)
  
  # Recode hosp to binary 0/1, and create a binary from SF_12 for above/below
  #  threshold
  if (var == 'hosp_visits') {
    data$hosp_visits <- ifelse(data$hosp_visits == 1, 1, 0)
  }
  below <- paste0("Below ", threshold) # create labels dynamically from the threshold
  above <- paste0("Above ", threshold)
  data$high_risk <- ifelse(data$SF_12 < threshold, below , above)
  
  # Create formula object for model from strings
  form <- formula(paste0(var, ' ~ high_risk + age + sex'))
  #print(form)
  
  model <- glm(form, 
               family = 'binomial', 
               data=data,
               weights = weight)
  options(scipen=999)
  print(summary(model))
  
  # Calculate odds ratio and confidence intervals
  odds_ratio = exp(coef(model)[[2]])
  
  #print('Confidence Intervals: ')
  #print(exp(confint(model)))
  odds.conf.low = exp(confint(model)[[2]])
  odds.conf.high = exp(confint(model)[[6]])
  
  if(threshold == 45.6) {
    schema = '30-day'
  } else if (threshold == 48.9) {
    schema = '12-month'
  }
  
  if(future) {
    admission = 'Next 12 months'
  } else {
    admission = 'Previous 12 months'
  }
  
  if(var == 'hosp_visits') {
    return_df <- data.frame(HospitalAdmission = admission, 
                            threshold = schema, 
                            OR = odds_ratio, 
                            conf.low = odds.conf.low,
                            conf.high = odds.conf.high,
                            row.names = NULL)
  }
  
  if(var == 'gp_visits') {
    return_df <- data.frame(GPVisit = admission, 
                            threshold = schema, 
                            OR = odds_ratio, 
                            conf.low = odds.conf.low,
                            conf.high = odds.conf.high,
                            row.names = NULL)
  }
  
  return(return_df)
}

```


## Quick Data Checking

```{r}
table(raw.dat$sex, raw.dat$hosp_visits)
```


## Clinical Depression

First we'll to see if there is a relationship between SF-12 Mental Component Score (MCS) and clinical_depression (from the UKHLS variable [hcond17](https://www.understandingsociety.ac.uk/documentation/mainstage/variables/hcond17/) - has a doctor ever told you that you have clinical depression?). clinical_depression == 0 is no clinical depression, and == 1 is clinical depression.

```{r}
dat <- raw.dat %>%
  select(pidp, time, SF_12, clinical_depression) %>%
  filter(clinical_depression >= 0)

t.test(SF_12 ~ clinical_depression, data = dat, var.equal=FALSE)
```

The above T-test shows a significant difference in mean SF-12 between individuals with and without clinical depression. The difference in means is also very large in the context of SF-12 MCS, with an 18 point gap.

## Hospital Utilisation

Next we will test the relationship between SF-12 MCS and Hospital Utilisation (from UKHLS variable [hosp](https://www.understandingsociety.ac.uk/documentation/mainstage/variables/hosp/) - In the last 12 months, have you been in hospital or clinic as an in-patient overnight or longer?).

```{r}
dat <- raw.dat %>%
  select(pidp, time, SF_12, hosp_visits) %>%
  filter(hosp_visits > 0)

dat$hosp_visits <- ifelse(dat$hosp_visits == 1, 1, 0)

t.test(SF_12 ~ hosp_visits, data = dat, var.equal=FALSE)
```

The above T-test shows once again that there is a significant difference in the mean SF-12 between individuals who have 

### Hospital Use in the Future

```{r}
d1 <- raw.dat %>%
  select(pidp, time, hosp_visits) %>%
  mutate(time = time - 1)

d1$hosp_visits <- ifelse(d1$hosp_visits == 1, 1, 0)

d2 <- raw.dat %>%
  select(pidp, time, SF_12)

d.merged <- merge(x = d1, y = d2, by = c('pidp', 'time'))
```

```{r}
t.test(SF_12 ~ hosp_visits, data = d.merged, var.equal=FALSE)
```

## GP Visit

### chi-squared

```{r}
dat <- raw.dat %>%
  select(pidp, time, SF_12, gp_visits) %>%
  filter(gp_visits >= 0)

dat$gp_visits <- factor(dat$gp_visits)

#t.test(SF_12 ~ gp_visits, data = dat, var.equal=FALSE)
#wilcox.test(SF_12 ~ gp_visits, data = dat)

threshold <- 48.9
below <- paste0("Below ", threshold) # create labels dynamically from the threshold
above <- paste0("Above ", threshold)
dat$high_risk <- ifelse(dat$SF_12 < threshold, below , above)


# Table the results to prepare for fishers test
table_high_risk <- table(dat$high_risk, dat$gp_visits)
print(table_high_risk)

# Fishers exact test
#fisher_test <- fisher.test(table_high_risk)

chi.gp <- chisq.test(table_high_risk)

print(chi.gp)
print(chi.gp$observed)
print(chi.gp$expected)

print(chi.gp$statistic)
```

### logistic regression odds ratios

```{r}
model <- glm(gp_visits ~ high_risk, family = 'binomial', data=dat)
options(scipen=999)
summary(model)
print('--------------------------------')
print(exp(coef(model)))

print('Odds Ratio: ')
print(exp(coef(model)[[2]]))

print('Confidence Intervals: ')
print(exp(confint(model)))
print(exp(confint(model)[[2]]))
print(exp(confint(model)[[4]]))

```


## SF12 Histograms

```{r}
t1 <- raw.dat %>%
  filter(hosp_visits == 1)  # YES TO HOSPITAL USE

t2 <- raw.dat %>%
  filter(hosp_visits == 2)  # NO TO HOSPITAL USE

hist(t1$SF_12,
     main = 'Histogram of SF-12 (Visited hospital in previous 12 months)',
     xlab = 'SF-12')
hist(t2$SF_12,
     main = 'Histogram of SF-12 (No hospital visit in previous 12 months)',
     xlab = 'SF-12')
```