---
title: "Depressive Threshold Investigation"
output:
  html_document:
    toc: true
    toc_float: true
    collapsed: false
    number_sections: false
    df_print: paged
    code_folding: hide
---




# TODO
- [x] Generate binary flags for each of the Scottish priority family groups
- [x] As part of question 2, generate a forest plot for the priority family groups and below the threshold
- [x] Recode hospital and gp variables into 0/1 binary
- [x] Remove records with missing future hosp and gp value (last wave will be removed)
- [ ] Add variables to the Characteristics analysis
    - [ ] GOR (region)
    - [ ] Rurality
    - [ ] Highest Education Qualification
- [x] Add additional factors to the models to control for attrition and starting survey in poor health
    - [x] Dummy for present in next wave
    - [x] Dummy for present in all waves
    - [x] Counter for number of observations
- [ ] Do summary stats table - Remember rowSums not colSums
- [ ] Change plot labels from p value to OR value




# SETUP

```{r "setup", include=FALSE}

library(tidyverse)
library(ggplot2)
library(ggridges) # for densities over time plots. 
library(knitr)
library(here)
library(survey)
library(lme4)
library(glmmTMB)
library(broom.mixed)
library(gtsummary)

#workingDir <- "/home/luke/Documents/WORK/MINOS/"
workingDir <- normalizePath('../')
knitr::opts_knit$set(root.dir = workingDir)
knitr::opts_chunk$set(
  warning = FALSE,
  message = FALSE
)
rm(workingDir)
```

Source utils for some functions.

```{r, include=FALSE}
source(here::here('minos', 'utils_datain.R'))
```



```{r, include=FALSE}
# Read raw datafiles in
#raw.files <- list.files(here::here('data', 'raw_US'), pattern='2[0-9]{3}_US_cohort.csv', full.names = TRUE)
raw.files <- list.files(here::here('data', 'raw_US'), pattern='[0-9]{4}_US_cohort.csv', full.names = TRUE)

# Read all the files, and handle any problems with columns being different types
#   in different years
raw.dat <- lapply(raw.files, function(file) {
  # Read the file
  df <- read.csv(file)
  
  # Standardize the 'ethnicity' column to character (or choose numeric if preferred)
  if ("ethnicity" %in% names(df)) {
    df$ethnicity <- as.character(df$ethnicity)
  }
  
  return(df)
}) %>%
  bind_rows()

cpi_dat <- read.csv(here::here('persistent_data', 'CPI_202309.csv'))

```

Do all the pre-processing for the raw data here.

```{r}
# Forward fill some variables
#   All chronic disease variables ('hcond#')
#   nkids_ind_raw
raw.dat.p <- raw.dat %>%
  group_by(pidp) %>%
  # First replace those missing inapplicable (-8) with NA
  mutate(across(starts_with('hcond'), ~ na_if(., -8))) %>%
  mutate(across('nkids_ind_raw', ~ na_if(., -8))) %>%
  # Forward fill missing values
  fill(starts_with("hcond"), .direction = "down") %>%
  fill('nkids_ind_raw', .direction = "down") %>%
  # Create the chronic_disease variable and rename nkids_ind_raw
  mutate(
    chronic_disease = if_any(starts_with("hcond"), ~ . == 1) * 1,
    nkids_ind = nkids_ind_raw
  )

# Remove some records that are not useful, i.e. missing important vars
#   Also generate some variables like age_group and white_british (binary)
raw.dat.p <- raw.dat.p %>%
  filter(time > 2013) %>%
  filter(weight > 0) %>%  # Remove all 0-weight individuals
  filter(
    !hh_netinc %in% c(-9, -8, -7, -3, -2, -1),
    SF_12 >= 0,
    sex %in% c('Male', 'Female'),
    age >= 16,
    hosp_visits %in% c(1, 2),  # Ensure hosp_visits is present
    gp_visits %in% c(0, 1, 2, 3, 4),
    education_state %in% c(0,1,2,3,5,6,7)
  ) %>% 
  mutate(  # Recode marstat variable into string marital_status
    marital_status = case_when(
      marstat == 1 ~ "Single",
      marstat %in% c(2, 3, 10) ~ "Partnered",
      marstat %in% c(4, 5, 7, 8) ~ "Separated",
      marstat %in% c(6, 9) ~ "Widowed",
      TRUE ~ NA_character_  # Handle unexpected values
    )
  ) %>%
  filter(
    marital_status %in% c('Single', 'Partnered', 'Separated', 'Widowed')
  ) %>%
  mutate(  # Recode labour_state_raw into string labour_state
    labour_state = case_when(
      labour_state_raw %in% c("Employed", "Self-employed") & emp_type %in% c(1, -7, -9) ~ "FT Employed",
      labour_state_raw %in% c("Employed", "Self-employed") & emp_type == 2 ~ "PT Employed",
      labour_state_raw %in% c("Unemployed", "Short-term Working") ~ "Job Seeking",
      labour_state_raw %in% c("Student", "Government Training") ~ "FT Education",
      labour_state_raw %in% c("Family Care") ~ "Family Care",
      labour_state_raw %in% c("Retired", "Maternity Leave", "Sick/Disabled") ~ "Not Working",
      TRUE ~ NA_character_  # Handle unexpected values
    )
  ) %>%
  mutate(age_group = cut(age, 
                         breaks = c(0, 16, 20, 26, 46, 61, 120), 
                         labels = c('0-15', '16-19', '20-25', '26-45', '46-60', '61+'),
                         include.lowest = TRUE,
                         right = FALSE)) %>%
  mutate(  # Recode hosp_visits into binary 0/1
    hosp_visits = case_when(
      hosp_visits == 1 ~ 1,
      hosp_visits == 2 ~ 0,
      TRUE ~ NA_real_
    )
  ) %>%
  mutate(white_british = ifelse(ethnicity == 'WBI', 1, 0),
         depress_risk = SF_12 < 48.9,
         FT_employed = labour_state == 'FT Employed',
         PT_employed = labour_state == 'PT Employed',
         employed = labour_state %in% c('FT Employed', 'PT Employed'),
         gp_binary = gp_visits > 0)



# Generate binary flags for each of the priority family groups
raw.dat.p <- raw.dat.p %>%
  group_by(hidp, time) %>%  # These are household groupings so group_by hidp
  mutate(priority_min_ethnic = ifelse(any(ethnicity != 'WBI'), TRUE, FALSE),  # minority ethnic 
         priority_child_under_one = ifelse(any(substr(child_ages, 1, 1) == 0), TRUE, FALSE),  # child under one
         priority_three_plus_children = ifelse(any(nkids >= 3), TRUE, FALSE),  # three plus children
         priority_mother_under_25 = ifelse(any(age < 25 & nkids_ind > 0), TRUE, FALSE),  # mother under 25
         priority_disabled = ifelse(any(labour_state_raw == "Sick/Disabled"), TRUE, FALSE),  # disabled adult or child
         priority_lone_parent = ifelse(any(nkids > 0 & n() == 1), TRUE, FALSE)) %>%  # lone parent household
  ungroup()

# Generate vars for future use of healthcare 
raw.dat.p <- raw.dat.p %>%
  arrange(pidp, time) %>%  # First sort by person and time so we can use lead()
  group_by(pidp) %>%
  mutate(
    future_hosp_visits = lead(hosp_visits, n = 1),
    future_gp_binary = lead(gp_binary, n = 1)
  ) %>%
  ungroup()

# Generate dummys for controlling for attrition and poor starting health
raw.dat.p <- raw.dat.p %>%
  group_by(pidp) %>%
  mutate(
    # Dummy for present next wave
    present_next_wave = if_else(lead(time, default = NA) == time + 1, 1, 0, missing = 0),
    # Dummy for present in all waves
    present_all_waves = if_else(n_distinct(time) == max(time) - min(time) + 1, 1, 0),
    # Counter for number of observations
    num_obs = n()
  ) %>%
  ungroup()
```

Need to do some processing on the cpi dataframe, then adjust income values for inflation. Using November 2020 for baseline £ value.

```{r}
cpi <- cpi_dat %>%
  select(-X)

raw.dat.adj <- raw.dat.p %>%
  filter(hh_int_y != -9,
         hh_int_y != -8,
         hh_int_m != -9,
         hh_int_m != -8) %>%  # if no interview date can't do inflation adjustment
  mutate(Date = hh_int_y * 100 + hh_int_m) %>%  # Combine year and month into a Date variable with format YYYYMM (to match cpi data)
  left_join(cpi, by = "Date") %>%  # join cpi data onto raw.dat by Date column 
  mutate(hh_netinc_adjusted = hh_netinc / CPI * 100)  # adjust pound value using CPI with base November 2020
  
```


# RESEARCH QUESTIONS

1. Are you more likely to be under the threshold if in poverty? (Simple descriptive stats - pov/not
pov & threshold/not threshold)
2. a) What characteristics are associated with (make you more likely?) being under the threshold
(education, age, marital stat, employment, etc.)
2. b) Does poverty have an effect here that is independent of these characteristics? (run same models
this time controlling for poverty)
3. Why do we care? Under threshold means more likely to require healthcare and therefore cost
more money for the state. Looping that back means...
- Reducing poverty helps to reduce proportion of people under the threshold, which will reduce the
need for healthcare in the general population, which saves money
- Use the discussion to talk about the ScotGov priority subgroups, can relate these subgroups to
poverty and therefore lower mental well-being and increased need for healthcare

# ANALYSES REQUIRED

1. Link poverty to the threshold. First look at descriptive statistics, then use odds ratio (chisq in place
of glm) to look at the relationship between the 2 groups
2. Odds ratios for characteristics? Simple descriptive stats? Think an odds ratio plot with each
characteristic showing whether more or less likely to be seen in group under threshold
3. Same plot but with poverty added? Could just add poverty to the plot above and get same effect?
Or maybe this is more about how controlling for poverty changes the results? Do both then go back
to Nik and see what he thinks
4. Odds ratios for how threshold affects future use of healthcare. Can remove the previous 12 months
stuff as this is really more about the future than explaining the past

# 1. Link Poverty to Threshold

First job is to link the poverty rate to the SF-12 threshold. The hypothesis here is that the rate of poverty is significantly
higher in the group under the threshold. At first we only want to explore this specific relationship, so we won't control
for any other factors.
We will focus on Relative Poverty for now, as it is easier to justify (and work with) the values in a population such as US.

Research Question:
1. Are you more likely to be under the threshold if in poverty? (Simple descriptive stats - pov/not
pov & threshold/not threshold)

```{r}
# First step is to calculate the relative poverty threshold, and we can then 
#   attach that to the original data as a binary flag
#   The relative poverty threshold should be calculated on households and not individuals,
#   so we need to take only 1 individual from each household
pov_thresholds_yearly <- raw.dat.adj %>%
  select(pidp, hidp, time, hh_netinc_adjusted) %>%
  group_by(hidp) %>%
  slice(1) %>%
  ungroup() %>%
  group_by(time) %>%
  summarise(rel_pov_thresh = mean(hh_netinc_adjusted) * 0.6)

# Now attach the threshold back onto the data and create a binary poverty variable
data <- raw.dat.adj %>%
  left_join(pov_thresholds_yearly, by = "time") %>%
  mutate(poverty = hh_netinc_adjusted < rel_pov_thresh) %>%
  select(-rel_pov_thresh, -Date, -CPI) %>%
  filter(!is.na(future_hosp_visits),
         !is.na(future_gp_binary))

# Now take a small subset of the data and ask the question for each year
#dat.test <- data %>%
#  select(pidp, hidp, time, depress_risk, poverty)
```

## Rao-Scott Chi-Squared

A normal Chi-Squared test is not suitable here due to the repeated observations over time. This invalidates the assumption of independence in the observations so we need to use something different. The Rao-Scott Chi-Squared test from the survey package seems to be what we need, as this can handle complex survey data, including clustering and weights.

```{r}
# First create survey design object
design <- svydesign(id = ~pidp, data = data, weights = ~weight)

# Now perform Rao-Scott test
rs_test <- svychisq(~depress_risk + poverty, design = design)
print(rs_test)


## Visualise
# Contingency Table
table <- svytable(~depress_risk + poverty, design = design)
print(table)


# Convert to proportions
prop_table <- prop.table(table, margin = 2)  # Proportions within poverty groups
df <- as.data.frame(as.table(prop_table))

# Plot
ggplot(df, aes(x = poverty, y = Freq, fill = depress_risk)) +
  geom_bar(stat = "identity", position = "fill") +
  labs(
    x = "Poverty Status",
    y = "Proportion",
    fill = "Low SF-12 MCS",
    title = "Proportion of Low SF-12 MCS Scores by Poverty Status"
  ) +
  scale_y_continuous(labels = scales::percent) +
  theme_minimal()
```

## Odds Ratio (Mixed-Effects Logistic Regression)

The above Rao-Scott Chi-Squared test output shows a very significant result - that there is a relationship between poverty and the depressive risk threshold that is very unlikely to be a result of random chance.

Now we have verified a significant relationship we can quantify it by calculating odds ratios.

```{r}
model <- glmmTMB(
  depress_risk ~ poverty + (1 | pidp),
  data = data,
  family = binomial(link = "logit")
)

summary(model)
```

Now we have the model we can use it to calculate the odds ratio.

```{r}
# get fixed effects
coef_summary <- summary(model)$coefficients$cond
# calculate odds ratio
odds_ratios <- exp(coef_summary[, "Estimate"])
# add confidence intervals
conf_int <- exp(confint(model, parm = "beta_", level = 0.95))

# Combine results into a readable table
results <- data.frame(
  Term = rownames(coef_summary),
  Odds_Ratio = odds_ratios,
  Lower_CI = conf_int[, 1],
  Upper_CI = conf_int[, 2],
  p_value = coef_summary[, "Pr(>|z|)"]
)

print(results)

ggplot(results, aes(x = Term, y = Odds_Ratio)) +
  geom_point(size = 3) +
  geom_errorbar(aes(ymin = Lower_CI, ymax = Upper_CI), width = 0.2) +
  geom_hline(yintercept = 1, linetype = "dashed", color = "red") +
  #scale_y_log10() +  # Log scale for better visualization
  labs(
    title = "Odds Ratios and 95% Confidence Intervals",
    x = "Predictor",
    y = "Odds Ratio"
  ) +
  theme_minimal()
```


# 2. a) Link Characteristics to Threshold

2. a) What characteristics are associated with (make you more likely?) being under the threshold
(education, age, marital stat, employment, etc.)

Forest plot: "https://medium.com/@ginoasuncion/visualizing-logistic-regression-results-using-a-forest-plot-in-python-bc7ba65b55bb"

## Fit Model

```{r}
model_2a <- glmmTMB(
  depress_risk ~ age_group + sex + white_british + labour_state + marital_status + present_next_wave + present_all_waves + num_obs + (1 | pidp),
  data = data,
  family = binomial(link = "logit")
)

```

## Calculate Odds Ratios

```{r}

produce_OR_forest_data <- function(model) {
  # Extract fixed effects
  coef_summary <- summary(model)$coefficients$cond
  
  # Calculate odds ratios and confidence intervals
  odds_ratios <- exp(coef_summary[, "Estimate"])
  conf_int <- exp(confint(model, parm = "beta_", level = 0.95))
  
  # Combine results into a readable table
  forest_data <- data.frame(
    Term = rownames(coef_summary),
    Odds_Ratio = odds_ratios,
    Lower_CI = conf_int[, 1],
    Upper_CI = conf_int[, 2],
    p_value = coef_summary[, "Pr(>|z|)"]
  )
  
  # Keep only the predictors of interest (excluding intercept)
  forest_data <- forest_data[!forest_data$Term %in% "(Intercept)", ]
  
  # Do some cleanup of the plot labels
  forest_data$Term <- recode(
    forest_data$Term,
    `age_group20-25` = "Age: 20-25",
    `age_group26-45` = "Age: 26-45",
    `age_group46-60` = "Age: 46-60",
    `age_group61+` = "Age: 61+",
    `sexMale` = "Sex: Male",
    `white_british` = "Ethnicity: White-British",
    `marital_statusWidowed` = "Marital Status: Widowed",
    `marital_statusSingle` = "Marital Status: Single",
    `marital_statusSeparated` = "Marital Status: Separated",
    `labour_statePT Employed` = "Labour State: PT Employed",
    `labour_stateFT Employed` = "Labour State: FT Employed",
    `labour_stateFT Education` = "Labour State: PT Education",
    `labour_stateNot Working` = "Labour State: Not Working",
    `labour_stateJob Seeking` = "Labour State: Job Seeking",
    `employedTRUE` = "Employed",
    `povertyTRUE` = "Poverty",
    `priority_min_ethnicTRUE` = "Priority: Minority Ethnic",
    `priority_child_under_oneTRUE` = "Priority: Child Under One",
    `priority_three_plus_childrenTRUE` = "Priority: Three Plus Children",
    `priority_mother_under_25TRUE` = "Priority: Mother Under 25",
    `priority_disabledTRUE` = "Priority: Disabled Family Member",
    `priority_lone_parentTRUE` = "Priority: Lone Parent"
  )
  

  
  return(forest_data)
}

forest_2a <- produce_OR_forest_data(model_2a)
```

## Forest Plot

```{r}
ggplot(forest_2a, aes(x = Term, y = Odds_Ratio)) +
  geom_point(size = 3) +
  geom_errorbar(aes(ymin = Lower_CI, ymax = Upper_CI), width = 0.2) +
  geom_hline(yintercept = 1, linetype = "dashed", color = "red") +
  geom_text(aes(label = ifelse(p_value < 0.05, "p < 0.05", "")), 
            nudge_x = 0.3, size = 3, hjust = 0) +
  scale_y_log10() +
  coord_flip() +
  labs(
    title = "Forest Plot of Odds Ratios with p-values",
    x = "",
    y = "Odds Ratio (log scale)"
  ) +
  theme_minimal()
```

# 2. b) How Does Poverty Change This?

2. b) Does poverty have an effect here that is independent of these characteristics? (run same models
this time controlling for poverty)

This is simple, just generating a new model with the poverty term added.

```{r}
model_2b <- glmmTMB(
  depress_risk ~ age_group + sex + white_british + labour_state + marital_status + poverty + present_next_wave + present_all_waves + num_obs + (1 | pidp),
  data = data,
  family = binomial(link = "logit")
)

forest_2b <- produce_OR_forest_data(model_2b)

```

```{r}

ggplot(forest_2b, aes(x = Term, y = Odds_Ratio)) +
  geom_point(size = 3) +
  geom_errorbar(aes(ymin = Lower_CI, ymax = Upper_CI), width = 0.2) +
  geom_hline(yintercept = 1, linetype = "dashed", color = "red") +
  geom_text(aes(label = ifelse(p_value < 0.05, "p < 0.05", "")), 
            nudge_x = 0.3, size = 3, hjust = 0) +
  scale_y_log10() +
  coord_flip() +
  labs(
    title = "Forest Plot of Odds Ratios with p-values",
    x = "",
    y = "Odds Ratio (log scale)"
  ) +
  theme_minimal()
```

# 2. c) Priority Family Groups

```{r}
model_2c <- glmmTMB(
  depress_risk ~ priority_min_ethnic + priority_child_under_one + priority_three_plus_children + priority_mother_under_25 + priority_disabled + priority_lone_parent + present_next_wave + present_all_waves + num_obs + (1 | pidp),
  data = data,
  family = binomial(link = "logit")
)

forest_2c <- produce_OR_forest_data(model_2c)

ggplot(forest_2c, aes(x = Term, y = Odds_Ratio)) +
  geom_point(size = 3) +
  geom_errorbar(aes(ymin = Lower_CI, ymax = Upper_CI), width = 0.2) +
  geom_hline(yintercept = 1, linetype = "dashed", color = "red") +
  geom_text(aes(label = ifelse(p_value < 0.05, "p < 0.05", "")), 
            nudge_x = 0.3, size = 3, hjust = 0) +
  scale_y_log10() +
  coord_flip() +
  labs(
    title = "Forest Plot of Odds Ratios with p-values",
    x = "",
    y = "Odds Ratio (log scale)"
  ) +
  theme_minimal()
```


# 3. Depressive Threshold & Healthcare

3. Why do we care? Under threshold means more likely to require healthcare and therefore cost
more money for the state. Looping that back means...
- Reducing poverty helps to reduce proportion of people under the threshold, which will reduce the
need for healthcare in the general population, which saves money
- Use the discussion to talk about the ScotGov priority subgroups, can relate these subgroups to
poverty and therefore lower mental well-being and increased need for healthcare

Now produce odds ratios for the relationship between the threshold and healthcare utilisation **in the future**.
This means generating variables for hospital admission and gp visits (binary) in the next 12 months.

We will only use the binary for gp visits and not the ordinal levels (at least for now).


```{r}
model_3_hosp <- glmmTMB(
  future_hosp_visits ~ depress_risk + present_next_wave + present_all_waves + num_obs + (1 | pidp),
  data = data,
  family = binomial(link = "logit")
)

model_3_gp <- glmmTMB(
  future_gp_binary ~ depress_risk + present_next_wave + present_all_waves + num_obs + (1 | pidp),
  data = data,
  family = binomial(link = "logit")
)

# Extract odds ratios and confidence intervals
results <- bind_rows(
  tidy(model_3_hosp, conf.int = TRUE, effects = "fixed") %>% 
    filter(term == "depress_riskTRUE") %>% 
    mutate(variable = "Future Hospital Visits"),
  
  tidy(model_3_gp, conf.int = TRUE, effects = "fixed") %>% 
    filter(term == "depress_riskTRUE") %>% 
    mutate(variable = "Future GP Visits")
)

# Rename columns for clarity
results <- results %>%
  select(variable, estimate, conf.low, conf.high) %>%
  mutate(
    odds_ratio = exp(estimate),
    lower_ci = exp(conf.low),
    upper_ci = exp(conf.high)
  ) %>%
  select(variable, odds_ratio, lower_ci, upper_ci)

print(results)

# Plot results
ggplot(results, aes(x = variable, y = odds_ratio, ymin = lower_ci, ymax = upper_ci)) +
  geom_pointrange(color = "blue", size = 0.8) +
  geom_hline(yintercept = 1, linetype = "dashed", color = "red") +
  coord_flip() +  # Flip coordinates for easier reading
  labs(
    title = "Odds Ratios for Healthcare Use by Depression Risk",
    x = "Healthcare Type",
    y = "Odds Ratio (95% CI)"
  ) +
  theme_minimal()

```

# Summary Statistics

Row sums!

```{r}
dat.2014 <- data %>%
  filter(time == 2015)

table <- dat.2014 %>%
  select(depress_risk, age, hh_netinc_adjusted, sex, marital_status, education_state, labour_state) %>%
  tbl_summary(
    by = depress_risk, 
    type = list(
      age ~ "continuous",
      hh_netinc_adjusted ~ "continuous",
      sex ~ "categorical",
      marital_status ~ "categorical",
      education_state ~ "categorical",
      labour_state ~ "categorical"
      ),
    statistic = list(
      all_continuous() ~ "{mean} ({sd})",
      all_dichotomous() ~ "{p}%",
      all_categorical() ~ "{p}%"
      ),
    percent = "row"  # Ensures percentages sum to 100 across rows, not columns
    ) %>%
  add_p() %>%  # Add p-values for group comparisons
  modify_header(label ~ "**Variable**") %>%  # Format the table headers
  modify_spanning_header(all_stat_cols() ~ "**Depression Risk**")  # Add header span


print(table)
```

```{r}
latex_code <- table %>%
  as_gt() %>%
  gt::as_latex()

filename <- '/home/luke/Documents/WORK/MINOS/DELIVERABLES/MCS_to_hosp/sum_stats_table.tex'

writeLines(latex_code, filename)
```








```{r}

```

