---
title: "Financial Situation"
output: html_document
bibliography: 
  - "`r here::here('docsrc', 'refs.bib')`"
---


```{r setup, include=FALSE}
library(dplyr)
library(here)
library(ranger)
library(caret)

source(here::here("docsrc", "documentation", "notebooks", "sphinx_notebook_utils.R"))
source(here::here('minos', 'utils_datain.R'))
source(here::here('minos', 'utils_validation_vis.R'))
model_path <- here::here("data", "transitions", "financial_situation", "rfo", "financial_situation_RFO.rds")
model <- readRDS(model_path)

data <- read.csv(here::here("data", "final_US", "2020_US_cohort.csv"))

obs <- data$financial_situation
data$financial_situation_last <- data$financial_situation

preds <- ranger::predictions(stats::predict(model, data))
column_names <- colnames(preds)
preds <-glmnet::rmult(preds)
#preds <- plyr::mapvalues(preds, from=c(1,2,3), to= column_names)
#preds <- factor(preds,
#                levels = c("High", "Medium", "Low"))
v <- "financial_situation"




### Read data in for handovers plots
# Read raw datafiles in
raw.files <- list.files(here::here('data', 'final_US'), pattern='[0-9]{4}_US_cohort.csv', full.names = TRUE)
raw.dat <- do.call(rbind, lapply(raw.files, read.csv))
raw.dat <- raw.dat %>%
  filter(weight > 0)

out.path <- here::here('output', 'default_config/')
base.dat <- read_singular_local_out(out.path, 'baseline', 
                                    drop.dead = TRUE, 
                                    drop.zero.weight = TRUE)

# cut off any years of raw data AFTER start year of simulation
if (min(base.dat$time) <= max(raw.dat$time)) {
  raw.dat <- raw.dat %>%
    filter(time <= min(base.dat$time))
}

# cut missing data for key variable
raw.dat <- raw.dat %>%
  filter(!.data[[v]] %in% miss.values)


### Read data in for cross-val plots
out.path <- here::here('output', 'cv')
cv1 <- read_singular_local_out(here::here(out.path, 'default1/'), 'baseline', drop.dead = TRUE)
cv2 <- read_singular_local_out(here::here(out.path, 'default2/'), 'baseline', drop.dead = TRUE)
cv3 <- read_singular_local_out(here::here(out.path, 'default3/'), 'baseline', drop.dead = TRUE)
cv4 <- read_singular_local_out(here::here(out.path, 'default4/'), 'baseline', drop.dead = TRUE)
cv5 <- read_singular_local_out(here::here(out.path, 'default5/'), 'baseline', drop.dead = TRUE)

cvlist <- list(cv1, cv2, cv3, cv4, cv5)
cv <- do.call(rbind, cvlist)

# cv simulation batches
cv.simul.files1 <- list.files(here::here('data', 'final_US', 'cross_validation', 'batch1'),
                             pattern = '[0-9]{4}_US_cohort.csv',
                             full.names = TRUE)
raw1 <- do.call(rbind, lapply(cv.simul.files1, read.csv))
cv.simul.files2 <- list.files(here::here('data', 'final_US', 'cross_validation', 'batch2'),
                             pattern = '[0-9]{4}_US_cohort.csv',
                             full.names = TRUE)
raw2 <- do.call(rbind, lapply(cv.simul.files2, read.csv))
cv.simul.files3 <- list.files(here::here('data', 'final_US', 'cross_validation', 'batch3'),
                             pattern = '[0-9]{4}_US_cohort.csv',
                             full.names = TRUE)
raw3 <- do.call(rbind, lapply(cv.simul.files3, read.csv))
cv.simul.files4 <- list.files(here::here('data', 'final_US', 'cross_validation', 'batch4'),
                             pattern = '[0-9]{4}_US_cohort.csv',
                             full.names = TRUE)
raw4 <- do.call(rbind, lapply(cv.simul.files4, read.csv))
cv.simul.files5 <- list.files(here::here('data', 'final_US', 'cross_validation', 'batch5'),
                             pattern = '[0-9]{4}_US_cohort.csv',
                             full.names = TRUE)
raw5 <- do.call(rbind, lapply(cv.simul.files5, read.csv))

rawlist <- list(raw1, raw2, raw3, raw4, raw5)
raw.dat <- do.call(rbind, rawlist)

# year filter
cv.years <- cv %>% select(time) %>% unique()
cv.years <- cv.years[['time']]

#  cv <- cv.dat %>% filter(pidp %in% both.pidps$pidp)
raw <- raw.dat %>% filter(time %in% cv.years)

rm(cv.years)
```

# Financial Situation

Financial Situation is a supplementary module in Minos. It is based on the [finnow](https://www.understandingsociety.ac.uk/documentation/mainstage/variables/finnow/) variable from Understanding Society, which represents an individuals current subjective financial situation. There are 5 levels of response; Living comfortably (1), Doing alright (2), Just about getting by (3), Finding it quite difficult (4), Finding it very difficult (5).

```{r fsitch_data}
#discrete_barplot(obs, 'loneliness')
order <- c(1, 2, 3, 4, 5)
discrete_barplot(obs, order)
```

## Transition Model
  
To predict the next state of financial_situation we use a Random Forest Ordinal model from the [ranger](https://www.rdocumentation.org/packages/ranger/versions/0.16.0) package in R.

Formula:

$$  financial\_situation \sim financial\_situation_last + age + sex + ethnicity + region\\ + education\_state + housing\_quality + neighbourhood\_safety\\ + loneliness + nutrition\_quality + ncigs + job\_sec\\ + hh\_income + marital\_status + housing\_tenure  $$

```{r fsitch_model_summary}
plot_rfo_importance(model)
```


## Validation

```{r fsitch_validation}
handover_ordinal(raw.dat, base.dat, v)
```

```{r fsitch_cv}
pivoted <- combine_and_pivot_long(df1 = cv, 
                                       df1.name = 'simulated', 
                                       df2 = raw, 
                                       df2.name = 'raw', 
                                       var = v)

cv_ordinal_plots(pivoted.df = pivoted, 
                 var = v,
                 save = FALSE)
```

## Results

Random Forest Ordinal models from the ranger package cannot provide a summary like some other models can, so instead we will look at plots of observed vs predicted values as well as the importance of each variable in the resulting model.

```{r fsitch_output, echo=FALSE}
options(width=120)
discrete_barplot2(obs, preds, v)
```



```{r fsitch_performance}
cumulative_link_plot(obs, preds)
```




