---
title: "Housing"
output: html_document
bibliography: 
  - "`r here::here('docsrc', 'refs.bib')`"

---

```{r setup, include=FALSE}
library(dplyr)
library(here)
library(ranger)

source(here::here("docsrc", "documentation", "notebooks", "sphinx_notebook_utils.R"))
source(here::here('minos', 'utils_datain.R'))
source(here::here('minos', 'utils_validation_vis.R'))
model_path <- here::here("data", "transitions", "housing_quality", "rfo", "housing_quality_RFO.rds")
model <- readRDS(model_path)

data <- read.csv(here::here("data", "final_US", "2020_US_cohort.csv"))
obs <- data$housing_quality
data$housing_quality_last <- data$housing_quality

preds <- ranger::predictions(stats::predict(model, data))
column_names <- colnames(preds)
preds <-glmnet::rmult(preds)
preds <- plyr::mapvalues(preds, from=c(1,2,3), to= column_names)
v <- "housing_quality"

### Read data in for handovers plots
# Read raw datafiles in
raw.files <- list.files(here::here('data', 'final_US'), pattern='[0-9]{4}_US_cohort.csv', full.names = TRUE)
raw.dat <- do.call(rbind, lapply(raw.files, read.csv))
raw.dat <- raw.dat %>%
  filter(weight > 0)

out.path <- here::here('output', 'default_config/')
base.dat <- read_singular_local_out(out.path, 'baseline', 
                                    drop.dead = TRUE, 
                                    drop.zero.weight = TRUE)

# cut off any years of raw data AFTER start year of simulation
if (min(base.dat$time) <= max(raw.dat$time)) {
  raw.dat <- raw.dat %>%
    filter(time <= min(base.dat$time))
}

# cut missing data for key variable
raw.dat <- raw.dat %>%
  filter(!.data[[v]] %in% miss.values)
```

# Housing Quality

Housing Quality is one of the pathways outlined by the SIPHER consortium that mediates the impact of changes in household disposable income on mental wellbeing. It is based on the presence of consumer durable items in a household, as well as the ability to adequately heat the household.

Information on the variables involved:

- fridge_freezer    ([cduse5](https://www.understandingsociety.ac.uk/documentation/mainstage/variables/cduse5/))
- washing_machine   ([cduse6](https://www.understandingsociety.ac.uk/documentation/mainstage/variables/cduse6/))
- tumble_dryer      ([cduse7](https://www.understandingsociety.ac.uk/documentation/mainstage/variables/cduse7/))
- dishwasher        ([cduse8](https://www.understandingsociety.ac.uk/documentation/mainstage/variables/cduse8/))
- microwave         ([cduse9](https://www.understandingsociety.ac.uk/documentation/mainstage/variables/cduse9/))
- heating           ([hheat](https://www.understandingsociety.ac.uk/documentation/mainstage/variables/hheat/))

The housing_quality composite variable is based on the presence of a set of factors, separated into a core set and a bonus set. Variables in the core set are access to a fridge freezer, a washing machine, and being able to adequately heat your home. The bonus set includes access to a dishwasher, microwave, and tumble dryer. We chose this distinction for 2 reasons; firstly the number of households without access to items in the core set is much smaller than those without access to the bonus set, and secondly because the bonus items can be considered more of a choice, and do not necessarily represent lower housing quality if they are not present. For example, some households will not have a microwave by choice, which does not necessarily indicate poorer housing quality and certainly not in the same way that having no access to a fridge freezer would indicate lower quality. See table below for the core and bonus groupings:

| Core | Bonus |
|------|-------|
| Fridge Freezer | Dishwasher |
| Washing Machines | Tumble Dryer |
| Adequate Heating | Microwave |

The housing_quality composite is defined as:

- Missing 1+ core     == 1
- All core some bonus == 2
- All core all bonus  == 3

  
```{r housing_barchart, echo=FALSE}
order <- c("Low", "Medium", "High")
discrete_barplot(obs, order)
```

## Transition Model
  
We use a Random Forest Ordinal model from the [ranger](https://www.rdocumentation.org/packages/ranger/versions/0.16.0) package in R to estimate transitions for this variable.

Formula:

$$  housing\_quality \sim housing\_quality\_last + age + sex + ethnicity + region + education\_state + \\neighbourhood\_safety + loneliness + nutrition\_quality + ncigs + hh\_income + \\housing\_tenure + behind\_on\_bills + financial\_situation  $$

- age: Age at time of interview. 
- sex: Individual's biological sex.
- ethnicity: Discrete string values White British, Black African, etc.
- region: Administrative region of the UK. Discrete strings such as London, North-East.
- education_state: Highest attained qualification. Ordinal values based on UK government education tiers
- neighbourhood_safety: Ordinal values based on frequency of 6 factors related to safety
- loneliness: Ordinal variable for frequency of feeling lonely. Often/Sometimes/Never
- nutrition_quality: Household nutrition quality. Continuous variable proxied by frequency of consumption of fruit and vegetables.
- ncigs: Tobacco consumption. Count of cigarettes smoked per week.
- hh_income: Household Income. Continuous, equivalised household disposable income.
- housing_tenure: Housing Tenure. Ordinal variable for tenure type e.g. Owned outright, Local authority rent
- behind_on_bills: Subjective feeling of struggling to pay bills.
- financial_situation: Ordinal variable for current subjective financial situation.
- SF_12:  Mental well-being. Continuous score indicating overall mental-wellbeing.


```{r housing_model_summary}
plot_rfo_importance(model)
```

## Validation

```{r housing_validation}
handover_ordinal(raw.dat, base.dat, v)
```

## Results
  
Random Forest Ordinal models from the ranger package cannot provide a summary like some other models can, so instead we will look at plots of observed vs predicted values as well as the importance of each variable in the resulting model.


```{r housing_output, echo=FALSE}
options(width=120)
discrete_barplot2(obs, preds, 'housing_quality')
```


## References