---
title: "Household Income"
output: html_document
bibliography: 
  #- "refs.bib"  # switch bibliography position. depending on where the file is being run. stick to this one when compiiling the website using the makefile
  - "../../refs.bib" # useful for debugging.
---

## Household Income

Household disposable income is a well known indicator of mental well-being. 

```{r setup, include=FALSE}
source('sphinx_notebook_utils.R')
notebook_setwd()
```

### Methods

  What methods are used? Justification due to output data type. explanation of model output.
  
### Data
  
  What variables are included? Why is this output chosen. What explanatory variables are used and why are they chosen
  
```{r, hh_income_data}
ols_histogram("data/transitions/test/hh_income_2018_2019.rds", "hh_income_next")  
```

### Results
  
  What are the results. Coefficients tables. diagnostic plots. measures of goodness of fit.


```{r income_output, echo=FALSE}
options(width=120)
ols_output(hh_income_data_path <- "data/transitions/test/hh_income_2018_2019.rds"
)
```


### References