---
title: "Housing"
output: html_document
bibliography: 
  - "`r here::here('docsrc', 'refs.bib')`"
---

```{r setup, include=FALSE}
library(dplyr)
library(here)
library(ranger)
library(caret)

source(here::here("docsrc", "documentation", "notebooks", "sphinx_notebook_utils.R"))
source(here::here('minos', 'utils_datain.R'))
source(here::here('minos', 'utils_validation_vis.R'))
model_path <- here::here("data", "transitions", "housing_quality", "rfo", "housing_quality_RFO.rds")
model <- readRDS(model_path)

data <- read.csv(here::here("data", "final_US", "2020_US_cohort.csv"))
data$housing_quality <- factor(data$housing_quality,
                               levels = c("High",
                                          "Medium",
                                          "Low"))
obs <- data$housing_quality
data$housing_quality_last <- data$housing_quality

preds <- ranger::predictions(stats::predict(model, data))
column_names <- colnames(preds)
preds <-glmnet::rmult(preds)
preds <- plyr::mapvalues(preds, from=c(1,2,3), to= column_names)
preds <- factor(preds,
                levels = c("High", "Medium", "Low"))
v <- "housing_quality"




### Read data in for handovers plots
# Read raw datafiles in
raw.files <- list.files(here::here('data', 'final_US'), pattern='[0-9]{4}_US_cohort.csv', full.names = TRUE)
raw.dat <- do.call(rbind, lapply(raw.files, read.csv))
raw.dat <- raw.dat %>%
  filter(weight > 0)

out.path <- here::here('output', 'default_config/')
base.dat <- read_singular_local_out(out.path, 'baseline', 
                                    drop.dead = TRUE, 
                                    drop.zero.weight = TRUE)

# cut off any years of raw data AFTER start year of simulation
if (min(base.dat$time) <= max(raw.dat$time)) {
  raw.dat <- raw.dat %>%
    filter(time <= min(base.dat$time))
}

# cut missing data for key variable
raw.dat <- raw.dat %>%
  filter(!.data[[v]] %in% miss.values)


### Read data in for cross-val plots
out.path <- here::here('output', 'cv')
cv1 <- read_singular_local_out(here::here(out.path, 'default1/'), 'baseline', drop.dead = TRUE)
cv2 <- read_singular_local_out(here::here(out.path, 'default2/'), 'baseline', drop.dead = TRUE)
cv3 <- read_singular_local_out(here::here(out.path, 'default3/'), 'baseline', drop.dead = TRUE)
cv4 <- read_singular_local_out(here::here(out.path, 'default4/'), 'baseline', drop.dead = TRUE)
cv5 <- read_singular_local_out(here::here(out.path, 'default5/'), 'baseline', drop.dead = TRUE)

cvlist <- list(cv1, cv2, cv3, cv4, cv5)
cv <- do.call(rbind, cvlist)

# cv simulation batches
cv.simul.files1 <- list.files(here::here('data', 'final_US', 'cross_validation', 'batch1'),
                             pattern = '[0-9]{4}_US_cohort.csv',
                             full.names = TRUE)
raw1 <- do.call(rbind, lapply(cv.simul.files1, read.csv))
cv.simul.files2 <- list.files(here::here('data', 'final_US', 'cross_validation', 'batch2'),
                             pattern = '[0-9]{4}_US_cohort.csv',
                             full.names = TRUE)
raw2 <- do.call(rbind, lapply(cv.simul.files2, read.csv))
cv.simul.files3 <- list.files(here::here('data', 'final_US', 'cross_validation', 'batch3'),
                             pattern = '[0-9]{4}_US_cohort.csv',
                             full.names = TRUE)
raw3 <- do.call(rbind, lapply(cv.simul.files3, read.csv))
cv.simul.files4 <- list.files(here::here('data', 'final_US', 'cross_validation', 'batch4'),
                             pattern = '[0-9]{4}_US_cohort.csv',
                             full.names = TRUE)
raw4 <- do.call(rbind, lapply(cv.simul.files4, read.csv))
cv.simul.files5 <- list.files(here::here('data', 'final_US', 'cross_validation', 'batch5'),
                             pattern = '[0-9]{4}_US_cohort.csv',
                             full.names = TRUE)
raw5 <- do.call(rbind, lapply(cv.simul.files5, read.csv))

rawlist <- list(raw1, raw2, raw3, raw4, raw5)
raw.dat <- do.call(rbind, rawlist)

# year filter
cv.years <- cv %>% select(time) %>% unique()
cv.years <- cv.years[['time']]

#  cv <- cv.dat %>% filter(pidp %in% both.pidps$pidp)
raw <- raw.dat %>% filter(time %in% cv.years)

rm(cv.years)
```

# Housing Quality

Housing Quality is one of the pathways outlined by the SIPHER consortium that mediates the impact of changes in household disposable income on mental wellbeing. It is based on the presence of consumer durable items in a household, as well as the ability to adequately heat the household.

Information on the variables involved:

- fridge_freezer    ([cduse5](https://www.understandingsociety.ac.uk/documentation/mainstage/variables/cduse5/))
- washing_machine   ([cduse6](https://www.understandingsociety.ac.uk/documentation/mainstage/variables/cduse6/))
- tumble_dryer      ([cduse7](https://www.understandingsociety.ac.uk/documentation/mainstage/variables/cduse7/))
- dishwasher        ([cduse8](https://www.understandingsociety.ac.uk/documentation/mainstage/variables/cduse8/))
- microwave         ([cduse9](https://www.understandingsociety.ac.uk/documentation/mainstage/variables/cduse9/))
- heating           ([hheat](https://www.understandingsociety.ac.uk/documentation/mainstage/variables/hheat/))

The housing_quality composite variable is based on the presence of a set of factors, separated into a core set and a bonus set. Variables in the core set are access to a fridge freezer, a washing machine, and being able to adequately heat your home. The bonus set includes access to a dishwasher, microwave, and tumble dryer. We chose this distinction for 2 reasons; firstly the number of households without access to items in the core set is much smaller than those without access to the bonus set, and secondly because the bonus items can be considered more of a choice, and do not necessarily represent lower housing quality if they are not present. For example, some households will not have a microwave by choice, which does not necessarily indicate poorer housing quality and certainly not in the same way that having no access to a fridge freezer would indicate lower quality. See table below for the core and bonus groupings:

| Core | Bonus |
|------|-------|
| Fridge Freezer | Dishwasher |
| Washing Machines | Tumble Dryer |
| Adequate Heating | Microwave |

The housing_quality composite is defined as:

- Missing 1+ core     == 1
- All core some bonus == 2
- All core all bonus  == 3

*IMPORTANT NOTE:* Unfortunately, one of the core components of this composite is not present in every wave of the survey - `heating`. This caused us a major problem, as the way the pathways are devised we need at least one wave with all pathway variables present, so we can fit a transition model for SF-12. Because of this, we decided to forward fill the `heating` variable before generating the `housing_quality` composite variable. As `heating` is a fairly static variable (highest transition rate between years is 6%, mean 4.5%) we believe this is a justified decision. Please see the heating module documentation page for more information on this (specifically under the heading "Justification for Forward Fill".

  
```{r housing_barchart, echo=FALSE}
order <- c("Low", "Medium", "High")
discrete_barplot(obs, order)
```

## Transition Model
  
We use a Random Forest Ordinal model from the [ranger](https://www.rdocumentation.org/packages/ranger/versions/0.16.0) package in R to estimate transitions for this variable.

Formula:

$$  housing\_quality \sim housing\_quality\_last + age + sex + ethnicity + region + education\_state + \\neighbourhood\_safety + loneliness + nutrition\_quality + ncigs + hh\_income + \\housing\_tenure + behind\_on\_bills + financial\_situation + job\_sec  $$


| Predictor | Description | Literature/Justification |
|------|-------|-------|
| Previous Housing Quality |  |  |
| Age |  | [@whelan2012understanding] |
| Sex |  | [@whelan2012understanding] |
| Ethnicity |  |[@whelan2012understanding]  |
| Region |  |  |
| Education |  | [@whelan2012understanding] |
| Neighbourhood Safety |  | [@whelan2012understanding] |
| Loneliness |  |  |
| Nutrition Quality |  |  |
| Tobacco Consumption | Count of cigarettes smoked per week |  |
| Household Income |  | [@waters2023housing] |
| Housing Tenure | Ordinal variable for tenure type e.g. Owned outright, Local authority rent | [@whelan2012understanding] [@waters2023housing] |
| Behind on Bills | Subjective feeling of struggling to pay bills |  |
| Financial Situation | Ordinal variable for current subjective financial situation |  |
| SF-12 MCS | Mental wellbeing | [@whelan2012understanding] |


```{r housing_model_summary}
plot_rfo_importance(model)
```

## Validation

```{r housing_validation}
handover_ordinal(raw.dat, base.dat, v)
```

```{r housing_cv}
hous.pivoted <- combine_and_pivot_long(df1 = cv, 
                                       df1.name = 'simulated', 
                                       df2 = raw, 
                                       df2.name = 'raw', 
                                       var = 'housing_quality')

cv_ordinal_plots(pivoted.df = hous.pivoted, 
                 var = 'housing_quality',
                 save = FALSE)
```

## Results
  
Random Forest Ordinal models from the ranger package cannot provide a summary like some other models can, so instead we will look at plots of observed vs predicted values as well as the importance of each variable in the resulting model.


```{r housing_output, echo=FALSE}
options(width=120)
discrete_barplot2(obs, preds, 'housing_quality')
```

```{r housing_performance}
cumulative_link_plot(obs, preds)
```


## References