---
title: "Housing"
output: html_document
bibliography: 
  - "refs.bib"  # switch bibliography position. depending on where the file is being run. stick to this one when compiiling the website using the makefile
  #- "../../refs.bib" # use this one if knitting directly in Rstudio. Easier for debugging.
---

## Housing Quality


Number of cigarettes consumed is an indicator of XXXX. test reference [@1987:nelson]. 

```{r housing_setup, include=FALSE}
source('sphinx_notebook_utils.R')
```

### Methods

  What methods are used? Justification due to output data type. explanation of model output.
  
```{r housing_barchart, echo=FALSE}
print(table(real_data$housing_quality))
discrete_barplot("housing_quality")
```

### Data
  
  What variables are included? Why is this output chosen. What explanatory variables are used and why are they chosen
  
### Results
  
  What are the results. Coefficients tables. diagnostic plots. measures of goodness of fit.


```{r housing_output, echo=FALSE}
options(width=120)
clm_barplot("../../../data/transitions/test/housing_clm_2018_2019.rds", "housing_quality_next")
clm_output("../../../data/transitions/test/housing_clm_2018_2019.rds")
```


### References