---
title: "Housing"
output: html_document
bibliography: 
  - "`r here::here('docsrc', 'refs.bib')`"

---

```{r setup, include=FALSE}
library(here)
library(glmnet)
library(plyr)

source(here::here("docsrc", "documentation", "notebooks", "sphinx_notebook_utils.R"))
model_path <- here::here("data", "transitions", "housing_quality", "rfo", "housing_quality_RFO.rds")
model <- readRDS(model_path)

data <- read.csv(here::here("data", "final_US", "2020_US_cohort.csv"))
obs <- data$housing_quality
data$housing_quality_last <- data$housing_quality

preds <- ranger::predictions(stats::predict(model, data))
column_names <- colnames(preds)
preds <-glmnet::rmult(preds)
preds <- plyr::mapvalues(preds, from=c(1,2,3), to= column_names)
v <- "housing_quality"

```

# Housing Quality

Housing Quality is one of the pathways outlined by the SIPHER consortium that mediates the impact of changes in household disposable income on mental wellbeing. It is 

Information on the variables involved:
- fridge_freezer    ([cduse5](https://www.understandingsociety.ac.uk/documentation/mainstage/variables/cduse5/))
- washing_machine   ([cduse6](https://www.understandingsociety.ac.uk/documentation/mainstage/variables/cduse6/))
- tumble_dryer      ([cduse7](https://www.understandingsociety.ac.uk/documentation/mainstage/variables/cduse7/))
- dishwasher        ([cduse8](https://www.understandingsociety.ac.uk/documentation/mainstage/variables/cduse8/))
- microwave         ([cduse9](https://www.understandingsociety.ac.uk/documentation/mainstage/variables/cduse9/))
- heating           ([hheat](https://www.understandingsociety.ac.uk/documentation/mainstage/variables/hheat/))

Core set:
- fridge_freezer
- washing_machine
- adequate_heating

The housing_quality composite is defined as:
- Missing 1+ core     == 1
- All core some bonus == 2
- All core all bonus  == 3

  
```{r housing_barchart, echo=FALSE}
order <- c("Low", "Medium", "High")
discrete_barplot(obs, order)
```

## Transition Model
  
We use a Random Forest Ordinal model from the [ranger](https://www.rdocumentation.org/packages/ranger/versions/0.16.0) package in R to estimate transitions for this variable.

Formula:

$$  housing\_quality \sim housing\_quality\_last + age + sex + ethnicity + region + education\_state + neighbourhood\_safety + loneliness + nutrition\_quality + ncigs + hh\_income + housing\_tenure + behind\_on\_bills + financial\_situation  $$

- age: Age at time of interview. 
- sex: Individual's biological sex.
- ethnicity: Discrete string values White British, Black African, etc.
- region: Administrative region of the UK. Discrete strings such as London, North-East.
- education_state: Highest attained qualification. Ordinal values based on UK government education tiers
- neighbourhood_safety: Ordinal values based on frequency of 6 factors related to safety
- loneliness: Ordinal variable for frequency of feeling lonely. Often/Sometimes/Never
- nutrition_quality: Household nutrition quality. Continuous variable proxied by frequency of consumption of fruit and vegetables.
- ncigs: Tobacco consumption. Count of cigarettes smoked per week.
- hh_income: Household Income. Continuous, equivalised household disposable income.
- housing_tenure: Housing Tenure. Ordinal variable for tenure type e.g. Owned outright, Local authority rent
- behind_on_bills: Subjective feeling of struggling to pay bills.
- financial_situation: Ordinal variable for current subjective financial situation.
- SF_12:  Mental well-being. Continuous score indicating overall mental-wellbeing.

## Results
  
  What are the results. Coefficients tables. diagnostic plots. measures of goodness of fit.


```{r housing_output, echo=FALSE}
options(width=120)
discrete_barplot2(obs, preds, 'housing_quality') 
rfo_output(model)
```

```{r}
plot_rfo_importance(model)
```


## References