---
title: "Household Income"
output: html_document
bibliography: 
  - "`r here::here('docsrc', 'refs.bib')`" # finally figure out how to combine these for debugging and actual 
---

```{r load_data, include=FALSE}
library(here)
library(tidyverse)
library(lme4)
source(here::here("docsrc", "documentation", "notebooks", "sphinx_notebook_utils.R"))
source(here::here('minos', 'utils_datain.R'))
source(here::here('minos', 'utils_validation_vis.R'))
model_path <- here::here("data", "transitions", "hh_income", "glmm", "hh_income_new_GLMM.rds")
model <- readRDS(model_path)

obs <- model@frame$hh_income
preds <- predict(model, type='response')
v <- "hh_income"



### Read data in for handovers plots
# Read raw datafiles in
raw.files <- list.files(here::here('data', 'final_US'), pattern='[0-9]{4}_US_cohort.csv', full.names = TRUE)
raw.dat <- do.call(rbind, lapply(raw.files, read.csv))
raw.dat <- raw.dat %>%
  filter(weight > 0)

out.path <- here::here('output', 'default_config/')
base.dat <- read_singular_local_out(out.path, 'baseline', 
                                    drop.dead = TRUE, 
                                    drop.zero.weight = TRUE)

# cut off any years of raw data AFTER start year of simulation
if (min(base.dat$time) <= max(raw.dat$time)) {
  raw.dat <- raw.dat %>%
    filter(time <= min(base.dat$time))
}

# cut missing data for key variable
raw.dat <- raw.dat %>%
  filter(!.data[[v]] %in% miss.values)


### Read data in for cross-val plots
out.path <- here::here('output', 'cv')
cv1 <- read_singular_local_out(here::here(out.path, 'default1/'), 'baseline', drop.dead = TRUE)
cv2 <- read_singular_local_out(here::here(out.path, 'default2/'), 'baseline', drop.dead = TRUE)
cv3 <- read_singular_local_out(here::here(out.path, 'default3/'), 'baseline', drop.dead = TRUE)
cv4 <- read_singular_local_out(here::here(out.path, 'default4/'), 'baseline', drop.dead = TRUE)
cv5 <- read_singular_local_out(here::here(out.path, 'default5/'), 'baseline', drop.dead = TRUE)

cvlist <- list(cv1, cv2, cv3, cv4, cv5)
cv <- do.call(rbind, cvlist)

# cv simulation batches
cv.simul.files1 <- list.files(here::here('data', 'final_US', 'cross_validation', 'batch1'),
                             pattern = '[0-9]{4}_US_cohort.csv',
                             full.names = TRUE)
raw1 <- do.call(rbind, lapply(cv.simul.files1, read.csv))
cv.simul.files2 <- list.files(here::here('data', 'final_US', 'cross_validation', 'batch2'),
                             pattern = '[0-9]{4}_US_cohort.csv',
                             full.names = TRUE)
raw2 <- do.call(rbind, lapply(cv.simul.files2, read.csv))
cv.simul.files3 <- list.files(here::here('data', 'final_US', 'cross_validation', 'batch3'),
                             pattern = '[0-9]{4}_US_cohort.csv',
                             full.names = TRUE)
raw3 <- do.call(rbind, lapply(cv.simul.files3, read.csv))
cv.simul.files4 <- list.files(here::here('data', 'final_US', 'cross_validation', 'batch4'),
                             pattern = '[0-9]{4}_US_cohort.csv',
                             full.names = TRUE)
raw4 <- do.call(rbind, lapply(cv.simul.files4, read.csv))
cv.simul.files5 <- list.files(here::here('data', 'final_US', 'cross_validation', 'batch5'),
                             pattern = '[0-9]{4}_US_cohort.csv',
                             full.names = TRUE)
raw5 <- do.call(rbind, lapply(cv.simul.files5, read.csv))

rawlist <- list(raw1, raw2, raw3, raw4, raw5)
raw.dat <- do.call(rbind, rawlist)

# year filter
cv.years <- cv %>% select(time) %>% unique()
cv.years <- cv.years[['time']]

#  cv <- cv.dat %>% filter(pidp %in% both.pidps$pidp)
raw <- raw.dat %>% filter(time %in% cv.years)

rm(cv.years)
```

# Household Disposable Income

Household disposable income is a well known indicator of mental well-being [@graham2009understanding]. Estimating this is a crucial instrument for the effects of many policy interventions

The output variable is monthly household disposable income. This is calculated as a composite using several variables. Rent, mortgages, and council tax are subtracted from net household income and adjusted by household size. This value is then adjusted for yearly inflation estimates.

$$    hh\_income\_intermediate = ((net\_hh\_income) - (rent + mortgage + council\_tax)) / oecd\_equivalence\_factor$$
$$    hh\_income = hh\_income\_intermediate * inflation\_factor$$

More information on these variables can be found at the following links:

- [net_monthly_income](https://www.understandingsociety.ac.uk/documentation/mainstage/dataset-documentation/variable/fihhmnnet1_dv)
- monthly_outgoings is the sum of [rent](https://www.understandingsociety.ac.uk/documentation/mainstage/dataset-documentation/variable/rentgrs_dv), [mortgage](https://www.understandingsociety.ac.uk/documentation/mainstage/dataset-documentation/variable/xpmg_dv), and [council tax](https://www.understandingsociety.ac.uk/documentation/mainstage/variables/ctband_dv/).
- [oecd_equivalence_scale](https://www.understandingsociety.ac.uk/documentation/mainstage/dataset-documentation/variable/ieqmoecd_dv)
- See note [below](#Council-Tax) about council tax.

This produces a continuous distribution of pounds per month available for a household to spend as it likes. This is plotted below with a median income of $\sim£1650$.

```{r, hh_income_data}
continuous_density(obs)
```

## Transition Model

To estimate this variable we use a Generalised Linear Mixed Model (GLMM) using the [lme4](https://www.rdocumentation.org/packages/lme4/versions/1.1-36) package in R.
  
Formula:
  
$$  hh\_income \sim hh\_income\_last + age + age^2 +  age^3 + sex + ethnicity + region + \\education\_state + job\_sec + SF\_12 + labour\_state + (1|pidp)$$

Each variable included is defined as follows. Each variable with discrete values is defined in the data tables section of this documentation [here](https://leeds-mrg.github.io/Minos/documentation/data_tables.html).

| Predictor | Description | Literature/Justification |
|------|-------|-------|
| Previous Income |  | [@dilmaghani2018sexual] |
| Sex |  | [@dilmaghani2018sexual] |
| Age |  |  |
| Ethnicity |  | [@clemens2014method] |
| Region | Administrative region of the UK | [@brewer2007poverty] |
| Education | Highest attained qualification | [@eika2019educational] |
| Job NSSEC | 8 level socio-economic employment category | [@clemens2014method] |
| SF-12 MCS | Mental wellbeing | [@viswanathan2005nature] |
| Labour State | Employment status| [@dilmaghani2018sexual] |

```{r hh_income_model_summary}
print(summary(model))
```

### Council Tax

In the UKHLS main release data, [council tax](https://www.understandingsociety.ac.uk/documentation/mainstage/variables/ctband_dv/) information is reported by band. Specific amount deductions are only available in the Special Licence and Secure Access datasets. Instead of reported deductions, we have simulated the amount of council tax each household is paying by taking a random uniform draw for each household within the confines of their band.

## Validation

```{r hh_income_handovers}
handover_boxplots(raw.dat, base.dat, v)
handover_lineplots(raw.dat, base.dat, v)
```

```{r hh_income_cv}
multi_year_boxplots(raw, cv, 'hh_income')
q_q_comparison(raw, cv, 'hh_income')
```


## Results
  
Model diagnostics are displayed below. To summarise:

- r squared of 0.21 indicates reasonable fit. 
- Gender not significant. Some ethnicities see increases. Only London has higher income. High quality jobs earn more. PT employed earn less students earn more. Housing quality strong indicator of higher income. 
- diagnostic plots show under dispersion. Some extreme outlier values need investigating. 
- overall decent fit. 

```{r income_output, echo=FALSE}
options(width=120)
continuous_densities(obs, preds, v)
plot(model)
```


## References