---
title: "Labour"
output: html_document
bibliography: 
  - "`r here::here('docsrc', 'refs.bib')`" # finally figure out how to combine these for debugging and actual 
---

```{r load_data, include=FALSE}
library(dplyr)
library(here)
library(nnet)

source(here::here("docsrc", "documentation", "notebooks", "sphinx_notebook_utils.R"))
source(here::here('minos', 'utils_datain.R'))
source(here::here('minos', 'utils_validation_vis.R'))
model_path <- here::here("data", "transitions", "S7_labour_state", "nnet", "S7_labour_state_2019_2020.rds")
model <- readRDS(model_path)

data <-  read.csv(here::here("data", "final_US", "2020_US_cohort.csv"))
obs <- data$S7_labour_state
preds <- stats::predict(model, data, type='class')
obs <- factor(obs,
              levels = c("FT Employed", "PT Employed", "FT Education", 
                         "Family Care", "Job Seeking", "Not Working"))
preds <- factor(preds,
                levels = c("FT Employed", "PT Employed", "FT Education", 
                         "Family Care", "Job Seeking", "Not Working"))
v <- "S7_labour_state"

### Read data in for handovers plots
# Read raw datafiles in
raw.files <- list.files(here::here('data', 'final_US'), pattern='[0-9]{4}_US_cohort.csv', full.names = TRUE)
raw.dat <- do.call(rbind, lapply(raw.files, read.csv))
raw.dat <- raw.dat %>%
  filter(weight > 0)

out.path <- here::here('output', 'default_config/')
base.dat <- read_singular_local_out(out.path, 'baseline', 
                                    drop.dead = TRUE, 
                                    drop.zero.weight = TRUE)

# cut off any years of raw data AFTER start year of simulation
if (min(base.dat$time) <= max(raw.dat$time)) {
  raw.dat <- raw.dat %>%
    filter(time <= min(base.dat$time))
}

# cut missing data for key variable
raw.dat <- raw.dat %>%
  filter(!.data[[v]] %in% miss.values)
```

# Labour

Labour state is a measure of what an individual does. There are 8 distinctive categories including employment, unemployment, and retired. 
The encodings of these states can be found [here]](https://leeds-mrg.github.io/Minos/documentation/data_tables.html).

```{r labour_barchart, echo=FALSE}
discrete_barplot(obs)
discrete_barplot2(obs, preds, "S7_labour_state")
```

# Transition Model

Labour state is a complex categorical data type. Single layer neural network is a simple way to estimate this state. Use multinom function from R's [nnet](https://www.rdocumentation.org/packages/nnet/versions/7.3-20) package. Formula for weights included given as.

$$  labour\_state \sim labour\_state_\_last + age + sex + ethnicity + region + education\_state  $$
  
Variables used in this model. Encodings for discrete variables found in data tables.

- sex. Biological sex male/female.
- ethnicity. Ethnicity e.g. white british. XXXX cite.
- age in years. XXXX cite.
- education. Highest qualification attained. XXXX cite 
- sf12. Mental well-being score. XXXX cite
- labour_state. Previous labour state. XXXX cite. Probably remove this. dominates prediction..
- household income. Monthly disposable income of individuals household. XXXX cite.

## Validation

```{r S7_labour_state_validation}
handover_ordinal(raw.dat, base.dat, v)
```


## Results
  
  - hard to determine goodness of fit. 
  - use confusion matrix to estimate quality of fit. 
  - employed/retired well predicted. unemployed/student volatile socially and expectedly hard to predict. 
  - some deterministic replacement needed for categories like student that have specific time frames. e.g. three years for a degree.

```{r labour_output, echo=FALSE}
options(width=120)
#nnet_output("data/transitions/labour/nnet/labour_nnet_2018_2019.rds")
nnet_confusion_matrix(obs, preds, mode='multinom', 'S7_labour_state') # Note this is transition out of this state. 
```

```{r labour_performance}
cumulative_link_plot(obs, preds)
```

## References