---
title: "Labour"
output: html_document
bibliography: 
  - "`r here::here('docsrc', 'refs.bib')`" # finally figure out how to combine these for debugging and actual 
---

```{r setup, include=FALSE}
library(dplyr)
library(here)
library(ranger)
library(caret)

source(here::here("docsrc", "documentation", "notebooks", "sphinx_notebook_utils.R"))
source(here::here('minos', 'utils_datain.R'))
source(here::here('minos', 'utils_validation_vis.R'))
model_path <- here::here("data", "transitions", "S7_labour_state", "nnet", "S7_labour_state_2019_2020.rds")
model <- readRDS(model_path)

data <- read.csv(here::here("data", "final_US", "2020_US_cohort.csv"))

#data$S7_labour_state_last <- data$S7_labour_state

obs <- data$S7_labour_state
preds <- stats::predict(model, data, type='class')
obs <- factor(obs,
              levels = c("FT Employed", "PT Employed", "FT Education", 
                         "Family Care", "Job Seeking", "Not Working"))
preds <- factor(preds,
                levels = c("FT Employed", "PT Employed", "FT Education", 
                         "Family Care", "Job Seeking", "Not Working"))
v <- "S7_labour_state"




### Read data in for handovers plots
# Read raw datafiles in
raw.files <- list.files(here::here('data', 'final_US'), pattern='[0-9]{4}_US_cohort.csv', full.names = TRUE)
raw.dat <- do.call(rbind, lapply(raw.files, read.csv))
raw.dat <- raw.dat %>%
  filter(weight > 0)

out.path <- here::here('output', 'default_config/')
base.dat <- read_singular_local_out(out.path, 'baseline', 
                                    drop.dead = TRUE, 
                                    drop.zero.weight = TRUE)

# cut off any years of raw data AFTER start year of simulation
if (min(base.dat$time) <= max(raw.dat$time)) {
  raw.dat <- raw.dat %>%
    filter(time <= min(base.dat$time))
}

# cut missing data for key variable
raw.dat <- raw.dat %>%
  filter(!.data[[v]] %in% miss.values)


### Read data in for cross-val plots
out.path <- here::here('output', 'cv')
cv1 <- read_singular_local_out(here::here(out.path, 'default1/'), 'baseline', drop.dead = TRUE)
cv2 <- read_singular_local_out(here::here(out.path, 'default2/'), 'baseline', drop.dead = TRUE)
cv3 <- read_singular_local_out(here::here(out.path, 'default3/'), 'baseline', drop.dead = TRUE)
cv4 <- read_singular_local_out(here::here(out.path, 'default4/'), 'baseline', drop.dead = TRUE)
cv5 <- read_singular_local_out(here::here(out.path, 'default5/'), 'baseline', drop.dead = TRUE)

cvlist <- list(cv1, cv2, cv3, cv4, cv5)
cv <- do.call(rbind, cvlist)

# cv simulation batches
cv.simul.files1 <- list.files(here::here('data', 'final_US', 'cross_validation', 'batch1'),
                             pattern = '[0-9]{4}_US_cohort.csv',
                             full.names = TRUE)
raw1 <- do.call(rbind, lapply(cv.simul.files1, read.csv))
cv.simul.files2 <- list.files(here::here('data', 'final_US', 'cross_validation', 'batch2'),
                             pattern = '[0-9]{4}_US_cohort.csv',
                             full.names = TRUE)
raw2 <- do.call(rbind, lapply(cv.simul.files2, read.csv))
cv.simul.files3 <- list.files(here::here('data', 'final_US', 'cross_validation', 'batch3'),
                             pattern = '[0-9]{4}_US_cohort.csv',
                             full.names = TRUE)
raw3 <- do.call(rbind, lapply(cv.simul.files3, read.csv))
cv.simul.files4 <- list.files(here::here('data', 'final_US', 'cross_validation', 'batch4'),
                             pattern = '[0-9]{4}_US_cohort.csv',
                             full.names = TRUE)
raw4 <- do.call(rbind, lapply(cv.simul.files4, read.csv))
cv.simul.files5 <- list.files(here::here('data', 'final_US', 'cross_validation', 'batch5'),
                             pattern = '[0-9]{4}_US_cohort.csv',
                             full.names = TRUE)
raw5 <- do.call(rbind, lapply(cv.simul.files5, read.csv))

rawlist <- list(raw1, raw2, raw3, raw4, raw5)
raw.dat <- do.call(rbind, rawlist)

# year filter
cv.years <- cv %>% select(time) %>% unique()
cv.years <- cv.years[['time']]

#  cv <- cv.dat %>% filter(pidp %in% both.pidps$pidp)
raw <- raw.dat %>% filter(time %in% cv.years)

rm(cv.years)
```

# Labour

Labour state relates to the employment status of an individual, which is derived from the [jbstat](https://www.understandingsociety.ac.uk/documentation/mainstage/variables/jbstat/) and [jbft_dv](https://www.understandingsociety.ac.uk/documentation/mainstage/variables/jbft_dv/) variables from Understanding Society. The jbstat variable from US has 16 categories, which we have recoded into a variable with 6 categories based on the SIPHER 7 definition of labour state. jbft_dv indicates whether the individual worked full or part time (greater than 30 hours per week for full time). The table below shows which categories have been combined into the new reduced categories:

| New Category | Old Categories |
| ------------ | -------------- |
| FT Employed  | Paid employment (AND jbft_dv == 1); Self-employed; Unpaid, family business; Apprenticeship; Furlough |
| PT Employed  | Paid employment (AND jbft_dv == 2) |
| Job Seeking  | Unemployed; Temporarily laid off/Short-term Working |
| FT Education | Full-time Student; Government Training |
| Family Care  | Family Care |
| Not Working  | Retired; Maternity Leave; LT Sick or Disabled |

```{r labour_barchart, echo=FALSE}
discrete_barplot(obs)
```

## Transition Model

Labour state is a complex categorical data type. Single layer neural network is a simple way to estimate this state. Use multinom function from R's [nnet](https://www.rdocumentation.org/packages/nnet/versions/7.3-20) package. Formula for weights included given as.

$$  labour\_state \sim labour\_state_\_last + age + sex + ethnicity + region + education\_state + SF\_12 + hh\_income  $$

## Validation

```{r S7_labour_state_validation}
handover_ordinal(raw.dat, base.dat, v)
```


## Results
  
  - hard to determine goodness of fit. 
  - use confusion matrix to estimate quality of fit. 
  - employed/retired well predicted. unemployed/student volatile socially and expectedly hard to predict. 
  - some deterministic replacement needed for categories like student that have specific time frames. e.g. three years for a degree.

```{r labour_output, echo=FALSE}
options(width=120)
discrete_barplot2(obs, preds, v)
#nnet_output("data/transitions/labour/nnet/labour_nnet_2018_2019.rds")
nnet_confusion_matrix(obs, preds, mode='multinom', 'S7_labour_state') # Note this is transition out of this state. 
```

```{r labour_performance}
cumulative_link_plot(obs, preds)
```

## References