---
title: "Mental Well-Being"
output: html_document
bibliography: 
  - "`r here::here('docsrc', 'refs.bib')`"
---

# Mental Well-Being

```{r load_data, include=FALSE}
library(dplyr)
library(here)
library(lme4)
source(here::here("docsrc", "documentation", "notebooks", "sphinx_notebook_utils.R"))
source(here::here('minos', 'utils_datain.R'))
source(here::here('minos', 'utils_validation_vis.R'))
model_path <- here::here("data", "transitions", "SF_12", "lmm", "SF_12_LMM.rds")
model <- readRDS(model_path)

obs <- model@frame$SF_12
preds <- predict(model, type='response')
v <- "SF_12"

### Read data in for handovers plots
# Read raw datafiles in
raw.files <- list.files(here::here('data', 'final_US'), pattern='[0-9]{4}_US_cohort.csv', full.names = TRUE)
raw.dat <- do.call(rbind, lapply(raw.files, read.csv))
raw.dat <- raw.dat %>%
  filter(weight > 0)

out.path <- here::here('output', 'default_config/')
base.dat <- read_singular_local_out(out.path, 'baseline', 
                                    drop.dead = TRUE, 
                                    drop.zero.weight = TRUE)

# cut off any years of raw data AFTER start year of simulation
if (min(base.dat$time) <= max(raw.dat$time)) {
  raw.dat <- raw.dat %>%
    filter(time <= min(base.dat$time))
}

# cut missing data for key variable
raw.dat <- raw.dat %>%
  filter(!.data[[v]] %in% miss.values)



### Read data in for cross-val plots
out.path <- here::here('output', 'cv')
cv1 <- read_singular_local_out(here::here(out.path, 'default1/'), 'baseline', drop.dead = TRUE)
cv2 <- read_singular_local_out(here::here(out.path, 'default2/'), 'baseline', drop.dead = TRUE)
cv3 <- read_singular_local_out(here::here(out.path, 'default3/'), 'baseline', drop.dead = TRUE)
cv4 <- read_singular_local_out(here::here(out.path, 'default4/'), 'baseline', drop.dead = TRUE)
cv5 <- read_singular_local_out(here::here(out.path, 'default5/'), 'baseline', drop.dead = TRUE)

cvlist <- list(cv1, cv2, cv3, cv4, cv5)
cv <- do.call(rbind, cvlist)

# cv simulation batches
cv.simul.files1 <- list.files(here::here('data', 'final_US', 'cross_validation', 'batch1'),
                             pattern = '[0-9]{4}_US_cohort.csv',
                             full.names = TRUE)
raw1 <- do.call(rbind, lapply(cv.simul.files1, read.csv))
cv.simul.files2 <- list.files(here::here('data', 'final_US', 'cross_validation', 'batch2'),
                             pattern = '[0-9]{4}_US_cohort.csv',
                             full.names = TRUE)
raw2 <- do.call(rbind, lapply(cv.simul.files2, read.csv))
cv.simul.files3 <- list.files(here::here('data', 'final_US', 'cross_validation', 'batch3'),
                             pattern = '[0-9]{4}_US_cohort.csv',
                             full.names = TRUE)
raw3 <- do.call(rbind, lapply(cv.simul.files3, read.csv))
cv.simul.files4 <- list.files(here::here('data', 'final_US', 'cross_validation', 'batch4'),
                             pattern = '[0-9]{4}_US_cohort.csv',
                             full.names = TRUE)
raw4 <- do.call(rbind, lapply(cv.simul.files4, read.csv))
cv.simul.files5 <- list.files(here::here('data', 'final_US', 'cross_validation', 'batch5'),
                             pattern = '[0-9]{4}_US_cohort.csv',
                             full.names = TRUE)
raw5 <- do.call(rbind, lapply(cv.simul.files5, read.csv))

rawlist <- list(raw1, raw2, raw3, raw4, raw5)
raw.dat <- do.call(rbind, rawlist)

# year filter
cv.years <- cv %>% select(time) %>% unique()
cv.years <- cv.years[['time']]

#  cv <- cv.dat %>% filter(pidp %in% both.pidps$pidp)
raw <- raw.dat %>% filter(time %in% cv.years)

rm(cv.years)
```

Mental wellbeing is one of the key output of MINOS. 

To measure mental wellbeing, we use the Short-Form 12 Mental Component Score (SF-12 MCS). The Short-Form 12 survey is a survey consisting of 12 questions relating to both physical and mental health. [See here](https://www.england.nhs.uk/wp-content/uploads/2022/12/Short-form-12-health-survey-questionnaire.pdf) for a copy of the survey.

Summary scores for both mental and physical health can be calculated from the responses, leading to the Mental Component Score (MCS). MCS is a measure ranging from 0 (low functioning) to 100 (high functioning). SF-12 MCS is represented by a variable directly from the survey - [`sf12mcs_dv`](https://www.understandingsociety.ac.uk/documentation/mainstage/variables/sf12mcs_dv/). Each of the responses to the 12 questions are also available in the survey.


```{r}
continuous_density(obs)
```

## Transition Model

We use a Linear Mixed Model (LMM) from the [lme4](https://www.rdocumentation.org/packages/lme4/versions/1.1-36) package in R.

Formula:

$$  SF\_12 \sim SF\_12\_last + age + sex + ethnicity + region + education\_state + hh\_income + \\housing\_quality + neighbourhood\_safety + loneliness + nutrition\_quality + ncigs + \\I(ncigs>0) + (1|pidp)  $$

| Predictor | Description | Literature/Justification |
|------|-------|-------|
| Previous Mental Wellbeing |  |  |
| Sex |  |  |
| Age |  |  |
| Ethnicity |  |  |
| Region | Administrative region of the UK |  |
| Education | Highest attained qualification |  |
| Household Income |  |  |
| Housing Quality |  |  |
| Neighbourhood Safety |  | [@ruijsbroek2014social] [@putrik2019assessing] |
| Loneliness |  |  |
| Nutrition Quality |  |  |
| Tobacco Use |  |  |

```{r mwb_model_summary}
print(summary(model))
```

## Validation

```{r mwb_handovers}
handover_boxplots(raw.dat, base.dat, v)
#handover_lineplots(raw.dat, base.dat, v)
```

```{r mwb_cv}
multi_year_boxplots(raw, cv, v)
q_q_comparison(raw, cv, v)
```

## Results

```{r SF12_Output, echo=FALSE}
options(width=120)
continuous_densities(obs, preds, v)
plot(model)
```

## References
