---
title: "Mental Well-Being"
output: html_document
bibliography: 
  - "docsrc/refs.bib"
---

```{r setup, include=FALSE}
knitr::opts_knit$set(root.dir= "../minos")
```

## Mental Well-Being

Introductory fluff. Why do we need this module? test reference [@1987:nelson].

```{r load_data, include=FALSE}
source("docsrc/documentation/notebooks/sphinx_notebook_utils.R")
```

### Methods

What methods are used? Justification due to output data type. explanation of model output.

```{r SF12_Density}
continuous_density("data/transitions/SF_12/OLS/SF_12_2018_2019.rds", "next_SF_12")  
```

### Data

What variables are included? Why is this output chosen. What explanatory variables are used and why are they chosen

### Results

What are the results. Coefficients tables. diagnostic plots. measures of goodness of fit.

```{r SF12_Output, echo=FALSE}
options(width=120)
ols_output("data/transitions/SF_12/OLS/SF_12_2018_2019.rds")
ols_histogram("data/transitions/SF_12/OLS/SF_12_2018_2019.rds", "next_SF_12")
```

### References
