---
title: "Mental Well-Being"
output: html_document
bibliography: 
  - "`r here::here('docsrc', 'refs.bib')`"
---

# Mental Well-Being

```{r load_data, include=FALSE}
library(here)
source(here::here("docsrc", "documentation", "notebooks", "sphinx_notebook_utils.R"))
model_path <- here::here("data", "transitions", "SF_12", "lmm", "SF_12_LMM.rds")
model <- readRDS(model_path)

obs <- model@frame$SF_12
preds <- predict(model, type='response')
v <- "SF_12"
```

Mental wellbeing is one of the key output of MINOS. 

To measure mental wellbeing, we use the Short-Form 12 Mental Component Score (SF-12 MCS). The Short-Form 12 survey is a survey consisting of 12 questions relating to both physical and mental health. [See here](https://www.england.nhs.uk/wp-content/uploads/2022/12/Short-form-12-health-survey-questionnaire.pdf) for a copy of the survey.
Summary scores for both mental and physical health can be calculated from the responses, leading to the Mental Component Score (MCS). MCS is a measure ranging from 0 (low functioning) to 100 (high functioning). SF-12 MCS is represented by a variable directly from the survey - [`sf12mcs_dv`](https://www.understandingsociety.ac.uk/documentation/mainstage/variables/sf12mcs_dv/). Each of the responses to the 12 questions are also available in the survey.


```{r}
continuous_density(obs)
```

## Transition Model

We use a Linear Mixed Model (LMM) from the [lme4](https://www.rdocumentation.org/packages/lme4/versions/1.1-36) package in R.

Formula:

$$  SF\_12 \sim SF\_12\_last + age + sex + ethnicity + region + education\_state + hh\_income + \\housing\_quality + neighbourhood\_safety + loneliness + nutrition\_quality + ncigs + \\I(ncigs>0) + (1|pidp)  $$

```{r mwb_model_summary}
print(summary(model))
```

## Results

```{r SF12_Output, echo=FALSE}
options(width=120)
continuous_densities(obs, preds, v)
plot(model)
```

## References
