---
title: "Neighbourhood"
output: html_document
bibliography: 
  - "`r here::here('docsrc', 'refs.bib')`"

---

```{r setup, include=FALSE}
library(here)
library(glmnet)
library(plyr)

source(here::here("docsrc", "documentation", "notebooks", "sphinx_notebook_utils.R"))
model_path <- here::here("data", "transitions", "neighbourhood_safety", "rfo", "neighbourhood_safety_RFO.rds")
model <- readRDS(model_path)

data <- read.csv(here::here("data", "final_US", "2020_US_cohort.csv"))
obs <- data$neighbourhood_safety
data$neighbourhood_safety_last <- data$neighbourhood_safety

preds <- ranger::predictions(stats::predict(model, data))
column_names <- colnames(preds)
preds <-glmnet::rmult(preds)
preds <- plyr::mapvalues(preds, from=c(1,2,3), to= column_names)
v <- " neighbourhood_safety"

```

# Neighbourhood

Neighbourhood Safety is a composite derived from 7 questions related to different facets of safety in the neighbourhood.

They are:

- burglaries        ([crburg](https://www.understandingsociety.ac.uk/documentation/mainstage/variables/crburg/))
- car crime         ([crcar](https://www.understandingsociety.ac.uk/documentation/mainstage/variables/crcar/))
- drunks            ([crdrnk](https://www.understandingsociety.ac.uk/documentation/mainstage/variables/crdrnk/))
- muggings          ([crmugg](https://www.understandingsociety.ac.uk/documentation/mainstage/variables/crmugg/))
- racial abuse      ([crrace](https://www.understandingsociety.ac.uk/documentation/mainstage/variables/crrace/))
- teenager issues   ([crteen](https://www.understandingsociety.ac.uk/documentation/mainstage/variables/crteen/))
- vandalism issues  ([crvand](https://www.understandingsociety.ac.uk/documentation/mainstage/variables/crvand/))

Each respondent is asked if they are concerned with these issues in their neighbourhood, and response with 1 of:

1. Hardly ever
2. Some of the time
3. Often


We then assign people into three categories:

1. Very Safe Neighbourhood: Response to all crime questions is “not at all common”. Justification is that if you
    perceive no threat at all this is the best possible state.
2. Safe Neighbourhood: Responds to 1+ question as “not very common” but no responses to ‘fairly or very common’.
    Justification is that on the whole these people probably feel safe but not all is perfect, so probably not
    quite as desirable as group 1.
3. Unsafe Neighbourhood: Responds to 1+ question as fairly or very common’. Justification is that if perception of crime is
    very or fairly common, no matter what category, you are likely to feel that your neighbourhood safety is
    compromised.


## Methods
  
```{r neighbourhood_barchart, echo=FALSE}
order <- c(1, 2, 3)
discrete_barplot(obs, order)
```
  
## Transition Model

We fit a Random Forest Ordinal model from the [ranger](https://www.rdocumentation.org/packages/ranger/versions/0.16.0) package in R to estimate transitions for this variable.

Formula:

$$  neighbourhood\_safety \sim age + sex + ethnicity + region + education\_state + hh\_income + behind\_on\_bills + financial\_situation  $$

## Results

```{r neighbourhood_output, echo=FALSE}
options(width=120)
discrete_barplot2(obs, preds, "neighbourhood_safety") 
plot_rfo_importance(model)
```


## References