---
title: "Nutrition"
output: html_document
bibliography: 
  - "`r here::here('docsrc', 'refs.bib')`"

---

```{r setup, include=FALSE}
library(here)
library(glmnet)
library(plyr)

source(here::here("docsrc", "documentation", "notebooks", "sphinx_notebook_utils.R"))
model_path <- here::here("data", "transitions", "nutrition_quality", "lmm", "nutrition_quality_new_LMM.rds")
model <- readRDS(model_path)

data <- read.csv(here::here("data", "final_US", "2021_US_cohort.csv"))
obs <- data$nutrition_quality
data$nutrition_quality_last <- data$nutrition_quality
preds <- predict(model, type='response')
v <- "nutrition_quality"

```

# Nutrition

Nutrition Quality is represented by a proxy of the number of portions of fruit and vegetables eaten per week. The following variables from understanding society that measure fruit and vegetable consumption were used:

- [wkfruit](https://www.understandingsociety.ac.uk/documentation/mainstage/dataset-documentation/variable/wkfruit),
- [fruitamt](https://www.understandingsociety.ac.uk/documentation/mainstage/dataset-documentation/variable/fruitamt),
- [wkvege](https://www.understandingsociety.ac.uk/documentation/mainstage/dataset-documentation/variable/wkvege), and
- [vegeamt](https://www.understandingsociety.ac.uk/documentation/mainstage/dataset-documentation/variable/vegeamt).

The equations to generate the nutrition composite are as follows:

$$  fruit\_intermediate = days\_eating\_fruit\_per\_week * fruit\_per\_day  $$
$$  veg\_intermediate = days\_eating\_veg\_per\_week * veg\_per\_day  $$
$$  nutrition\_composite = fruit\_intermediate + veg\_intermediate $$

Both [fruit](https://www.understandingsociety.ac.uk/documentation/mainstage/dataset-documentation/variable/wkfruit) and [vegetable](https://www.understandingsociety.ac.uk/documentation/mainstage/dataset-documentation/variable/wkvege) consumption frequency was measured in days per week, and reported as:

1. Never
2. 1-3 days
3. 4-6 days
4. Every day

The amount of [fruit](https://www.understandingsociety.ac.uk/documentation/mainstage/dataset-documentation/variable/fruitamt) and [veg](https://www.understandingsociety.ac.uk/documentation/mainstage/dataset-documentation/variable/vegeamt) per day was a continuous variable, indicating the number of portions of fruit or veg eaten on an average day when the respondent eats fruit or veg.

This gives us a continuous nutrition score, composed of the sum of two proxy values for the amount of fruit and veg eaten per week. Unfortunately because the `days_eating_<>_per_week` variables are ordinal (levels = [Never, 1-3 days, 4-6 days, Everyday]) and not just the number of days, we can't calculate an actual value 
for `amount_per_week`.

```{r, nutrition_quality_data}
continuous_density(obs)
```


## Transition Model

We use a Linear Mixed Model (LMM) from the [lme4](https://www.rdocumentation.org/packages/lme4/versions/1.1-36) package in R to predict the next state of nutrition quality.

Formula:

$$  nutrition\_quality \sim age + sex + ethnicity + region + education\_state + hh\_income + behind\_on\_bills + financial\_situation + (1|pidp) + (1|hidp)  $$

```{r nutrition_model_summary}
print(summary(model))
```


## Results

```{r nutrition_output, echo=FALSE}
options(width=120)
continuous_densities(obs, preds, v)
plot(model)
```

## References