---
title: "Tobacco Transition Module"
output: html_document
bibliography: 
  - "refs.bib"  # switch bibliography position. depending on where the file is being run. stick to this one when compiiling the website using the makefile
  #- "../../refs.bib" # use this one if knitting directly in Rstudio. Easier for debugging.
---

## Tobacco


Number of cigarettes consumed is an indicator of XXXX. test reference [@1987:nelson]. 

```{r setup, include=FALSE}
source('sphinx_notebook_utils.R')
notebook_setwd()

```

### Methods

  What methods are used? Justification due to output data type. explanation of model output.
  
### Data
  
  What variables are included? Why is this output chosen. What explanatory variables are used and why are they chosen

```{r tobacco_data}
zip_density("data/transitions/test/tobacco_zip_2018_2019.rds", 'y')
```
### Results
  
  What are the results. Coefficients tables. diagnostic plots. measures of goodness of fit.


```{r tobacco_output, echo=FALSE}
options(width=120)
zip_output("data/transitions/test/tobacco_zip_2018_2019.rds")
```


### References

