---
title: "Tobacco"
output:
  pdf_document: default
  html_document: default
bibliography: docsrc/refs.bib
---

```{r setup, include=FALSE}
knitr::opts_knit$set(root.dir= "../minos")
```
## Tobacco


Number of cigarettes consumed is an indicator of several mental illnesses including anxiety [@lawrence2010anxiety].

```{r load_data, include=FALSE}
source('docsrc/documentation/notebooks/sphinx_notebook_utils.R')
```


### Data
  
  What variables are included? Why is this output chosen. What explanatory variables are used and why are they chosen

```{r tobacco_data}
counts_density("data/transitions/ncigs/zip/ncigs_2018_2019.rds", "y")
```

### Methods

The number of zero inflated values is higher than expected for a count distribution such as a poisson distribution. This inflation occurs naturally as a large proportion (over 50\%) of the population do not smoke. There are two sources of cigarette consumption that can be modelled using zero inflated models. In this case a zero-inflated poisson (ZIP) is used. Two models are fitted simulatenously. One is a logistic regression that estimates whether a person smokes cigarettes or not. This provides a simple probability of smoking or not. The second is a poisson counts model estimating the number of cigarettes consumed. 

### Data

Two set of variables are needed for the logistic and poisson parts of the ZIP model respectively.

Variables that predict how much a person smokes.

age. persons age. generally older people and very young smoke. 
SF_12. wellbeing estimates number of cigarettes smoked.
labour_state. whether a person is employed or not.
ethnicity. certain ethnicities more likely to smoke cigarettes. 
education_state. highest qualification.
job_sec job quality
hh_income household income
ncigs previous number consumed.

Variables that predict whether a person smokes

ethnicity. certain ethnicities more likely to smoke cigarettes. 
labour_state. whether a person is employed or not.
age
SF_12. wellbeing estimates number of cigarettes smoked.
ncigs previous number consumed.

### Results
  
Almost all coefficients significant. Particularly prevous consumption of cigarettes. Good estimation of the number of non-smokers in the population at around 55\%. Counts of smoking are underdispersed and fail to estimate consumption over 20 cigarettes. 


```{r tobacco_output, echo=FALSE}
options(width=120)
zip_output("data/transitions/ncigs/zip/ncigs_2018_2019.rds")
zip_density("data/transitions/ncigs/zip/ncigs_2018_2019.rds", 'y')
```


### References

