---
title: "Tobacco"
output: html_document
bibliography: 
  - "`r here::here('docsrc', 'refs.bib')`"
  
---

# Tobacco

```{r setup, include=FALSE}
library(here)
library(glmnet)
library(plyr)

source(here::here("docsrc", "documentation", "notebooks", "sphinx_notebook_utils.R"))
model_path <- here::here("data", "transitions", "ncigs", "zip", "ncigs_2019_2020.rds")
model <- readRDS(model_path)

data <- read.csv(here::here("data", "final_US", "2020_US_cohort.csv"))
obs <- data$ncigs
data$ncigs_last <- data$ncigs

#preds <- ranger::predictions(stats::predict(model, data))
#column_names <- colnames(preds)
#preds <-glmnet::rmult(preds) - 1
#preds <- 5 * preds

v <- "ncigs"

```

Tobacco consumption is measured in the usual number of cigarettes smoked per day, and is taken directly from a US variable ([ncigs](https://www.understandingsociety.ac.uk/documentation/mainstage/dataset-documentation/variable/ncigs)). Number of cigarettes consumed is an indicator of several mental illnesses including anxiety [@lawrence2010anxiety].

```{r tobacco_data}
continuous_density(obs)
obs_no_zero <- obs[obs != 0]  # remove zero values to look at counts only for smokers
continuous_density(obs_no_zero)
```

## Transition Model

The number of zero inflated values is higher than expected for a count distribution such as a poisson distribution. This inflation occurs naturally as a large proportion (over 50\%) of the population do not smoke. There are two sources of cigarette consumption that can be modelled using zero inflated models. In this case a zero-inflated poisson (ZIP) is used. Two models are fitted simultaneously. One is a logistic regression that estimates whether a person smokes cigarettes or not. This provides a simple probability of smoking or not. The second is a poisson counts model estimating the number of cigarettes consumed. This is modelled using the `zeroinfl()` function from the [pscl](https://www.rdocumentation.org/packages/pscl/versions/1.5.9) package in R.

Formula:

$$  ncigs ~ ncigs\_last + age + sex + ethnicity + region + education\_state + housing\_quality + neighbourhood\_safety + loneliness + nutrition\_quality + hh\_income + SF\_12 + behind\_on\_bills + financial\_situation | ncigs\_last + I(ncigs_last>0) + ethnicity + housing\_quality + neighbourhood\_safety + loneliness + nutrition\_quality + job\_sec + hh\_income + SF\_12 + behind\_on\_bills + financial\_situation  $$

NOTE: The syntax seen above `I(ncigs>0)` represents a binary flag for whether a person smoked previously (`ncigs > 0`).

Two set of variables are needed for the logistic and poisson parts of the ZIP model respectively. These two formula are separated by a '|' symbol. On the right hand side of the '|' is the formula for the logistic regression that determines whether an individual is a smoker or not. On the left side is the formula for the poisson model to predict the counts of cigarettes for smokers.

ncigs_last previous number consumed.
age. persons age. generally older people and very young smoke. 
sex.
ethnicity. certain ethnicities more likely to smoke cigarettes. 
region.
education_state. highest qualification.
housing quality.
neighbourhood safety.
loneliness.
nutrition quality.
hh_income household income
SF_12. wellbeing estimates number of cigarettes smoked.
behind on bills.
financial situation.
labour_state. whether a person is employed or not.
job_sec job quality

```{r tobacco_model_summary}
zip_output(model)
```


## Results
  
Almost all coefficients significant. Particularly prevous consumption of cigarettes. Good estimation of the number of non-smokers in the population at around 55\%. Counts of smoking are underdispersed and fail to estimate consumption over 20 cigarettes. 


```{r tobacco_output, echo=FALSE}
options(width=120)
continuous_densities(obs, preds, "ncigs")
#zip_density(model, 'ncigs')
```

## References