---
title: "Tobacco"
output: html_document
bibliography: 
  - "`r here::here('docsrc', 'refs.bib')`"
  
---

# Tobacco

```{r setup, include=FALSE}
library(dplyr)
library(here)
library(pscl)

source(here::here("docsrc", "documentation", "notebooks", "sphinx_notebook_utils.R"))
source(here::here('minos', 'utils_datain.R'))
source(here::here('minos', 'utils_validation_vis.R'))
model_path <- here::here("data", "transitions", "ncigs", "zip", "ncigs_2019_2020.rds")
model <- readRDS(model_path)

data <- read.csv(here::here("data", "final_US", "2020_US_cohort.csv"))
obs <- data$ncigs
data$ncigs_last <- data$ncigs

#preds <- ranger::predictions(stats::predict(model, data))
#column_names <- colnames(preds)
#preds <-glmnet::rmult(preds) - 1
#preds <- 5 * preds

v <- "ncigs"

### Read data in for handovers plots
# Read raw datafiles in
raw.files <- list.files(here::here('data', 'final_US'), pattern='[0-9]{4}_US_cohort.csv', full.names = TRUE)
raw.dat <- do.call(rbind, lapply(raw.files, read.csv))
raw.dat <- raw.dat %>%
  filter(weight > 0)

out.path <- here::here('output', 'default_config/')
base.dat <- read_singular_local_out(out.path, 'baseline', 
                                    drop.dead = TRUE, 
                                    drop.zero.weight = TRUE)

# cut off any years of raw data AFTER start year of simulation
if (min(base.dat$time) <= max(raw.dat$time)) {
  raw.dat <- raw.dat %>%
    filter(time <= min(base.dat$time))
}

# cut missing data for key variable
raw.dat <- raw.dat %>%
  filter(!.data[[v]] %in% miss.values)
```

Tobacco consumption is measured in the usual number of cigarettes smoked per day, and is taken directly from a US variable ([ncigs](https://www.understandingsociety.ac.uk/documentation/mainstage/dataset-documentation/variable/ncigs)). Number of cigarettes consumed is an indicator of several mental illnesses including anxiety [@lawrence2010anxiety].

```{r tobacco_data}
continuous_density(obs)
obs_no_zero <- obs[obs != 0]  # remove zero values to look at counts only for smokers
continuous_density(obs_no_zero)
```

## Transition Model

The number of zero inflated values is higher than expected for a count distribution such as a poisson distribution. This inflation occurs naturally as a large proportion (over 50\%) of the population do not smoke. There are two sources of cigarette consumption that can be modelled using zero inflated models. In this case a zero-inflated poisson (ZIP) is used. Two models are fitted simultaneously. One is a logistic regression that estimates whether a person smokes cigarettes or not. This provides a simple probability of smoking or not. The second is a poisson counts model estimating the number of cigarettes consumed. This is modelled using the `zeroinfl()` function from the [pscl](https://www.rdocumentation.org/packages/pscl/versions/1.5.9) package in R.

Formula:

$$  ncigs \sim ncigs\_last + age + sex + ethnicity + region + education\_state + housing\_quality + \\neighbourhood\_safety + loneliness + nutrition\_quality + \\hh\_income + SF\_12 + behind\_on\_bills + financial\_situation \\|\\ ncigs\_last + I(ncigs_last>0) + ethnicity + housing\_quality + \\neighbourhood\_safety + loneliness + nutrition\_quality + job\_sec + \\hh\_income + SF\_12 + behind\_on\_bills + financial\_situation  $$

NOTE: The syntax seen above `I(ncigs>0)` represents a binary flag for whether a person smoked previously (`ncigs > 0`).

Two set of variables are needed for the logistic and poisson parts of the ZIP model respectively. These two formula are separated by a '|' symbol. On the right hand side of the '|' is the formula for the logistic regression that determines whether an individual is a smoker or not. On the left side is the formula for the poisson model to predict the counts of cigarettes for smokers.

ncigs_last previous number consumed.
age. persons age. generally older people and very young smoke. 
sex.
ethnicity. certain ethnicities more likely to smoke cigarettes. 
region.
education_state. highest qualification.
housing quality.
neighbourhood safety.
loneliness.
nutrition quality.
hh_income household income
SF_12. wellbeing estimates number of cigarettes smoked.
behind on bills.
financial situation.
labour_state. whether a person is employed or not.
job_sec job quality

```{r tobacco_model_summary}
zip_output(model)
```


## Validation

```{r ncigs_validation}
handover_boxplots(raw.dat, base.dat, v)
handover_lineplots(raw.dat, base.dat, v)
```



## Results
  
Almost all coefficients significant. Particularly previous consumption of cigarettes. Good estimation of the number of non-smokers in the population at around 55\%. Counts of smoking are underdispersed and fail to estimate consumption over 20 cigarettes. 


```{r tobacco_output, echo=FALSE}
options(width=120)
#continuous_densities(obs, preds, "ncigs")

zip_density <- function (zip_model, v){
  # Density plot for zip models.
  # zip model outputs two sets of predictors.
  #
  # First is probability of non-zero event. 
  # For sample n this is a length n vector of values between 0 and 1 containing probabilities.
  # E.g. probability a person smokes anything. 
  #
  # Second is count values given non-zero event.
  # E.g. if a person smokes what is their predicted consumption.
  #
  # Combine these two together to get an estimated count density for the whole population.
  # Randomly sample if individuals have a non-zero even using probabilities.
  # If they have an event assign them the corresponding count else 0.
  
  # get obs/preds
  #zip_model <- readRDS(data_path)
  obs <- zip_model[[v]]
  # predict probability of zero value and counts of non-zero value..
  probs <- predict(zip_model, type='zero')
  counts <- predict(zip_model, type='count')
  # randomly assign 0 values to individuals based on probability of zero status.
  preds <- (runif(length(probs)) >= probs) * counts
  # density plot for obs and preds lines.
  plot(density(preds, from=0), lty=1, col='red')
  lines(density(obs, from=0), col='blue', lty=2)
  legend('topright', legend=c("Predicted", "Real"), col=c("red", "blue"), lty=1:2)
}

zip_density(model, 'ncigs')
```

## References